### 2023-02-05 drafting_results_section.Rmd
started drafting results section

---
title: "Who Cares about Morality"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
```

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)
```

```{r}

#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

df$sex3 <- as.factor(df$sex1)
df$sex3 <- dplyr::recode(df$sex3,
               "1"="male"
              ,"2"="female"
              ,"3"="other")

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")

```

```{r}

```

# H1 Gender Differences

```{r}

x <- df

table(x$sex3)
x <- x[which(x$sex3!="other"),]
x$sex3 <- droplevels(x$sex3)

t1 <- t.test(x$moral_identity_internal ~ x$sex3)
d1 <- cohen.d(x$moral_identity_internal, x$sex3)

d1$cohen.d[2]
sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))
sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))
sprintf("%.2f",t1$parameter)
sprintf("%.2f",t1$statistic)

t2 <- t.test(x$moral_identity_symbolic ~ x$sex3)
d2 <- cohen.d(x$moral_identity_symbolic, x$sex3)

```

Our first hypothesis was that women would have higher levels of internalization and symbolization than men. To test this we isolated the data for men and women from the main dataset. An independent samples t-test revealed that for the entire sample, women had higher internalization scores (*M* = `r sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))`), than men (*M* = `r sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='male')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='male')],na.rm=T))`), *t*(`r sprintf("%.2f",t1$parameter)`) = `r sprintf("%.2f",t1$statistic)`, *p* `r paste(p_report(t1$p.value))`, *d* = `r sprintf("%.2f", d1$cohen.d[2])`. Similarly, for symbolization, an independent samples t-test revealed that for the entire sample, women had higher scores (*M* = `r sprintf("%.1f",mean(x$moral_identity_symbolic[which(x$sex3=='female')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_symbolic[which(x$sex3=='female')],na.rm=T))`), than men (*M* = `r sprintf("%.1f",mean(x$moral_identity_symbolic[which(x$sex3=='male')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_symbolic[which(x$sex3=='male')],na.rm=T))`), *t*(`r sprintf("%.2f",t2$parameter)`) = `r sprintf("%.2f",t2$statistic)`, *p* `r paste(p_report(t2$p.value))`, *d* = `r sprintf("%.2f", d2$cohen.d[2])`.

```{r}

x <- df

table(x$sex3)
x <- x[which(x$sex3!="other"),]
x$sex3 <- droplevels(x$sex3)

x$sex_01 <-  dplyr::recode(x$sex3,
               "male"="0"
              ,"female"="1")

model0 <- lmerTest::lmer(moral_identity_internal ~
                 #  sex_01
                 # * age
                  + (1|country)
                , data = x
                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )

model1 <- lmerTest::lmer(moral_identity_internal ~
                    sex_01
                 # * age
                  + (1|country)
                , data = x
               # , contrasts = list(sex_01 = contr.sum)
            )
summary(model1)
anova(model0,model1)

summary(model1)
anova(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)
summary_model1
results_coef <- as.data.frame(summary_model1$coefficients)
results_coef

aov1 <- anova(model1)

f3a <- aov1$`F value`[1]
p3a <- aov1$`Pr(>F)`[1]

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
t1 <- results_coef$`t value`[2]
p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)
```

```{r}

#### ensure correct data is loaded ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

#### remove any missing data #### 
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
table(x$country_name,x$sex3)
x$country_name

#### group by country ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

#### identify countries with small samples
male_length <- function(x){sum(x$sex3=='male')}
males <- lapply(x, male_length)
female_length <- function(x){sum(x$sex3=='female')}
females <- lapply(x, female_length)
names(females)

#### generate a vector containing all countries with less than 10 observations for either males or females ####
exclusions <- c(names(males[males<2]),
  names(females[females<2]))

#### re-load ungrouped data ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]

#### Filter out any countries to be excluded ####
x <- subset(x, !(country_name %in% exclusions))

#### group by country for analysis ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

ttest_fun <- function(x){
  t.test(moral_identity_internal ~ sex3, data = x)
}
all_t_tests <- lapply(x, ttest_fun)

means_fun <- function(x){
  mean(x$moral_identity_internal)
}
lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal)
}
lapply(x, sd_fun)

cohens_d_fun <- function(x){
  cohen.d(x$moral_identity_symbolic, x$sex3)
}
all_ds <- lapply(x, cohens_d_fun)
show_d_fun <- function(x){
  x$cohen.d[2]
}
ds_for_table <- lapply(all_ds, show_d_fun)

all_t_stats <- function(t){
  t$statistic
}
ts_for_table <- lapply(all_t_tests, all_t_stats)

all_t_df <- function(t){
  t$parameter
}
df_for_table <- lapply(all_t_tests, all_t_df)

all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), p_report)

total_sig <- sum(unlist(lapply(all_t_tests, all_t_ps))<.05)

#### means for Males ####
# re-load ungrouped data #
x <- df[which(df$sex3=="male"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
male_means <- lapply(x, means_fun)
male_sds <- lapply(x, sd_fun)

#### means for Females
# re-load ungrouped data #
x <- df[which(df$sex3=="female"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
female_means <- lapply(x, means_fun)
female_sds <- lapply(x, sd_fun)

```

We conducted a linear-mixed-effects model to test for gender differences in internalization when participants are nested within country. Our outcome measure was internalization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`), *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher internalization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`
, *p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in internalization across all countries. We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).

```{r}

x <- df

table(x$sex3)
x <- x[which(x$sex3!="other"),]
x$sex3 <- droplevels(x$sex3)

x$sex_01 <-  dplyr::recode(x$sex3,
               "male"="0"
              ,"female"="1")

model0 <- lmerTest::lmer(moral_identity_symbolic ~
                 #  sex_01
                 # * age
                  + (1|country)
                , data = x
                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    sex_01
                 # * age
                  + (1|country)
                , data = x
              #  , contrasts = list(sex_01 = contr.sum)
            )
summary(model1)
anova(model0,model1)

summary(model1)
anova(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)
summary_model1
results_coef <- as.data.frame(summary_model1$coefficients)
results_coef

aov1 <- anova(model1)

f3a <- aov1$`F value`[1]
p3a <- aov1$`Pr(>F)`[1]

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
t1 <- results_coef$`t value`[2]
p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)
```

```{r}

#### ensure correct data is loaded ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

#### remove any missing data #### 
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
table(x$country_name,x$sex3)
x$country_name

#### group by country ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

#### identify countries with small samples
male_length <- function(x){sum(x$sex3=='male')}
males <- lapply(x, male_length)
female_length <- function(x){sum(x$sex3=='female')}
females <- lapply(x, female_length)
names(females)

#### generate a vector containing all countries with less than 10 observations for either males or females ####
exclusions <- c(names(males[males<2]),
  names(females[females<2]))

#### re-load ungrouped data ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]

#### Filter out any countries to be excluded ####
x <- subset(x, !(country_name %in% exclusions))

#### group by country for analysis ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

ttest_fun <- function(x){
  t.test(moral_identity_symbolic ~ sex3, data = x)
}
all_t_tests <- lapply(x, ttest_fun)

means_fun <- function(x){
  mean(x$moral_identity_symbolic)
}
lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_symbolic)
}
lapply(x, sd_fun)

cohens_d_fun <- function(x){
  cohen.d(x$moral_identity_symbolic, x$sex3)
}
all_ds <- lapply(x, cohens_d_fun)
show_d_fun <- function(x){
  x$cohen.d[2]
}
ds_for_table <- lapply(all_ds, show_d_fun)

all_t_stats <- function(t){
  t$statistic
}
ts_for_table <- lapply(all_t_tests, all_t_stats)

all_t_df <- function(t){
  t$parameter
}
df_for_table <- lapply(all_t_tests, all_t_df)

all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), p_report)

total_sig <- sum(unlist(lapply(all_t_tests, all_t_ps))<.05)

#### means for Males ####
# re-load ungrouped data #
x <- df[which(df$sex3=="male"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
male_means <- lapply(x, means_fun)
male_sds <- lapply(x, sd_fun)

#### means for Females
# re-load ungrouped data #
x <- df[which(df$sex3=="female"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
female_means <- lapply(x, means_fun)
female_sds <- lapply(x, sd_fun)

```

We conducted another linear-mixed-effects model to test for gender differences in symbolization when participants are nested within country. Our outcome measure was symbolization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`), *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher symbolization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`
, *p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in symbolization across all countries. We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).

```{r internalizationPlot}

x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

df1 <- x

df1_male <- df1[which(df1$sex3=="male"),]
df1_female <- df1[which(df1$sex3=="female"),]

internal_mean_sd <- function(x){
  z <- x
  z$mean <- mean(z$moral_identity_internal, na.rm=T)
  z$sd <- sd(z$moral_identity_internal, na.rm=T)
  z
}

df1 <- rbind.data.frame(
  internal_mean_sd(df1_female),
  internal_mean_sd(df1_male)
)

df1$sex3 <- dplyr::recode(df1$sex3
                           , "male" = "Male"
                           , "female" = "Female")

g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
               position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=2)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl, 
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Internalization")+  
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

#g1
```

```{r symbolizationPlot}

symbolic_mean_sd <- function(x){
  z <- x
  z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
  z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
  z
}

df1 <- rbind.data.frame(
  symbolic_mean_sd(df1_female),
  symbolic_mean_sd(df1_male)
)

df1$sex3 <- dplyr::recode(df1$sex3
                           , "male" = "Male"
                           , "female" = "Female")

# df1 <- df
g2 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  #geom_quasirandom(size=.1)+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
               position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=2)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl, 
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Symbolization")+  
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

#g2
```

```{r, combinePlots, include=FALSE}
figure <- ggarrange(g1
                    , g2
                    #,labels = c("A")
                    , ncol = 1
                    , nrow = 2
                    #, widths = c(0.485, 0.5)
)
figure
```

```{r, meanSymbolizationGender,include=TRUE}
suppressWarnings(print(figure))

```

### symb

# Predictors (Individual Level Only)

## Internalization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    sex3
                 # * age
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

```

## Symbolization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    sex3
                  * age
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

```

# Predictors (Cultural Variables Included)

## Internalization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    sex3
                    * (age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG)
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

```

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_internal ~
                    sex3
                    + age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

```

## Symbolization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    sex3
                    * (age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG)
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

```

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_symbolic ~
                    sex3
                    + age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

```

# Men and Women Separately

## Men
### Internalization
```{r}
x <- df[
  which(
    df$sex3=="male"
        # |
        #   df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)
```

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

```

### Symbolization
```{r}
x <- df[
  which(
    df$sex3=="male"
        # |
        #   df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)
```

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

```

## Women
### Internalization

```{r}
x <- df[
  which(
    # df$sex3=="male"
    #     |
          df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

```

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

```

### Symbolization
```{r}
x <- df[
  which(
    # df$sex3=="male"
    #     |
          df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

```

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

```

### 2023-02-05 drafting_supplementary_analysis.Rmd
started drafting results section

--- 2023-02-05 drafting_results_section.Rmd
@@
 ---
-title: "Who Cares about Morality"
+title: "Supplementary Analyses"
 author: "Mariola Paruzel-Czachura, Cillian McHugh"
@@
 df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
-
-```
-
-```{r}
-
 ```
@@
 
-```{r}
-
-x <- df
-
-table(x$sex3)
-x <- x[which(x$sex3!="other"),]
-x$sex3 <- droplevels(x$sex3)
-
-t1 <- t.test(x$moral_identity_internal ~ x$sex3)
-d1 <- cohen.d(x$moral_identity_internal, x$sex3)
-
-d1$cohen.d[2]
-sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))
-sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))
-sprintf("%.2f",t1$parameter)
-sprintf("%.2f",t1$statistic)
-
-t2 <- t.test(x$moral_identity_symbolic ~ x$sex3)
-d2 <- cohen.d(x$moral_identity_symbolic, x$sex3)
-
-```
-
-Our first hypothesis was that women would have higher levels of internalization and symbolization than men.
-To test this we isolated the data for men and women from the main dataset.
-An independent samples t-test revealed that for the entire sample, women had higher internalization scores (*M* = `r sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))`), than men (*M* = `r sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='male')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='male')],na.rm=T))`), *t*(`r sprintf("%.2f",t1$parameter)`) = `r sprintf("%.2f",t1$statistic)`, *p* `r paste(p_report(t1$p.value))`, *d* = `r sprintf("%.2f", d1$cohen.d[2])`.
-Similarly, for symbolization, an independent samples t-test revealed that for the entire sample, women had higher scores (*M* = `r sprintf("%.1f",mean(x$moral_identity_symbolic[which(x$sex3=='female')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_symbolic[which(x$sex3=='female')],na.rm=T))`), than men (*M* = `r sprintf("%.1f",mean(x$moral_identity_symbolic[which(x$sex3=='male')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_symbolic[which(x$sex3=='male')],na.rm=T))`), *t*(`r sprintf("%.2f",t2$parameter)`) = `r sprintf("%.2f",t2$statistic)`, *p* `r paste(p_report(t2$p.value))`, *d* = `r sprintf("%.2f", d2$cohen.d[2])`.
-
-```{r}
-
-x <- df
-
-table(x$sex3)
-x <- x[which(x$sex3!="other"),]
-x$sex3 <- droplevels(x$sex3)
-
-x$sex_01 <-  dplyr::recode(x$sex3,
-               "male"="0"
-              ,"female"="1")
-
-model0 <- lmerTest::lmer(moral_identity_internal ~
-                 #  sex_01
-                 # * age
-                  + (1|country)
-                , data = x
-                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                    sex_01
-                 # * age
-                  + (1|country)
-                , data = x
-               # , contrasts = list(sex_01 = contr.sum)
-            )
-summary(model1)
-anova(model0,model1)
-
-summary(model1)
-anova(model1)
-results_anova <- as.data.frame(anova(model0,model1))
-results_anova
-results_anova$Chisq[2]
-results_anova$Df
-p1 <- results_anova$`Pr(>Chisq)`[2]
-p_report(p1)
-#p_report(results_anova$`Pr(>Chisq)`)[2]
-results_anova$AIC
-summary_model1 <- summary(model1)
-summary_model1
-results_coef <- as.data.frame(summary_model1$coefficients)
-results_coef
-
-aov1 <- anova(model1)
-
-f3a <- aov1$`F value`[1]
-p3a <- aov1$`Pr(>F)`[1]
-
-results_coef$Estimate[2]
-results_coef$`Std. Error`[2]
-results_coef$df[2]
-t1 <- results_coef$`t value`[2]
-p2 <- results_coef$`Pr(>|t|)`[2]
-
-#QuantPsyc::lm.beta(results_coef)
-anova(model1)
-```
-
-```{r}
+## Internalization
+
+```{r}
+
+ps <- function(y){
+  y <- round(y, digits = 3)
+  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
+  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
+        y, quote = FALSE)),"*"))
+  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
+        y)))}
 
@@
 
+# Means and Standard Deviations
 means_fun <- function(x){
@@
 
+N_fun <- function(x){
+  length(x$sex3)
+}
+total_Ns <- lapply(x, N_fun)
+
+# Statistics for table
+# Cohen's d
 cohens_d_fun <- function(x){
@@
 
+# t statistic
 all_t_stats <- function(t){
@@
 
+# df
 all_t_df <- function(t){
@@
 
+# p value
 all_t_ps <- function(t){
@@
 }
-ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), p_report)
-
-total_sig <- sum(unlist(lapply(all_t_tests, all_t_ps))<.05)
+ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)
+
+sum(unlist(lapply(all_t_tests, all_t_ps))<.05)
 
@@
 male_sds <- lapply(x, sd_fun)
+male_Ns <- lapply(x, N_fun)
 
@@
 female_sds <- lapply(x, sd_fun)
-
-```
-
-We conducted a linear-mixed-effects model to test for gender differences in internalization when participants are nested within country.
-Our outcome measure was internalization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
-Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
-$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`), *p* `r paste(p_report(p1))`. 
-There was a significant main effect for gender,
-*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
-`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
-with a significant positive association between being female and higher internalization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
-*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
-`r sprintf("%.2f",t1)`
-, *p* `r paste(p_report(p2))`.
-We conducted a series of independent-samples t-tests to test for gender differences in internalization across all countries.
-We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).
-
-```{r}
-
-x <- df
-
-table(x$sex3)
-x <- x[which(x$sex3!="other"),]
-x$sex3 <- droplevels(x$sex3)
-
-x$sex_01 <-  dplyr::recode(x$sex3,
-               "male"="0"
-              ,"female"="1")
-
-model0 <- lmerTest::lmer(moral_identity_symbolic ~
-                 #  sex_01
-                 # * age
-                  + (1|country)
-                , data = x
-                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                    sex_01
-                 # * age
-                  + (1|country)
-                , data = x
-              #  , contrasts = list(sex_01 = contr.sum)
-            )
-summary(model1)
-anova(model0,model1)
-
-summary(model1)
-anova(model1)
-results_anova <- as.data.frame(anova(model0,model1))
-results_anova
-results_anova$Chisq[2]
-results_anova$Df
-p1 <- results_anova$`Pr(>Chisq)`[2]
-p_report(p1)
-#p_report(results_anova$`Pr(>Chisq)`)[2]
-results_anova$AIC
-summary_model1 <- summary(model1)
-summary_model1
-results_coef <- as.data.frame(summary_model1$coefficients)
-results_coef
-
-aov1 <- anova(model1)
-
-f3a <- aov1$`F value`[1]
-p3a <- aov1$`Pr(>F)`[1]
-
-results_coef$Estimate[2]
-results_coef$`Std. Error`[2]
-results_coef$df[2]
-t1 <- results_coef$`t value`[2]
-p2 <- results_coef$`Pr(>|t|)`[2]
-
-#QuantPsyc::lm.beta(results_coef)
-anova(model1)
-```
-
-```{r}
+female_Ns <- lapply(x, N_fun)
+
+```
+
+### Internalization Ns
+
+```{r}
+#### Total Ns
+x <- df[which(df$sex3=="male"
+              |df$sex3=="female"
+              ),]
+x$sex3 <- droplevels(x$sex3)
+
+# and remove missing again
+sum(is.na(x$moral_identity_internal))
+x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+total_Ns <- lapply(x, N_fun)
+
+#### Ns for Males 
+# re-load ungrouped data #
+x <- df[which(df$sex3=="male"
+              #|df$sex3=="female"
+              ),]
+x$sex3 <- droplevels(x$sex3)
+
+# and remove missing again
+sum(is.na(x$moral_identity_internal))
+x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+male_Ns <- lapply(x, N_fun)
+
+#### Ns for Females
+# re-load ungrouped data #
+x <- df[which(df$sex3=="female"
+              #|df$sex3=="female"
+              ),]
+x$sex3 <- droplevels(x$sex3)
+# and remove missing again
+sum(is.na(x$moral_identity_internal))
+x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+female_Ns <- lapply(x, N_fun)
+
+test <- 
+  cbind.data.frame(do.call(rbind, total_Ns)
+                 ,do.call(rbind, female_Ns)
+                 ,do.call(rbind, male_Ns))
+
+test <- `colnames<-`(test, c("Total N","n Female","N male"))
+
+loop_exclusions_fun <- function(x){
+  if(rownames(test)[x] %in% exclusions) print(paste0(rownames(test)[x],"*"),quote = FALSE)
+  else print(rownames(test)[x])
+  }
+
+rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_exclusions_fun))
+test
+test <- test[order(rownames(test) ),]
+
+```
+
+```{r include=TRUE}
+
+apa_table(
+  test
+  , align = c("c", "c", "c")
+  , caption = "Total samples for each country for Internalization analysis"
+  , note = "* = sample too small to be included in analysis below")
+
+```
+
+### Internalization Table
+
+```{r}
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, female_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, male_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, ts_for_table),digits=2)
+    ,round(do.call(rbind, df_for_table),digits=2)
+    ,do.call(rbind, ps_for_table)
+    ,round(do.call(rbind, ds_for_table),digits=2)
+    )
+
+test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
+test
+
+x <- df[which(df$sex3=="male"
+              |df$sex3=="female"
+              ),]
+x$sex3 <- droplevels(x$sex3)
+
+# and remove missing again
+sum(is.na(x$moral_identity_internal))
+x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+total_Ns <- lapply(x, N_fun)
+
+P_R <- x$`Puerto Rico`
+P_R <- 
+  `rownames<-`(
+    `colnames<-`(
+      as.data.frame(
+        rbind(
+          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
+          # ,
+          c(
+            P_R$moral_identity_internal[which(P_R$sex3=="male")]
+            ,"-"
+            ,P_R$moral_identity_internal[which(P_R$sex3=="female")]
+            ,"-"
+            ,"-"
+            ,"-"
+            ,"-"
+            ,"-"))),
+      c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
+    ,c("Peurto Rico"))
+
+test <- rbind(test[1:49,],P_R,test[50:length(test$`mean F`),])
+test <- test[order(rownames(test) ),]
+
+```
+
+```{r include=TRUE}
+
+apa_table(
+  test
+  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
+  , caption = "Gender differences in Internalization for each Country"
+  , note = "* = sig. at p < .05; ** = sig. at p < .001")
+
+```
+
+## Symbolization
+
+```{r}
+
+ps <- function(y){
+  y <- round(y, digits = 3)
+  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
+  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
+        y, quote = FALSE)),"*"))
+  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
+        y)))}
 
@@
 }
-ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), p_report)
+ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)
 
@@
 
-We conducted another linear-mixed-effects model to test for gender differences in symbolization when participants are nested within country.
-Our outcome measure was symbolization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
-Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
-$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`), *p* `r paste(p_report(p1))`. 
-There was a significant main effect for gender,
-*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
-`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
-with a significant positive association between being female and higher symbolization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
-*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
-`r sprintf("%.2f",t1)`
-, *p* `r paste(p_report(p2))`.
-We conducted a series of independent-samples t-tests to test for gender differences in symbolization across all countries.
-We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).
-
-```{r internalizationPlot}
-
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-df1 <- x
-
-df1_male <- df1[which(df1$sex3=="male"),]
-df1_female <- df1[which(df1$sex3=="female"),]
-
-internal_mean_sd <- function(x){
-  z <- x
-  z$mean <- mean(z$moral_identity_internal, na.rm=T)
-  z$sd <- sd(z$moral_identity_internal, na.rm=T)
-  z
-}
-
-df1 <- rbind.data.frame(
-  internal_mean_sd(df1_female),
-  internal_mean_sd(df1_male)
-)
-
-df1$sex3 <- dplyr::recode(df1$sex3
-                           , "male" = "Male"
-                           , "female" = "Female")
-
-g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
-  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
-  geom_violin(fill = NA) +
+### Symbolization Ns
+
+```{r}
+#### Total Ns
+x <- df[which(df$sex3=="male"
+              |df$sex3=="female"
+              ),]
+x$sex3 <- droplevels(x$sex3)
+
+# and remove missing again
+sum(is.na(x$moral_identity_symbolic))
+x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+total_Ns <- lapply(x, N_fun)
+
+#### Ns for Males 
+# re-load ungrouped data #
+x <- df[which(df$sex3=="male"
+              #|df$sex3=="female"
+              ),]
+x$sex3 <- droplevels(x$sex3)
+
+# and remove missing again
+sum(is.na(x$moral_identity_symbolic))
+x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+male_Ns <- lapply(x, N_fun)
+
+#### Ns for Females
+# re-load ungrouped data #
+x <- df[which(df$sex3=="female"
+              #|df$sex3=="female"
+              ),]
+x$sex3 <- droplevels(x$sex3)
+# and remove missing again
+sum(is.na(x$moral_identity_symbolic))
+x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+female_Ns <- lapply(x, N_fun)
+
+test <- 
+  cbind.data.frame(do.call(rbind, total_Ns)
+                 ,do.call(rbind, female_Ns)
+                 ,do.call(rbind, male_Ns))
+
+test <- `colnames<-`(test, c("Total N","n Female","N male"))
+
+loop_exclusions_fun <- function(x){
+  if(rownames(test)[x] %in% exclusions) print(paste0(rownames(test)[x],"*"),quote = FALSE)
+  else print(rownames(test)[x])
+  }
+
+rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_exclusions_fun))
+test
+test <- test[order(rownames(test) ),]
+
+```
+
+```{r include=TRUE}
+
+apa_table(
+  test
+  , align = c("c", "c", "c")
+  , caption = "Total samples for each country for Symbolization analysis"
+  , note = "* = sample too small to be included in analysis below")
+
+```
+
+### Symbolization Table
+
+```{r}
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, female_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, male_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, ts_for_table),digits=2)
+    ,round(do.call(rbind, df_for_table),digits=2)
+    ,do.call(rbind, ps_for_table)
+    ,round(do.call(rbind, ds_for_table),digits=2)
+    )
+
+test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
+test
+
+x <- df[which(df$sex3=="male"
+              |df$sex3=="female"
+              ),]
+x$sex3 <- droplevels(x$sex3)
+
+# and remove missing again
+sum(is.na(x$moral_identity_symbolic))
+x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+total_Ns <- lapply(x, N_fun)
+
+P_R <- x$`Puerto Rico`
+P_R <- 
+  `rownames<-`(
+    `colnames<-`(
+      as.data.frame(
+        rbind(
+          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
+          # ,
+          c(
+            P_R$moral_identity_symbolic[which(P_R$sex3=="male")]
+            ,"-"
+            ,P_R$moral_identity_symbolic[which(P_R$sex3=="female")]
+            ,"-"
+            ,"-"
+            ,"-"
+            ,"-"
+            ,"-"))),
+      c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
+    ,c("Peurto Rico"))
+
+test <- rbind(test[1:49,],P_R,test[50:length(test$`mean F`),])
+test <- test[order(rownames(test) ),]
+
+```
+
+```{r include=TRUE}
+
+apa_table(
+  test
+  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
+  , caption = "Gender differences in Symbolization for each Country"
+  , note = "* = sig. at p < .05; ** = sig. at p < .001")
+
+```
+
+# Overview
+
+# Testing for Country Effects
+
+## Internalization
+
+```{r}
+
+# start building the model
+## first test if country should be included
+
+# no country
+interceptOnly <-gls(moral_identity_internal ~ 1
+                    , data = df
+                    , method = "ML"
+                    , na.action = na.exclude)
+summary(interceptOnly)
+
+# country included
+randomInterceptOnly <-lme(moral_identity_internal ~ 1
+                          , data = df
+                          , random = ~1|country
+                          , method = "ML"
+                          , na.action = na.exclude)
+summary(randomInterceptOnly)
+
+LL_d <- logLik(interceptOnly)*-2 - logLik(randomInterceptOnly)*-2
+aov <- anova(interceptOnly, randomInterceptOnly)
+country_p <- aov$`p-value`[2]
+
+```
+
+Initial testing revealed that for Internalization, allowing intercepts to vary with Country significantly improved the predictive power of the model $\chi$^2^(`r round(aov$df[2]-aov$df[1], digits=2)`) = `r round(aov$L.Ratio[2],digits=2)`, *p* `r paste(p_report(country_p))`.
+
+```{r}
+test <- 
+  do.call(
+    rbind,
+    tapply(df$moral_identity_internal, df$ISO3, descriptives)
+    )
+
+descriptives(df$moral_identity_internal)
+
+test[order(-test$mean), ]
+country_order <- rownames(test[order(-test$mean), ])
+```
+
+```{r, internalizationCountry, include=TRUE}
+apa_table(
+  test
+  , caption = "Internalization basic descriptives by Country")
+```
+
+```{r}
+# https://www.r-bloggers.com/2019/03/all-around-the-world-maps-and-flags-in-r/
+df$flag_location <- rep(-1)
+
+test1 <- test[order(-test$mean), ]
+test1$country1 <- rownames(test1)
+test1$position <- c(11:(10+length(test1$country1)))
+test1$ISO3 <- test1$country1
+test1$position_country <- paste0(test1$position,test1$country1)
+df1 <- left_join(df, test1, by = "ISO3")
+```
+
+```{r}
+
+g <- ggplot(df1,aes(x=position_country,y=moral_identity_internal))+
+  #geom_violin() +
+  stat_summary(fun=mean, geom="point", shape=23, size=2)+
+  geom_boxplot(width=0.1, outlier.shape = NA)+
+  xlab("Country")+
+  ylab("Internalization")+
+  geom_jitter(shape=16, position=position_jitter(0.15), size=.1, color="dark grey")+
+  geom_axis_flags(breaks = df1$position_country,
+                   labels = df1$ISO3,
+                   country_icons = df1$ISO3,
+                   axis = "x",
+                    width = 20,
+                   # lineheight = 2,
+                   # fontface = "bold"
+  )
+```
+
+<div class=superbigimage>
+```{r, meanInternalization,include=TRUE,fig.width=20,fig.height=6}
+suppressWarnings(print(g))
+
+```
+
+</div>
+## Symbolization
+
+```{r}
+# 
+# # start building the model
+# ## first test if country should be included
+# 
+# # no country
+# interceptOnly <-gls(moral_identity_symbolic ~ 1
+#                     , data = df
+#                     , method = "ML"
+#                     , na.action = na.exclude)
+# summary(interceptOnly)
+# 
+# # country included
+# randomInterceptOnly <-lme(moral_identity_symbolic ~ 1
+#                           , data = df
+#                           , random = ~1|country
+#                           , method = "ML"
+#                           , na.action = na.exclude)
+# summary(randomInterceptOnly)
+# 
+# LL_d <- logLik(interceptOnly)*-2 - logLik(randomInterceptOnly)*-2
+# aov <- anova(interceptOnly, randomInterceptOnly)
+# country_p <- aov$`p-value`[2]
+
+```
+
+Initial testing revealed that for Symbolization, allowing intercepts to vary with Country significantly improved the predictive power of the model $\chi$^2^(`r round(aov$df[2]-aov$df[1], digits=2)`) = `r round(aov$L.Ratio[2],digits=2)`, *p* `r paste(p_report(country_p))`.
+
+```{r}
+test <- 
+  do.call(
+    rbind,
+    tapply(df$moral_identity_symbolic, df$ISO3, descriptives)
+    )
+
+descriptives(df$moral_identity_symbolic)
+
+test[order(-test$mean), ]
+country_order <- rownames(test[order(-test$mean), ])
+```
+
+```{r, symbolizationCountry, include=TRUE}
+apa_table(
+  test
+  , caption = "Symbolization basic descriptives by Country")
+```
+
+```{r}
+# https://www.r-bloggers.com/2019/03/all-around-the-world-maps-and-flags-in-r/
+df$flag_location <- rep(-1)
+
+test1 <- test[order(-test$mean), ]
+test1$country1 <- rownames(test1)
+test1$position <- c(11:(10+length(test1$country1)))
+test1$ISO3 <- test1$country1
+test1$position_country <- paste0(test1$position,test1$country1)
+df1 <- left_join(df, test1, by = "ISO3")
+```
+
+```{r}
+
+g <- ggplot(df1,aes(x=position_country,y=moral_identity_symbolic))+
+  #geom_violin() +
+  stat_summary(fun=mean, geom="point", shape=23, size=2)+
+  geom_boxplot(width=0.1, outlier.shape = NA)+
+  xlab("Country")+
+  ylab("Symbolization")+
+  geom_jitter(shape=16, position=position_jitter(0.15), size=.1, color="dark grey")+
+  geom_axis_flags(breaks = df1$position_country,
+                   labels = df1$ISO3,
+                   country_icons = df1$ISO3,
+                   axis = "x",
+                    width = 20,
+                   # lineheight = 2,
+                   # fontface = "bold"
+  )
+```
+
+<div class=superbigimage>
+```{r, meanSymbolization,include=TRUE,fig.width=20,fig.height=6}
+suppressWarnings(print(g))
+
+```
+
+</div>
+
+# Gender Differences
+
+```{r}
+test <- 
+  do.call(
+    rbind,
+    tapply(df$moral_identity_internal, df$sex3, descriptives)
+    )
+
+descriptives(df$moral_identity_internal)
+
+test[order(-test$mean), ]
+country_order <- rownames(test[order(-test$mean), ])
+```
+
+```{r, internalizationgender, include=TRUE}
+apa_table(
+  test
+  , caption = "Internalization basic descriptives by Gender")
+```
+
+```{r}
+df1 <- df
+g <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
+  geom_violin() +
   #ggforce::geom_sina(size=.01)+
-  # geom_sina(shape=16
-  #           , position=position_jitter(height=.25,width=0)
-  #           , size=.000001
-  #           , color="dark grey"
-  #           ,jitter_y=F
-  # )+
-  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
-  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
-               position=position_dodge(0.05), color="#5a5a5a")+
-  stat_summary(fun=mean, geom="point", shape=16, size=2)+
-  # stat_summary(geom = "linerange",
-  #   fun.data = mean_sdl, 
-  #   fun.args = list(mult = 1),
-  #   colour = "black"
-  # )+
+  stat_summary(fun=mean, geom="point", shape=23, size=2)+
+  geom_boxplot(width=0.1, outlier.shape = NA)+
   xlab("Gender")+
   ylab("Internalization")+  
-  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-  theme_bw() +
-  theme(panel.border = element_blank(),
-        axis.line = element_line(size = .2),
-        strip.background  = element_blank(),
-        panel.grid = element_blank(),
-        plot.title=element_text(#family="Times",
-          size=12
-        ),
-        #legend.position="right",
-        legend.text=element_text(#family="Times",
-          size=8
-        ),
-        legend.title=element_text(#family="Times",
-          size=10
-        ),
-        axis.text=element_text(#family="Times",
-          colour = "black",
-          size=8
-        ),
-        axis.ticks.x = element_blank(),
-        axis.title=element_text(#family="Times",
-          size=12
-        ),
-        strip.text=element_text(#family = "Times",
-          size = 12
-        ),
-        # strip.background = element_rect(fill = "white"),
-        legend.position="none")
-
-#g1
-```
-
-```{r symbolizationPlot}
-
-symbolic_mean_sd <- function(x){
-  z <- x
-  z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
-  z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
-  z
-}
-
-df1 <- rbind.data.frame(
-  symbolic_mean_sd(df1_female),
-  symbolic_mean_sd(df1_male)
-)
-
-df1$sex3 <- dplyr::recode(df1$sex3
-                           , "male" = "Male"
-                           , "female" = "Female")
-
-# df1 <- df
-g2 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
-  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
-  geom_violin(fill = NA) +
+  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
+
+g
+```
+
+```{r, meanInternalizationGender,include=TRUE}
+suppressWarnings(print(g))
+
+```
+
+```{r}
+test <- 
+  do.call(
+    rbind,
+    tapply(df$moral_identity_symbolic, df$sex3, descriptives)
+    )
+
+descriptives(df$moral_identity_symbolic)
+
+test[order(-test$mean), ]
+country_order <- rownames(test[order(-test$mean), ])
+```
+
+```{r, symbolizationgender, include=TRUE}
+apa_table(
+  test
+  , caption = "Symbolization basic descriptives by Gender")
+```
+
+```{r}
+df1 <- df
+g <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
+  geom_violin() +
   #ggforce::geom_sina(size=.01)+
-  # geom_sina(shape=16
-  #           , position=position_jitter(height=.25,width=0)
-  #           , size=.000001
-  #           , color="dark grey"
-  #           ,jitter_y=F
-  # )+
-  #geom_quasirandom(size=.1)+
-  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
-  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
-               position=position_dodge(0.05), color="#5a5a5a")+
-  stat_summary(fun=mean, geom="point", shape=16, size=2)+
-  # stat_summary(geom = "linerange",
-  #   fun.data = mean_sdl, 
-  #   fun.args = list(mult = 1),
-  #   colour = "black"
-  # )+
+  stat_summary(fun=mean, geom="point", shape=23, size=2)+
+  geom_boxplot(width=0.1, outlier.shape = NA)+
   xlab("Gender")+
   ylab("Symbolization")+  
-  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-  theme_bw() +
-  theme(panel.border = element_blank(),
-        axis.line = element_line(size = .2),
-        strip.background  = element_blank(),
-        panel.grid = element_blank(),
-        plot.title=element_text(#family="Times",
-          size=12
-        ),
-        #legend.position="right",
-        legend.text=element_text(#family="Times",
-          size=8
-        ),
-        legend.title=element_text(#family="Times",
-          size=10
-        ),
-        axis.text=element_text(#family="Times",
-          colour = "black",
-          size=8
-        ),
-        axis.ticks.x = element_blank(),
-        axis.title=element_text(#family="Times",
-          size=12
-        ),
-        strip.text=element_text(#family = "Times",
-          size = 12
-        ),
-        # strip.background = element_rect(fill = "white"),
-        legend.position="none")
-
-#g2
-```
-
-```{r, combinePlots, include=FALSE}
-figure <- ggarrange(g1
-                    , g2
-                    #,labels = c("A")
-                    , ncol = 1
-                    , nrow = 2
-                    #, widths = c(0.485, 0.5)
-)
-figure
+  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
+
+g
 ```
@@
 ```{r, meanSymbolizationGender,include=TRUE}
-suppressWarnings(print(figure))
-
-```
-
-### symb
+suppressWarnings(print(g))
+
+```
 
@@
                     sex3
-                 # * age
+                  * age
                   + (1|country)

### 2023-02-05 drafting_results_section.Rmd
added plots

@@
 Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
-$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`), *p* `r paste(p_report(p1))`. 
+$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
 There was a significant main effect for gender,
@@
 Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
-$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`), *p* `r paste(p_report(p1))`. 
+$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
 There was a significant main effect for gender,
@@
 
+x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+x$sex3 <- droplevels(x$sex3)
+
+df1 <- x
+
 symbolic_mean_sd <- function(x){
@@
 ```
-
-### symb
-
-# Predictors (Individual Level Only)
-
-## Internalization
-```{r}
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                    sex3
-                 # * age
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-## Symbolization
-```{r}
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                    sex3
-                  * age
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-# Predictors (Cultural Variables Included)
-
-## Internalization
-```{r}
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                    sex3
-                    * (age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG)
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_internal ~
-                    sex3
-                    + age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
-
-## Symbolization
-```{r}
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                    sex3
-                    * (age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG)
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_symbolic ~
-                    sex3
-                    + age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
-
-# Men and Women Separately
-
-## Men
-### Internalization
-```{r}
-x <- df[
-  which(
-    df$sex3=="male"
-        # |
-        #   df$sex3=="female"
-          ),]
-
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_internal ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
-
-### Symbolization
-```{r}
-x <- df[
-  which(
-    df$sex3=="male"
-        # |
-        #   df$sex3=="female"
-          ),]
-
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_symbolic ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
-
-## Women
-### Internalization
-
-```{r}
-x <- df[
-  which(
-    # df$sex3=="male"
-    #     |
-          df$sex3=="female"
-          ),]
-
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_internal ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
-
-### Symbolization
-```{r}
-x <- df[
-  which(
-    # df$sex3=="male"
-    #     |
-          df$sex3=="female"
-          ),]
-
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_symbolic ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```

### 2023-02-05 drafting_supplementary_analysis.Rmd
added plots

@@
       c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
-    ,c("Peurto Rico"))
+    ,c("Puerto Rico"))
 
@@
 ```
+
+### Internalization Plot
+
+```{r internalizationPlot}
+
+# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+# x$sex3 <- droplevels(x$sex3)
+# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+# 
+# #### identify countries with small samples
+# male_length <- function(x){sum(x$sex3=='male')}
+# males <- lapply(x, male_length)
+# female_length <- function(x){sum(x$sex3=='female')}
+# females <- lapply(x, female_length)
+# names(females)
+# 
+# #### generate a vector containing all countries with less than 10 observations for either males or females ####
+# exclusions <- c(names(males[males<2]),
+#   names(females[females<2]))
+# 
+# #### re-load ungrouped data ####
+# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+# x$sex3 <- droplevels(x$sex3)
+# 
+# # and remove missing again
+# sum(is.na(x$moral_identity_internal))
+# x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+# 
+# #### Filter out any countries to be excluded ####
+# x <- subset(x, !(country_name %in% exclusions))
+# 
+# df1 <- x
+# 
+# df1_male <- df1[which(df1$sex3=="male"),]
+# df1_female <- df1[which(df1$sex3=="female"),]
+# 
+# internal_mean_sd <- function(x){
+#   z <- x
+#   z$mean <- mean(z$moral_identity_internal, na.rm=T)
+#   z$sd <- sd(z$moral_identity_internal, na.rm=T)
+#   z
+# }
+# 
+# 
+# df1 <- rbind.data.frame(
+#   internal_mean_sd(df1_female),
+#   internal_mean_sd(df1_male)
+# )
+# 
+# df1$sex3 <- dplyr::recode(df1$sex3
+#                            , "male" = "Male"
+#                            , "female" = "Female")
+# 
+# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
+#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") + 
+#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="lightgrey")+
+#   geom_violin(fill = NA) +
+#   #ggforce::geom_sina(size=.01)+
+#   # geom_sina(shape=16
+#   #           , position=position_jitter(height=.25,width=0)
+#   #           , size=.000001
+#   #           , color="dark grey"
+#   #           ,jitter_y=F
+#   # )+
+#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
+#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
+#                 position=position_dodge(0.05), color="#5a5a5a")+
+#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
+#   # stat_summary(geom = "linerange",
+#   #   fun.data = mean_sdl, 
+#   #   fun.args = list(mult = 1),
+#   #   colour = "black"
+#   # )+
+#   xlab("Gender")+
+#   ylab("Internalization")+  
+#   facet_wrap(~df1$ISO3, ncol = 9 )+
+#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
+#   theme_bw() +
+#   theme(panel.border = element_blank(),
+#         axis.line = element_line(size = .2),
+#         strip.background  = element_blank(),
+#         panel.grid = element_blank(),
+#         plot.title=element_text(#family="Times",
+#           size=12
+#         ),
+#         #legend.position="right",
+#         legend.text=element_text(#family="Times",
+#           size=8
+#         ),
+#         legend.title=element_text(#family="Times",
+#           size=10
+#         ),
+#         axis.text=element_text(#family="Times",
+#           colour = "black",
+#           size=8
+#         ),
+#         axis.ticks.x = element_blank(),
+#         axis.title=element_text(#family="Times",
+#           size=12
+#         ),
+#         strip.text=element_text(#family = "Times",
+#           size = 12
+#         ),
+#         # strip.background = element_rect(fill = "white"),
+#         legend.position="none")
+# 
+# ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
+
+```
+
+```{r, InternalizationGender,fig.cap="Gender differences in Internalization for each country",include=TRUE}
+#suppressWarnings(print(g1))
+
+```
+
+<style>
+#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
+#scaled-frame { width: 250%; height: 900px; border: 1px; }
+#scaled-frame {
+    zoom: 0.50;
+    -moz-transform: scale(0.50);
+    -moz-transform-origin: 0 0;
+    -o-transform: scale(0.50);
+    -o-transform-origin: 0 0;
+    -webkit-transform: scale(0.50);
+    -webkit-transform-origin: 0 0;
+}
+
+@media screen and (-webkit-min-device-pixel-ratio:0) {
+ #scaled-frame  { zoom: 1;  }
+}
+</style>
+
+<div id="wrapper"><iframe id="scaled-frame" src="plots/internalization.png"></iframe></div>
 
@@
 test
-test <- test[order(rownames(test) ),]
+#test <-
+test[order(rownames(test) ),]
 
@@
 
-# Overview
-
-# Testing for Country Effects
-
-## Internalization
-
-```{r}
-
-# start building the model
-## first test if country should be included
-
-# no country
-interceptOnly <-gls(moral_identity_internal ~ 1
-                    , data = df
-                    , method = "ML"
-                    , na.action = na.exclude)
-summary(interceptOnly)
-
-# country included
-randomInterceptOnly <-lme(moral_identity_internal ~ 1
-                          , data = df
-                          , random = ~1|country
-                          , method = "ML"
-                          , na.action = na.exclude)
-summary(randomInterceptOnly)
-
-LL_d <- logLik(interceptOnly)*-2 - logLik(randomInterceptOnly)*-2
-aov <- anova(interceptOnly, randomInterceptOnly)
-country_p <- aov$`p-value`[2]
-
-```
-
-Initial testing revealed that for Internalization, allowing intercepts to vary with Country significantly improved the predictive power of the model $\chi$^2^(`r round(aov$df[2]-aov$df[1], digits=2)`) = `r round(aov$L.Ratio[2],digits=2)`, *p* `r paste(p_report(country_p))`.
-
-```{r}
-test <- 
-  do.call(
-    rbind,
-    tapply(df$moral_identity_internal, df$ISO3, descriptives)
-    )
-
-descriptives(df$moral_identity_internal)
-
-test[order(-test$mean), ]
-country_order <- rownames(test[order(-test$mean), ])
-```
-
-```{r, internalizationCountry, include=TRUE}
-apa_table(
-  test
-  , caption = "Internalization basic descriptives by Country")
-```
-
-```{r}
-# https://www.r-bloggers.com/2019/03/all-around-the-world-maps-and-flags-in-r/
-df$flag_location <- rep(-1)
-
-test1 <- test[order(-test$mean), ]
-test1$country1 <- rownames(test1)
-test1$position <- c(11:(10+length(test1$country1)))
-test1$ISO3 <- test1$country1
-test1$position_country <- paste0(test1$position,test1$country1)
-df1 <- left_join(df, test1, by = "ISO3")
-```
-
-```{r}
-
-g <- ggplot(df1,aes(x=position_country,y=moral_identity_internal))+
-  #geom_violin() +
-  stat_summary(fun=mean, geom="point", shape=23, size=2)+
-  geom_boxplot(width=0.1, outlier.shape = NA)+
-  xlab("Country")+
-  ylab("Internalization")+
-  geom_jitter(shape=16, position=position_jitter(0.15), size=.1, color="dark grey")+
-  geom_axis_flags(breaks = df1$position_country,
-                   labels = df1$ISO3,
-                   country_icons = df1$ISO3,
-                   axis = "x",
-                    width = 20,
-                   # lineheight = 2,
-                   # fontface = "bold"
-  )
-```
-
-<div class=superbigimage>
-```{r, meanInternalization,include=TRUE,fig.width=20,fig.height=6}
-suppressWarnings(print(g))
-
-```
-
-</div>
-## Symbolization
-
-```{r}
-# 
-# # start building the model
-# ## first test if country should be included
-# 
-# # no country
-# interceptOnly <-gls(moral_identity_symbolic ~ 1
-#                     , data = df
-#                     , method = "ML"
-#                     , na.action = na.exclude)
-# summary(interceptOnly)
-# 
-# # country included
-# randomInterceptOnly <-lme(moral_identity_symbolic ~ 1
-#                           , data = df
-#                           , random = ~1|country
-#                           , method = "ML"
-#                           , na.action = na.exclude)
-# summary(randomInterceptOnly)
-# 
-# LL_d <- logLik(interceptOnly)*-2 - logLik(randomInterceptOnly)*-2
-# aov <- anova(interceptOnly, randomInterceptOnly)
-# country_p <- aov$`p-value`[2]
-
-```
-
-Initial testing revealed that for Symbolization, allowing intercepts to vary with Country significantly improved the predictive power of the model $\chi$^2^(`r round(aov$df[2]-aov$df[1], digits=2)`) = `r round(aov$L.Ratio[2],digits=2)`, *p* `r paste(p_report(country_p))`.
-
-```{r}
-test <- 
-  do.call(
-    rbind,
-    tapply(df$moral_identity_symbolic, df$ISO3, descriptives)
-    )
-
-descriptives(df$moral_identity_symbolic)
-
-test[order(-test$mean), ]
-country_order <- rownames(test[order(-test$mean), ])
-```
-
-```{r, symbolizationCountry, include=TRUE}
-apa_table(
-  test
-  , caption = "Symbolization basic descriptives by Country")
-```
-
-```{r}
-# https://www.r-bloggers.com/2019/03/all-around-the-world-maps-and-flags-in-r/
-df$flag_location <- rep(-1)
-
-test1 <- test[order(-test$mean), ]
-test1$country1 <- rownames(test1)
-test1$position <- c(11:(10+length(test1$country1)))
-test1$ISO3 <- test1$country1
-test1$position_country <- paste0(test1$position,test1$country1)
-df1 <- left_join(df, test1, by = "ISO3")
-```
-
-```{r}
-
-g <- ggplot(df1,aes(x=position_country,y=moral_identity_symbolic))+
-  #geom_violin() +
-  stat_summary(fun=mean, geom="point", shape=23, size=2)+
-  geom_boxplot(width=0.1, outlier.shape = NA)+
-  xlab("Country")+
-  ylab("Symbolization")+
-  geom_jitter(shape=16, position=position_jitter(0.15), size=.1, color="dark grey")+
-  geom_axis_flags(breaks = df1$position_country,
-                   labels = df1$ISO3,
-                   country_icons = df1$ISO3,
-                   axis = "x",
-                    width = 20,
-                   # lineheight = 2,
-                   # fontface = "bold"
-  )
-```
-
-<div class=superbigimage>
-```{r, meanSymbolization,include=TRUE,fig.width=20,fig.height=6}
-suppressWarnings(print(g))
-
-```
-
-</div>
-
-# Gender Differences
-
-```{r}
-test <- 
-  do.call(
-    rbind,
-    tapply(df$moral_identity_internal, df$sex3, descriptives)
-    )
-
-descriptives(df$moral_identity_internal)
-
-test[order(-test$mean), ]
-country_order <- rownames(test[order(-test$mean), ])
-```
-
-```{r, internalizationgender, include=TRUE}
-apa_table(
-  test
-  , caption = "Internalization basic descriptives by Gender")
-```
-
-```{r}
-df1 <- df
-g <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
-  geom_violin() +
-  #ggforce::geom_sina(size=.01)+
-  stat_summary(fun=mean, geom="point", shape=23, size=2)+
-  geom_boxplot(width=0.1, outlier.shape = NA)+
-  xlab("Gender")+
-  ylab("Internalization")+  
-  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-
-g
-```
-
-```{r, meanInternalizationGender,include=TRUE}
-suppressWarnings(print(g))
-
-```
-
-```{r}
-test <- 
-  do.call(
-    rbind,
-    tapply(df$moral_identity_symbolic, df$sex3, descriptives)
-    )
-
-descriptives(df$moral_identity_symbolic)
-
-test[order(-test$mean), ]
-country_order <- rownames(test[order(-test$mean), ])
-```
-
-```{r, symbolizationgender, include=TRUE}
-apa_table(
-  test
-  , caption = "Symbolization basic descriptives by Gender")
-```
-
-```{r}
-df1 <- df
-g <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
-  geom_violin() +
-  #ggforce::geom_sina(size=.01)+
-  stat_summary(fun=mean, geom="point", shape=23, size=2)+
-  geom_boxplot(width=0.1, outlier.shape = NA)+
-  xlab("Gender")+
-  ylab("Symbolization")+  
-  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-
-g
-```
-
-```{r, meanSymbolizationGender,include=TRUE}
-suppressWarnings(print(g))
-
-```
-
-# Predictors (Individual Level Only)
-
-## Internalization
-```{r}
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                    sex3
-                  * age
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-## Symbolization
-```{r}
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                    sex3
-                  * age
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-# Predictors (Cultural Variables Included)
-
-## Internalization
-```{r}
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                    sex3
-                    * (age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG)
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_internal ~
-                    sex3
-                    + age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
-
-## Symbolization
-```{r}
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                    sex3
-                    * (age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG)
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_symbolic ~
-                    sex3
-                    + age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
-
-# Men and Women Separately
-
-## Men
-### Internalization
-```{r}
-x <- df[
-  which(
-    df$sex3=="male"
-        # |
-        #   df$sex3=="female"
-          ),]
-
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_internal ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
-
-### Symbolization
-```{r}
-x <- df[
-  which(
-    df$sex3=="male"
-        # |
-        #   df$sex3=="female"
-          ),]
-
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_symbolic ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
-
-## Women
-### Internalization
-
-```{r}
-x <- df[
-  which(
-    # df$sex3=="male"
-    #     |
-          df$sex3=="female"
-          ),]
-
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_internal ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
-
-### Symbolization
-```{r}
-x <- df[
-  which(
-    # df$sex3=="male"
-    #     |
-          df$sex3=="female"
-          ),]
-
-x$sex3 <- droplevels(x$sex3)
-```
-
-```{r, include=TRUE, echo=TRUE}
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                  + (1|country)
-                , data = x
-                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-summary(model1)
-anova(model1)
-
-```
-
-#### (Regular Regression)
-
-We also ran a regression without allowing slopes to vary by country. Results are below:
-
-```{r, include=TRUE, echo=TRUE}
-
-fit <- lm(moral_identity_symbolic ~
-                    age
-                    + Power.Distance
-                    + Individualism
-                    + Masculinity
-                    + Uncertainty.Avoidance
-                    + Long.Term.Orientation
-                    + Indulgence
-                    + CTL_C
-                    + CTL_DS
-                    + CTL_DG
-                , data = x
-            )
-
-summary(fit)
-
-```
+### Symbolization Plot
+
+```{r symbolizationPlot}
+
+# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+# x$sex3 <- droplevels(x$sex3)
+# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+# 
+# #### identify countries with small samples
+# male_length <- function(x){sum(x$sex3=='male')}
+# males <- lapply(x, male_length)
+# female_length <- function(x){sum(x$sex3=='female')}
+# females <- lapply(x, female_length)
+# names(females)
+# 
+# #### generate a vector containing all countries with less than 10 observations for either males or females ####
+# exclusions <- c(names(males[males<2]),
+#   names(females[females<2]))
+# 
+# #### re-load ungrouped data ####
+# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+# x$sex3 <- droplevels(x$sex3)
+# 
+# # and remove missing again
+# sum(is.na(x$moral_identity_symbolic))
+# x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
+# 
+# #### Filter out any countries to be excluded ####
+# x <- subset(x, !(country_name %in% exclusions))
+# 
+# df1 <- x
+# 
+# df1_male <- df1[which(df1$sex3=="male"),]
+# df1_female <- df1[which(df1$sex3=="female"),]
+# 
+# internal_mean_sd <- function(x){
+#   z <- x
+#   z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
+#   z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
+#   z
+# }
+# 
+# 
+# df1 <- rbind.data.frame(
+#   internal_mean_sd(df1_female),
+#   internal_mean_sd(df1_male)
+# )
+# 
+# df1$sex3 <- dplyr::recode(df1$sex3
+#                            , "male" = "Male"
+#                            , "female" = "Female")
+# 
+# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
+#   geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
+#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
+#   geom_violin(fill = NA) +
+#   #ggforce::geom_sina(size=.01)+
+#   # geom_sina(shape=16
+#   #           , position=position_jitter(height=.25,width=0)
+#   #           , size=.000001
+#   #           , color="dark grey"
+#   #           ,jitter_y=F
+#   # )+
+#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
+#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
+#                 position=position_dodge(0.05), color="#5a5a5a")+
+#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
+#   # stat_summary(geom = "linerange",
+#   #   fun.data = mean_sdl,
+#   #   fun.args = list(mult = 1),
+#   #   colour = "black"
+#   # )+
+#   xlab("Gender")+
+#   ylab("Internalization")+
+#   facet_wrap(~df1$ISO3, ncol = 9 )+
+#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
+#   theme_bw() +
+#   theme(panel.border = element_blank(),
+#         axis.line = element_line(size = .2),
+#         strip.background  = element_blank(),
+#         panel.grid = element_blank(),
+#         plot.title=element_text(#family="Times",
+#           size=12
+#         ),
+#         #legend.position="right",
+#         legend.text=element_text(#family="Times",
+#           size=8
+#         ),
+#         legend.title=element_text(#family="Times",
+#           size=10
+#         ),
+#         axis.text=element_text(#family="Times",
+#           colour = "black",
+#           size=8
+#         ),
+#         axis.ticks.x = element_blank(),
+#         axis.title=element_text(#family="Times",
+#           size=12
+#         ),
+#         strip.text=element_text(#family = "Times",
+#           size = 12
+#         ),
+#         # strip.background = element_rect(fill = "white"),
+#         legend.position="none")
+
+#g1
+
+#ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
+#g2
+```
+
+```{r, SymbolizationGender,fig.cap="Gender differences in Symbolization for each country",include=TRUE}
+#suppressWarnings(print(g1))
+
+```
+
+<style>
+#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
+#scaled-frame { width: 250%; height: 900px; border: 1px; }
+#scaled-frame {
+    zoom: 0.50;
+    -moz-transform: scale(0.50);
+    -moz-transform-origin: 0 0;
+    -o-transform: scale(0.50);
+    -o-transform-origin: 0 0;
+    -webkit-transform: scale(0.50);
+    -webkit-transform-origin: 0 0;
+}
+
+@media screen and (-webkit-min-device-pixel-ratio:0) {
+ #scaled-frame  { zoom: 1;  }
+}
+</style>
+
+<div id="wrapper"><iframe id="scaled-frame" src="plots/internalization.png"></iframe></div>

### 2023-02-05 drafting_supplementary_analysis.Rmd
added links and updated plots

@@
 ### Internalization Plot
+([open in new window](https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/internalization.png))
 
@@
 
-# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-# x$sex3 <- droplevels(x$sex3)
-# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-# 
-# #### identify countries with small samples
-# male_length <- function(x){sum(x$sex3=='male')}
-# males <- lapply(x, male_length)
-# female_length <- function(x){sum(x$sex3=='female')}
-# females <- lapply(x, female_length)
-# names(females)
-# 
-# #### generate a vector containing all countries with less than 10 observations for either males or females ####
-# exclusions <- c(names(males[males<2]),
-#   names(females[females<2]))
-# 
-# #### re-load ungrouped data ####
-# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-# x$sex3 <- droplevels(x$sex3)
-# 
-# # and remove missing again
-# sum(is.na(x$moral_identity_internal))
-# x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-# 
-# #### Filter out any countries to be excluded ####
-# x <- subset(x, !(country_name %in% exclusions))
-# 
-# df1 <- x
-# 
-# df1_male <- df1[which(df1$sex3=="male"),]
-# df1_female <- df1[which(df1$sex3=="female"),]
-# 
-# internal_mean_sd <- function(x){
-#   z <- x
-#   z$mean <- mean(z$moral_identity_internal, na.rm=T)
-#   z$sd <- sd(z$moral_identity_internal, na.rm=T)
-#   z
-# }
-# 
-# 
-# df1 <- rbind.data.frame(
-#   internal_mean_sd(df1_female),
-#   internal_mean_sd(df1_male)
-# )
-# 
-# df1$sex3 <- dplyr::recode(df1$sex3
-#                            , "male" = "Male"
-#                            , "female" = "Female")
-# 
-# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
-#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") + 
-#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="lightgrey")+
-#   geom_violin(fill = NA) +
-#   #ggforce::geom_sina(size=.01)+
-#   # geom_sina(shape=16
-#   #           , position=position_jitter(height=.25,width=0)
-#   #           , size=.000001
-#   #           , color="dark grey"
-#   #           ,jitter_y=F
-#   # )+
-#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
-#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
-#                 position=position_dodge(0.05), color="#5a5a5a")+
-#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
-#   # stat_summary(geom = "linerange",
-#   #   fun.data = mean_sdl, 
-#   #   fun.args = list(mult = 1),
-#   #   colour = "black"
-#   # )+
-#   xlab("Gender")+
-#   ylab("Internalization")+  
-#   facet_wrap(~df1$ISO3, ncol = 9 )+
-#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-#   theme_bw() +
-#   theme(panel.border = element_blank(),
-#         axis.line = element_line(size = .2),
-#         strip.background  = element_blank(),
-#         panel.grid = element_blank(),
-#         plot.title=element_text(#family="Times",
-#           size=12
-#         ),
-#         #legend.position="right",
-#         legend.text=element_text(#family="Times",
-#           size=8
-#         ),
-#         legend.title=element_text(#family="Times",
-#           size=10
-#         ),
-#         axis.text=element_text(#family="Times",
-#           colour = "black",
-#           size=8
-#         ),
-#         axis.ticks.x = element_blank(),
-#         axis.title=element_text(#family="Times",
-#           size=12
-#         ),
-#         strip.text=element_text(#family = "Times",
-#           size = 12
-#         ),
-#         # strip.background = element_rect(fill = "white"),
-#         legend.position="none")
-# 
-# ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
+x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+x$sex3 <- droplevels(x$sex3)
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+#### identify countries with small samples
+male_length <- function(x){sum(x$sex3=='male')}
+males <- lapply(x, male_length)
+female_length <- function(x){sum(x$sex3=='female')}
+females <- lapply(x, female_length)
+names(females)
+
+#### generate a vector containing all countries with less than 10 observations for either males or females ####
+exclusions <- c(names(males[males<2]),
+  names(females[females<2]))
+
+#### re-load ungrouped data ####
+x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+x$sex3 <- droplevels(x$sex3)
+
+# and remove missing again
+sum(is.na(x$moral_identity_internal))
+x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+
+#### Filter out any countries to be excluded ####
+x <- subset(x, !(country_name %in% exclusions))
+
+df1 <- x
+
+df1_male <- df1[which(df1$sex3=="male"),]
+df1_female <- df1[which(df1$sex3=="female"),]
+
+internal_mean_sd <- function(x){
+  z <- x
+  z$mean <- mean(z$moral_identity_internal, na.rm=T)
+  z$sd <- sd(z$moral_identity_internal, na.rm=T)
+  z
+}
+
+df1 <- rbind.data.frame(
+  internal_mean_sd(df1_female),
+  internal_mean_sd(df1_male)
+)
+
+df1$sex3 <- dplyr::recode(df1$sex3
+                           , "male" = "Male"
+                           , "female" = "Female")
+
+g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
+  #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
+  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
+  geom_violin(fill = NA) +
+  #ggforce::geom_sina(size=.01)+
+  # geom_sina(shape=16
+  #           , position=position_jitter(height=.25,width=0)
+  #           , size=.000001
+  #           , color="dark grey"
+  #           ,jitter_y=F
+  # )+
+  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
+                position=position_dodge(0.05), color="#5a5a5a")+
+  stat_summary(fun=mean, geom="point", shape=16, size=.5)+
+  # stat_summary(geom = "linerange",
+  #   fun.data = mean_sdl,
+  #   fun.args = list(mult = 1),
+  #   colour = "black"
+  # )+
+  xlab("Gender")+
+  ylab("Internalization")+
+  facet_wrap(~df1$ISO3, ncol = 9 )+
+  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
 
@@
 ### Symbolization Plot
+([open in new window](https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/symbolization.png))
 
@@
 # g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
-#   geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
-#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
+#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
+#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
 #   geom_violin(fill = NA) +
@@
 #         legend.position="none")
-
-#g1
-
-#ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
+# 
+# #g1
+# 
+# ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
 #g2

### 2023-02-05 drafting_supplementary_analysis.Rmd
fixed symbolization plot

@@
 ### Internalization Plot
-([open in new window](https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/internalization.png))
+
+(<a href="https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/internalization.png" target="_blank">open in new window</a>)
 
@@
 
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-#### identify countries with small samples
-male_length <- function(x){sum(x$sex3=='male')}
-males <- lapply(x, male_length)
-female_length <- function(x){sum(x$sex3=='female')}
-females <- lapply(x, female_length)
-names(females)
-
-#### generate a vector containing all countries with less than 10 observations for either males or females ####
-exclusions <- c(names(males[males<2]),
-  names(females[females<2]))
-
-#### re-load ungrouped data ####
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-
-#### Filter out any countries to be excluded ####
-x <- subset(x, !(country_name %in% exclusions))
-
-df1 <- x
-
-df1_male <- df1[which(df1$sex3=="male"),]
-df1_female <- df1[which(df1$sex3=="female"),]
-
-internal_mean_sd <- function(x){
-  z <- x
-  z$mean <- mean(z$moral_identity_internal, na.rm=T)
-  z$sd <- sd(z$moral_identity_internal, na.rm=T)
-  z
-}
-
-df1 <- rbind.data.frame(
-  internal_mean_sd(df1_female),
-  internal_mean_sd(df1_male)
-)
-
-df1$sex3 <- dplyr::recode(df1$sex3
-                           , "male" = "Male"
-                           , "female" = "Female")
-
-g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
-  #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
-  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
-  geom_violin(fill = NA) +
-  #ggforce::geom_sina(size=.01)+
-  # geom_sina(shape=16
-  #           , position=position_jitter(height=.25,width=0)
-  #           , size=.000001
-  #           , color="dark grey"
-  #           ,jitter_y=F
-  # )+
-  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
-  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
-                position=position_dodge(0.05), color="#5a5a5a")+
-  stat_summary(fun=mean, geom="point", shape=16, size=.5)+
-  # stat_summary(geom = "linerange",
-  #   fun.data = mean_sdl,
-  #   fun.args = list(mult = 1),
-  #   colour = "black"
-  # )+
-  xlab("Gender")+
-  ylab("Internalization")+
-  facet_wrap(~df1$ISO3, ncol = 9 )+
-  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-  theme_bw() +
-  theme(panel.border = element_blank(),
-        axis.line = element_line(size = .2),
-        strip.background  = element_blank(),
-        panel.grid = element_blank(),
-        plot.title=element_text(#family="Times",
-          size=12
-        ),
-        #legend.position="right",
-        legend.text=element_text(#family="Times",
-          size=8
-        ),
-        legend.title=element_text(#family="Times",
-          size=10
-        ),
-        axis.text=element_text(#family="Times",
-          colour = "black",
-          size=8
-        ),
-        axis.ticks.x = element_blank(),
-        axis.title=element_text(#family="Times",
-          size=12
-        ),
-        strip.text=element_text(#family = "Times",
-          size = 12
-        ),
-        # strip.background = element_rect(fill = "white"),
-        legend.position="none")
-
-ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
+# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+# x$sex3 <- droplevels(x$sex3)
+# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+# 
+# #### identify countries with small samples
+# male_length <- function(x){sum(x$sex3=='male')}
+# males <- lapply(x, male_length)
+# female_length <- function(x){sum(x$sex3=='female')}
+# females <- lapply(x, female_length)
+# names(females)
+# 
+# #### generate a vector containing all countries with less than 10 observations for either males or females ####
+# exclusions <- c(names(males[males<2]),
+#   names(females[females<2]))
+# 
+# #### re-load ungrouped data ####
+# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+# x$sex3 <- droplevels(x$sex3)
+# 
+# # and remove missing again
+# sum(is.na(x$moral_identity_internal))
+# x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+# 
+# #### Filter out any countries to be excluded ####
+# x <- subset(x, !(country_name %in% exclusions))
+# 
+# df1 <- x
+# 
+# df1_male <- df1[which(df1$sex3=="male"),]
+# df1_female <- df1[which(df1$sex3=="female"),]
+# 
+# internal_mean_sd <- function(x){
+#   z <- x
+#   z$mean <- mean(z$moral_identity_internal, na.rm=T)
+#   z$sd <- sd(z$moral_identity_internal, na.rm=T)
+#   z
+# }
+# 
+# 
+# df1 <- rbind.data.frame(
+#   internal_mean_sd(df1_female),
+#   internal_mean_sd(df1_male)
+# )
+# 
+# df1$sex3 <- dplyr::recode(df1$sex3
+#                            , "male" = "Male"
+#                            , "female" = "Female")
+# 
+# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
+#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
+#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
+#   geom_violin(fill = NA) +
+#   #ggforce::geom_sina(size=.01)+
+#   # geom_sina(shape=16
+#   #           , position=position_jitter(height=.25,width=0)
+#   #           , size=.000001
+#   #           , color="dark grey"
+#   #           ,jitter_y=F
+#   # )+
+#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
+#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
+#                 position=position_dodge(0.05), color="#5a5a5a")+
+#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
+#   # stat_summary(geom = "linerange",
+#   #   fun.data = mean_sdl,
+#   #   fun.args = list(mult = 1),
+#   #   colour = "black"
+#   # )+
+#   xlab("Gender")+
+#   ylab("Internalization")+
+#   facet_wrap(~df1$ISO3, ncol = 9 )+
+#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
+#   theme_bw() +
+#   theme(panel.border = element_blank(),
+#         axis.line = element_line(size = .2),
+#         strip.background  = element_blank(),
+#         panel.grid = element_blank(),
+#         plot.title=element_text(#family="Times",
+#           size=12
+#         ),
+#         #legend.position="right",
+#         legend.text=element_text(#family="Times",
+#           size=8
+#         ),
+#         legend.title=element_text(#family="Times",
+#           size=10
+#         ),
+#         axis.text=element_text(#family="Times",
+#           colour = "black",
+#           size=8
+#         ),
+#         axis.ticks.x = element_blank(),
+#         axis.title=element_text(#family="Times",
+#           size=12
+#         ),
+#         strip.text=element_text(#family = "Times",
+#           size = 12
+#         ),
+#         # strip.background = element_rect(fill = "white"),
+#         legend.position="none")
+# 
+# ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
 
@@
 ### Symbolization Plot
-([open in new window](https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/symbolization.png))
+
+(<a href="https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/symbolization.png" target="_blank">open in new window</a>)
 

### 2023-02-06 H1.Rmd
H2 all done (I think)

--- 2023-02-05 drafting_results_section.Rmd
@@
 ---
-title: "Who Cares about Morality"
+title: "H1: Gender Differences"
 author: "Mariola Paruzel-Czachura, Cillian McHugh"
@@
 
-```{r setup, include=FALSE}
+```{r setuph1, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE)
@@
 ```
-
-```{r}
-
-```
-
-# H1 Gender Differences
 
@@
 ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), p_report)
+raw_ps_for_table <- (lapply(all_t_tests, all_t_ps))
 
@@
 
+```{r}
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, female_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, male_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, ts_for_table),digits=2)
+    ,round(do.call(rbind, df_for_table),digits=2)
+    ,do.call(rbind, raw_ps_for_table)
+    ,round(do.call(rbind, ds_for_table),digits=2)
+    )
+
+test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
+test
+
+sum(unlist(lapply(all_t_tests, all_t_ps))<.05)
+
+test1 <- subset(test, p < .05)
+
+neg <- sum(test1$`mean F`<test1$`mean M`)
+pos <- sum(test1$`mean F`>test1$`mean M`)
+
+c1 <- paste0(rownames(test1[which(test1$`mean F`<test1$`mean M`),]))[1]
+c2 <- paste0(rownames(test1[which(test1$`mean F`<test1$`mean M`),]))[2]
+
+```
+
 We conducted a linear-mixed-effects model to test for gender differences in internalization when participants are nested within country.
@@
 *t*(`r sprintf("%.2f",results_coef$df[2])`) = 
-`r sprintf("%.2f",t1)`
-, *p* `r paste(p_report(p2))`.
+`r sprintf("%.2f",t1)`,
+*p* `r paste(p_report(p2))`.
 We conducted a series of independent-samples t-tests to test for gender differences in internalization across all countries.
-We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).
+We found significant gender differences in internalization across `r total_sig` countries.
+Of these, `r pos` were in the predicted direction, while in `r neg` countries (`r c1` and `r c2`), males showed higher internalization than females (see Supplementary Materials Table S_X).
 
@@
 
+```{r}
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, female_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, male_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, ts_for_table),digits=2)
+    ,round(do.call(rbind, df_for_table),digits=2)
+    ,do.call(rbind, raw_ps_for_table)
+    ,round(do.call(rbind, ds_for_table),digits=2)
+    )
+
+test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
+test
+
+sum(unlist(lapply(all_t_tests, all_t_ps))<.05)
+
+test1 <- subset(test, p < .05)
+
+neg <- sum(test1$`mean F`<test1$`mean M`)
+pos <- sum(test1$`mean F`>test1$`mean M`)
+
+c1 <- paste0(rownames(test1[which(test1$`mean F`<test1$`mean M`),]))[1]
+c2 <- paste0(rownames(test1[which(test1$`mean F`<test1$`mean M`),]))[2]
+
+```
+
 We conducted another linear-mixed-effects model to test for gender differences in symbolization when participants are nested within country.
@@
 *t*(`r sprintf("%.2f",results_coef$df[2])`) = 
-`r sprintf("%.2f",t1)`
-, *p* `r paste(p_report(p2))`.
+`r sprintf("%.2f",t1)`,
+*p* `r paste(p_report(p2))`.
 We conducted a series of independent-samples t-tests to test for gender differences in symbolization across all countries.
-We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).
+We found significant gender differences in symbolization across `r total_sig` countries.
+Of these, `r pos` were in the predicted direction, while in `r neg` countries (`r c1` and `r c2`), males showed higher symbolization than females (see Supplementary Materials Table S_X).
 

### 2023-02-06 H2.Rmd
H2 all done (I think)

---
title: "H2: Age Differences"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }

</style>

```{r setuph2, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
```

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)
```

```{r}
rm(list = ls())

#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

df$sex3 <- as.factor(df$sex1)
df$sex3 <- dplyr::recode(df$sex3,
               "1"="male"
              ,"2"="female"
              ,"3"="other")

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")

```

```{r}

x <- df
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]

c1 <- cor.test(x$moral_identity_internal,x$age)

```

```{r}

x <- df
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]

c2 <- cor.test(x$moral_identity_symbolic,x$age)

```

Due to mixed findings in the literature, we did not have specific predictions regarding the relationship between age and moral identity, and the analyses reported here are exploratory. Overall there was a significant negative correlation between age and internalization *r* = `r sprintf("%.3f", c1$estimate)`, *p* = `r paste(p_report(c1$p.value))`, suggesting that older participants had lower internalization scores. Similarly, we found a significant negative correlation between age and symbolization *r* = `r sprintf("%.3f", c2$estimate)`, *p* = `r paste(p_report(c2$p.value))`, again, suggesting that older participants had lower symbolization scores than younger participants.

```{r}
x <- df
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]

model0 <- lmerTest::lmer(moral_identity_internal ~
                 #  sex_01
                 # * age
                  + (1|country)
                , data = x
                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )

model1 <- lmerTest::lmer(moral_identity_internal ~
                 #  sex_01
                   age
                  + (1|country)
                , data = x
               # , contrasts = list(sex_01 = contr.sum)
            )
summary(model1)
anova(model0,model1)

summary(model1)
anova(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)
summary_model1
results_coef <- as.data.frame(summary_model1$coefficients)
results_coef

aov1 <- anova(model1)

f3a <- aov1$`F value`[1]
p3a <- aov1$`Pr(>F)`[1]

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
t1 <- results_coef$`t value`[2]
p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)

```

```{r}

x <- df
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
#### group by country for analysis ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

N_fun <- function(x){
  length(x$sex3)
}
total_Ns <- lapply(x, N_fun)

exclusions <- names(total_Ns)[which(total_Ns<3)]
x <- df
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

cor_fun <- function(x){
  cor.test(x$moral_identity_symbolic,x$age)
}
all_cor_tests <- lapply(x, cor_fun)

all_cor_rs <- function(c){
  c$estimate
}
rs_for_table <- lapply(all_cor_tests, all_cor_rs)
all_cor_ps <- function(c){
  c$estimate
}
ps_for_table <- lapply(all_cor_tests, all_cor_ps)
Ns_for_table <- lapply(x, N_fun)

means_INT_fun <- function(x){
  mean(x$moral_identity_internal)
}
mean_int_for_table <- lapply(x, means_INT_fun)
sd_INT_fun <- function(x){
  sd(x$moral_identity_internal)
}
sd_int_for_table <- lapply(x, sd_INT_fun)

means_age_fun <- function(x){
  mean(x$age)
}
mean_age_for_table <- lapply(x, means_age_fun)
sd_age_fun <- function(x){
  sd(x$age)
}
sd_age_for_table <- lapply(x, sd_age_fun)

```

```{r}
test <- 
  cbind.data.frame(
     do.call(rbind,mean_age_for_table)
    ,do.call(rbind,sd_age_for_table)
    ,do.call(rbind,mean_int_for_table)
    ,do.call(rbind,sd_int_for_table)
    ,round(do.call(rbind, rs_for_table),digits=3)
    ,do.call(rbind, ps_for_table)
    ,round(do.call(rbind, Ns_for_table))
    )

test <- `colnames<-`(test, c("mean age","SD age","mean internalization", "SD internalization", "r","p","N"))
test

sum(unlist(ps_for_table)<.05)

test1 <- subset(test, p < .05)
test1

total_sig <- length(test1$`mean age`)

neg <- sum(test1$r <0 )
pos <- sum(test1$r>0)

```

We conducted a linear-mixed-effects model to test if this relationship between age and internalization holds when participants are nested within country. Our outcome measure was internalization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of correlations test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials Table S_X).

```{r}

x <- df
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]

model0 <- lmerTest::lmer(moral_identity_symbolic ~
                 #  sex_01
                 # * age
                  + (1|country)
                , data = x
                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                 #  sex_01
                   age
                  + (1|country)
                , data = x
               # , contrasts = list(sex_01 = contr.sum)
            )
summary(model1)
anova(model0,model1)

summary(model1)
anova(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)
summary_model1
results_coef <- as.data.frame(summary_model1$coefficients)
results_coef

aov1 <- anova(model1)

f3a <- aov1$`F value`[1]
p3a <- aov1$`Pr(>F)`[1]

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
t1 <- results_coef$`t value`[2]
p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)

```

```{r}

x <- df
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
#### group by country for analysis ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

N_fun <- function(x){
  length(x$sex3)
}
total_Ns <- lapply(x, N_fun)

exclusions <- names(total_Ns)[which(total_Ns<3)]
x <- df
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

cor_fun <- function(x){
  cor.test(x$moral_identity_symbolic,x$age)
}
all_cor_tests <- lapply(x, cor_fun)

all_cor_rs <- function(c){
  c$estimate
}
rs_for_table <- lapply(all_cor_tests, all_cor_rs)
all_cor_ps <- function(c){
  c$estimate
}
ps_for_table <- lapply(all_cor_tests, all_cor_ps)
Ns_for_table <- lapply(x, N_fun)

means_INT_fun <- function(x){
  mean(x$moral_identity_symbolic)
}
mean_int_for_table <- lapply(x, means_INT_fun)
sd_INT_fun <- function(x){
  sd(x$moral_identity_symbolic)
}
sd_int_for_table <- lapply(x, sd_INT_fun)

means_age_fun <- function(x){
  mean(x$age)
}
mean_age_for_table <- lapply(x, means_age_fun)
sd_age_fun <- function(x){
  sd(x$age)
}
sd_age_for_table <- lapply(x, sd_age_fun)

```

```{r}
test <- 
  cbind.data.frame(
     do.call(rbind,mean_age_for_table)
    ,do.call(rbind,sd_age_for_table)
    ,do.call(rbind,mean_int_for_table)
    ,do.call(rbind,sd_int_for_table)
    ,round(do.call(rbind, rs_for_table),digits=3)
    ,do.call(rbind, ps_for_table)
    ,round(do.call(rbind, Ns_for_table))
    )

test <- `colnames<-`(test, c("mean age","SD age","mean symbolization", "SD symbolization", "r","p","N"))
test

sum(unlist(ps_for_table)<.05)

test1 <- subset(test, p < .05)
test1

total_sig <- length(test1$`mean age`)

neg <- sum(test1$r <0 )
pos <- sum(test1$r>0)

```

Similarly, for symbolization, we conducted a linear-mixed-effects model to test if the relationship between age and symbolization holds when participants are nested within country. Our outcome measure was symbolization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
We conducted a series of correlations test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials Table S_X).

### 2023-02-06 drafting_results_section.Rmd
H2 all done (I think)

@@
 
-```{r setup, include=FALSE}
+```{r setupparent, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE)
@@
 
-```{r}
+# H1 Gender Differences
 
+```{r child = 'H1.Rmd'}
 ```
 
-# H1 Gender Differences
+# H2 Age Differences
 
-```{r}
-
-x <- df
-
-table(x$sex3)
-x <- x[which(x$sex3!="other"),]
-x$sex3 <- droplevels(x$sex3)
-
-t1 <- t.test(x$moral_identity_internal ~ x$sex3)
-d1 <- cohen.d(x$moral_identity_internal, x$sex3)
-
-d1$cohen.d[2]
-sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))
-sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))
-sprintf("%.2f",t1$parameter)
-sprintf("%.2f",t1$statistic)
-
-t2 <- t.test(x$moral_identity_symbolic ~ x$sex3)
-d2 <- cohen.d(x$moral_identity_symbolic, x$sex3)
-
+```{r child = 'H2.Rmd'}
 ```
-
-Our first hypothesis was that women would have higher levels of internalization and symbolization than men.
-To test this we isolated the data for men and women from the main dataset.
-An independent samples t-test revealed that for the entire sample, women had higher internalization scores (*M* = `r sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))`), than men (*M* = `r sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='male')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='male')],na.rm=T))`), *t*(`r sprintf("%.2f",t1$parameter)`) = `r sprintf("%.2f",t1$statistic)`, *p* `r paste(p_report(t1$p.value))`, *d* = `r sprintf("%.2f", d1$cohen.d[2])`.
-Similarly, for symbolization, an independent samples t-test revealed that for the entire sample, women had higher scores (*M* = `r sprintf("%.1f",mean(x$moral_identity_symbolic[which(x$sex3=='female')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_symbolic[which(x$sex3=='female')],na.rm=T))`), than men (*M* = `r sprintf("%.1f",mean(x$moral_identity_symbolic[which(x$sex3=='male')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_symbolic[which(x$sex3=='male')],na.rm=T))`), *t*(`r sprintf("%.2f",t2$parameter)`) = `r sprintf("%.2f",t2$statistic)`, *p* `r paste(p_report(t2$p.value))`, *d* = `r sprintf("%.2f", d2$cohen.d[2])`.
-
-```{r}
-
-x <- df
-
-table(x$sex3)
-x <- x[which(x$sex3!="other"),]
-x$sex3 <- droplevels(x$sex3)
-
-x$sex_01 <-  dplyr::recode(x$sex3,
-               "male"="0"
-              ,"female"="1")
-
-model0 <- lmerTest::lmer(moral_identity_internal ~
-                 #  sex_01
-                 # * age
-                  + (1|country)
-                , data = x
-                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                    sex_01
-                 # * age
-                  + (1|country)
-                , data = x
-               # , contrasts = list(sex_01 = contr.sum)
-            )
-summary(model1)
-anova(model0,model1)
-
-summary(model1)
-anova(model1)
-results_anova <- as.data.frame(anova(model0,model1))
-results_anova
-results_anova$Chisq[2]
-results_anova$Df
-p1 <- results_anova$`Pr(>Chisq)`[2]
-p_report(p1)
-#p_report(results_anova$`Pr(>Chisq)`)[2]
-results_anova$AIC
-summary_model1 <- summary(model1)
-summary_model1
-results_coef <- as.data.frame(summary_model1$coefficients)
-results_coef
-
-aov1 <- anova(model1)
-
-f3a <- aov1$`F value`[1]
-p3a <- aov1$`Pr(>F)`[1]
-
-results_coef$Estimate[2]
-results_coef$`Std. Error`[2]
-results_coef$df[2]
-t1 <- results_coef$`t value`[2]
-p2 <- results_coef$`Pr(>|t|)`[2]
-
-#QuantPsyc::lm.beta(results_coef)
-anova(model1)
-```
-
-```{r}
-
-#### ensure correct data is loaded ####
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-#### remove any missing data #### 
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-table(x$country_name,x$sex3)
-x$country_name
-
-#### group by country ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-#### identify countries with small samples
-male_length <- function(x){sum(x$sex3=='male')}
-males <- lapply(x, male_length)
-female_length <- function(x){sum(x$sex3=='female')}
-females <- lapply(x, female_length)
-names(females)
-
-#### generate a vector containing all countries with less than 10 observations for either males or females ####
-exclusions <- c(names(males[males<2]),
-  names(females[females<2]))
-
-#### re-load ungrouped data ####
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-
-#### Filter out any countries to be excluded ####
-x <- subset(x, !(country_name %in% exclusions))
-
-#### group by country for analysis ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-ttest_fun <- function(x){
-  t.test(moral_identity_internal ~ sex3, data = x)
-}
-all_t_tests <- lapply(x, ttest_fun)
-
-means_fun <- function(x){
-  mean(x$moral_identity_internal)
-}
-lapply(x, means_fun)
-sd_fun <- function(x){
-  sd(x$moral_identity_internal)
-}
-lapply(x, sd_fun)
-
-cohens_d_fun <- function(x){
-  cohen.d(x$moral_identity_symbolic, x$sex3)
-}
-all_ds <- lapply(x, cohens_d_fun)
-show_d_fun <- function(x){
-  x$cohen.d[2]
-}
-ds_for_table <- lapply(all_ds, show_d_fun)
-
-all_t_stats <- function(t){
-  t$statistic
-}
-ts_for_table <- lapply(all_t_tests, all_t_stats)
-
-all_t_df <- function(t){
-  t$parameter
-}
-df_for_table <- lapply(all_t_tests, all_t_df)
-
-all_t_ps <- function(t){
-  t$p.value
-}
-ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), p_report)
-
-total_sig <- sum(unlist(lapply(all_t_tests, all_t_ps))<.05)
-
-#### means for Males ####
-# re-load ungrouped data #
-x <- df[which(df$sex3=="male"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-male_means <- lapply(x, means_fun)
-male_sds <- lapply(x, sd_fun)
-
-#### means for Females
-# re-load ungrouped data #
-x <- df[which(df$sex3=="female"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-female_means <- lapply(x, means_fun)
-female_sds <- lapply(x, sd_fun)
-
-```
-
-We conducted a linear-mixed-effects model to test for gender differences in internalization when participants are nested within country.
-Our outcome measure was internalization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
-Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
-$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
-There was a significant main effect for gender,
-*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
-`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
-with a significant positive association between being female and higher internalization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
-*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
-`r sprintf("%.2f",t1)`
-, *p* `r paste(p_report(p2))`.
-We conducted a series of independent-samples t-tests to test for gender differences in internalization across all countries.
-We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).
-
-```{r}
-
-x <- df
-
-table(x$sex3)
-x <- x[which(x$sex3!="other"),]
-x$sex3 <- droplevels(x$sex3)
-
-x$sex_01 <-  dplyr::recode(x$sex3,
-               "male"="0"
-              ,"female"="1")
-
-model0 <- lmerTest::lmer(moral_identity_symbolic ~
-                 #  sex_01
-                 # * age
-                  + (1|country)
-                , data = x
-                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                    sex_01
-                 # * age
-                  + (1|country)
-                , data = x
-              #  , contrasts = list(sex_01 = contr.sum)
-            )
-summary(model1)
-anova(model0,model1)
-
-summary(model1)
-anova(model1)
-results_anova <- as.data.frame(anova(model0,model1))
-results_anova
-results_anova$Chisq[2]
-results_anova$Df
-p1 <- results_anova$`Pr(>Chisq)`[2]
-p_report(p1)
-#p_report(results_anova$`Pr(>Chisq)`)[2]
-results_anova$AIC
-summary_model1 <- summary(model1)
-summary_model1
-results_coef <- as.data.frame(summary_model1$coefficients)
-results_coef
-
-aov1 <- anova(model1)
-
-f3a <- aov1$`F value`[1]
-p3a <- aov1$`Pr(>F)`[1]
-
-results_coef$Estimate[2]
-results_coef$`Std. Error`[2]
-results_coef$df[2]
-t1 <- results_coef$`t value`[2]
-p2 <- results_coef$`Pr(>|t|)`[2]
-
-#QuantPsyc::lm.beta(results_coef)
-anova(model1)
-```
-
-```{r}
-
-#### ensure correct data is loaded ####
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-#### remove any missing data #### 
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-table(x$country_name,x$sex3)
-x$country_name
-
-#### group by country ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-#### identify countries with small samples
-male_length <- function(x){sum(x$sex3=='male')}
-males <- lapply(x, male_length)
-female_length <- function(x){sum(x$sex3=='female')}
-females <- lapply(x, female_length)
-names(females)
-
-#### generate a vector containing all countries with less than 10 observations for either males or females ####
-exclusions <- c(names(males[males<2]),
-  names(females[females<2]))
-
-#### re-load ungrouped data ####
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-
-#### Filter out any countries to be excluded ####
-x <- subset(x, !(country_name %in% exclusions))
-
-#### group by country for analysis ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-ttest_fun <- function(x){
-  t.test(moral_identity_symbolic ~ sex3, data = x)
-}
-all_t_tests <- lapply(x, ttest_fun)
-
-means_fun <- function(x){
-  mean(x$moral_identity_symbolic)
-}
-lapply(x, means_fun)
-sd_fun <- function(x){
-  sd(x$moral_identity_symbolic)
-}
-lapply(x, sd_fun)
-
-cohens_d_fun <- function(x){
-  cohen.d(x$moral_identity_symbolic, x$sex3)
-}
-all_ds <- lapply(x, cohens_d_fun)
-show_d_fun <- function(x){
-  x$cohen.d[2]
-}
-ds_for_table <- lapply(all_ds, show_d_fun)
-
-all_t_stats <- function(t){
-  t$statistic
-}
-ts_for_table <- lapply(all_t_tests, all_t_stats)
-
-all_t_df <- function(t){
-  t$parameter
-}
-df_for_table <- lapply(all_t_tests, all_t_df)
-
-all_t_ps <- function(t){
-  t$p.value
-}
-ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), p_report)
-
-total_sig <- sum(unlist(lapply(all_t_tests, all_t_ps))<.05)
-
-#### means for Males ####
-# re-load ungrouped data #
-x <- df[which(df$sex3=="male"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-male_means <- lapply(x, means_fun)
-male_sds <- lapply(x, sd_fun)
-
-#### means for Females
-# re-load ungrouped data #
-x <- df[which(df$sex3=="female"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-female_means <- lapply(x, means_fun)
-female_sds <- lapply(x, sd_fun)
-
-```
-
-We conducted another linear-mixed-effects model to test for gender differences in symbolization when participants are nested within country.
-Our outcome measure was symbolization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
-Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
-$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
-There was a significant main effect for gender,
-*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
-`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
-with a significant positive association between being female and higher symbolization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
-*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
-`r sprintf("%.2f",t1)`
-, *p* `r paste(p_report(p2))`.
-We conducted a series of independent-samples t-tests to test for gender differences in symbolization across all countries.
-We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).
-
-```{r internalizationPlot}
-
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-df1 <- x
-
-df1_male <- df1[which(df1$sex3=="male"),]
-df1_female <- df1[which(df1$sex3=="female"),]
-
-internal_mean_sd <- function(x){
-  z <- x
-  z$mean <- mean(z$moral_identity_internal, na.rm=T)
-  z$sd <- sd(z$moral_identity_internal, na.rm=T)
-  z
-}
-
-df1 <- rbind.data.frame(
-  internal_mean_sd(df1_female),
-  internal_mean_sd(df1_male)
-)
-
-df1$sex3 <- dplyr::recode(df1$sex3
-                           , "male" = "Male"
-                           , "female" = "Female")
-
-g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
-  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
-  geom_violin(fill = NA) +
-  #ggforce::geom_sina(size=.01)+
-  # geom_sina(shape=16
-  #           , position=position_jitter(height=.25,width=0)
-  #           , size=.000001
-  #           , color="dark grey"
-  #           ,jitter_y=F
-  # )+
-  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
-  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
-               position=position_dodge(0.05), color="#5a5a5a")+
-  stat_summary(fun=mean, geom="point", shape=16, size=2)+
-  # stat_summary(geom = "linerange",
-  #   fun.data = mean_sdl, 
-  #   fun.args = list(mult = 1),
-  #   colour = "black"
-  # )+
-  xlab("Gender")+
-  ylab("Internalization")+  
-  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-  theme_bw() +
-  theme(panel.border = element_blank(),
-        axis.line = element_line(size = .2),
-        strip.background  = element_blank(),
-        panel.grid = element_blank(),
-        plot.title=element_text(#family="Times",
-          size=12
-        ),
-        #legend.position="right",
-        legend.text=element_text(#family="Times",
-          size=8
-        ),
-        legend.title=element_text(#family="Times",
-          size=10
-        ),
-        axis.text=element_text(#family="Times",
-          colour = "black",
-          size=8
-        ),
-        axis.ticks.x = element_blank(),
-        axis.title=element_text(#family="Times",
-          size=12
-        ),
-        strip.text=element_text(#family = "Times",
-          size = 12
-        ),
-        # strip.background = element_rect(fill = "white"),
-        legend.position="none")
-
-#g1
-```
-
-```{r symbolizationPlot}
-
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-df1 <- x
-
-symbolic_mean_sd <- function(x){
-  z <- x
-  z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
-  z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
-  z
-}
-
-df1 <- rbind.data.frame(
-  symbolic_mean_sd(df1_female),
-  symbolic_mean_sd(df1_male)
-)
-
-df1$sex3 <- dplyr::recode(df1$sex3
-                           , "male" = "Male"
-                           , "female" = "Female")
-
-# df1 <- df
-g2 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
-  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
-  geom_violin(fill = NA) +
-  #ggforce::geom_sina(size=.01)+
-  # geom_sina(shape=16
-  #           , position=position_jitter(height=.25,width=0)
-  #           , size=.000001
-  #           , color="dark grey"
-  #           ,jitter_y=F
-  # )+
-  #geom_quasirandom(size=.1)+
-  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
-  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
-               position=position_dodge(0.05), color="#5a5a5a")+
-  stat_summary(fun=mean, geom="point", shape=16, size=2)+
-  # stat_summary(geom = "linerange",
-  #   fun.data = mean_sdl, 
-  #   fun.args = list(mult = 1),
-  #   colour = "black"
-  # )+
-  xlab("Gender")+
-  ylab("Symbolization")+  
-  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-  theme_bw() +
-  theme(panel.border = element_blank(),
-        axis.line = element_line(size = .2),
-        strip.background  = element_blank(),
-        panel.grid = element_blank(),
-        plot.title=element_text(#family="Times",
-          size=12
-        ),
-        #legend.position="right",
-        legend.text=element_text(#family="Times",
-          size=8
-        ),
-        legend.title=element_text(#family="Times",
-          size=10
-        ),
-        axis.text=element_text(#family="Times",
-          colour = "black",
-          size=8
-        ),
-        axis.ticks.x = element_blank(),
-        axis.title=element_text(#family="Times",
-          size=12
-        ),
-        strip.text=element_text(#family = "Times",
-          size = 12
-        ),
-        # strip.background = element_rect(fill = "white"),
-        legend.position="none")
-
-#g2
-```
-
-```{r, combinePlots, include=FALSE}
-figure <- ggarrange(g1
-                    , g2
-                    #,labels = c("A")
-                    , ncol = 1
-                    , nrow = 2
-                    #, widths = c(0.485, 0.5)
-)
-figure
-```
-
-```{r, meanSymbolizationGender,include=TRUE}
-suppressWarnings(print(figure))
-
-```

### 2023-02-06 drafting_supplementary_analysis.Rmd
H2 all done (I think)

@@
 
-# H1 Gender Differences
-
+# Gender
 ## Internalization
@@
 #   xlab("Gender")+
-#   ylab("Internalization")+
+#   ylab("Symbolization")+
 #   facet_wrap(~df1$ISO3, ncol = 9 )+
@@
 # ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
-#g2
+# #g2
 ```
@@
 <div id="wrapper"><iframe id="scaled-frame" src="plots/internalization.png"></iframe></div>
+
+# Age
+
+```{r}
+rm(list = ls())
+#source("set_up_data_calculate_means.R")
+load("data/data_with_means.RData")
+
+df$sex3 <- as.factor(df$sex1)
+df$sex3 <- dplyr::recode(df$sex3,
+               "1"="male"
+              ,"2"="female"
+              ,"3"="other")
+
+df$country_lower <- tolower(df$country)
+df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
+```
+
+## Age & Internalization
+
+```{r}
+
+ps <- function(y){
+  y <- round(y, digits = 3)
+  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
+  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
+        y, quote = FALSE)),"*"))
+  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
+        y)))}
+
+x <- df
+x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+x <- x[which(is.na(x$age)==FALSE),]
+#### group by country for analysis ####
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+N_fun <- function(x){
+  length(x$sex3)
+}
+total_Ns <- lapply(x, N_fun)
+
+exclusions <- names(total_Ns)[which(total_Ns<3)]
+x <- df
+x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+x <- x[which(is.na(x$age)==FALSE),]
+x <- subset(x, !(country_name %in% exclusions))
+
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+cor_fun <- function(x){
+  cor.test(x$moral_identity_symbolic,x$age)
+}
+all_cor_tests <- lapply(x, cor_fun)
+
+all_cor_rs <- function(c){
+  c$estimate
+}
+rs_for_table <- lapply(all_cor_tests, all_cor_rs)
+all_cor_ps <- function(c){
+  c$estimate
+}
+ps_for_table <- lapply(all_cor_tests, all_cor_ps)
+ps_output_for_table <- lapply((lapply(all_cor_tests, all_cor_ps)), ps)
+Ns_for_table <- lapply(x, N_fun)
+
+means_INT_fun <- function(x){
+  mean(x$moral_identity_internal)
+}
+mean_int_for_table <- lapply(x, means_INT_fun)
+sd_INT_fun <- function(x){
+  sd(x$moral_identity_internal)
+}
+sd_int_for_table <- lapply(x, sd_INT_fun)
+
+means_age_fun <- function(x){
+  mean(x$age)
+}
+mean_age_for_table <- lapply(x, means_age_fun)
+sd_age_fun <- function(x){
+  sd(x$age)
+}
+sd_age_for_table <- lapply(x, sd_age_fun)
+
+```
+
+```{r}
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind,mean_age_for_table),digits = 2)
+    ,round(do.call(rbind,sd_age_for_table),digits = 2)
+    ,round(do.call(rbind,mean_int_for_table),digits = 2)
+    ,round(do.call(rbind,sd_int_for_table),digits = 2)
+    ,round(do.call(rbind, Ns_for_table))
+    ,round(do.call(rbind, rs_for_table),digits=3)
+    ,do.call(rbind, ps_output_for_table)
+    )
+
+test <- `colnames<-`(test, c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
+test
+
+sum(unlist(ps_for_table)<.05)
+
+test1 <- subset(test, p < .05)
+test1
+
+total_sig <- length(test1$`mean age`)
+
+neg <- sum(test1$r <0 )
+pos <- sum(test1$r>0)
+
+x <- df
+x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+x <- x[which(is.na(x$age)==FALSE),]
+
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+P_R <- x$`Puerto Rico`
+P_R <- 
+  `rownames<-`(
+    `colnames<-`(
+      as.data.frame(
+        rbind(
+          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
+          # ,
+          c(
+            round(mean(P_R$age),digits=2)
+            ,round(sd(P_R$age),digits=2)
+            ,round(mean(P_R$moral_identity_internal),digits=2)
+            ,round(sd(P_R$moral_identity_internal),digits=2)
+            ,length(P_R$moral_identity_internal)
+            ,"-"
+            ,"-"))),
+      c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
+    ,c("Puerto Rico"))
+
+test <- rbind(test[1:49,],P_R,test[50:length(test$p),])
+test <- test[order(rownames(test) ),]
+
+```
+
+```{r include=TRUE}
+
+apa_table(
+  test
+  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
+  , caption = "Correlation between Age and Internalization for each Country"
+  , note = "* = sig. at p < .05; ** = sig. at p < .001")
+
+```
+
+## Age & Symbolization
+
+```{r}
+
+ps <- function(y){
+  y <- round(y, digits = 3)
+  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
+  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
+        y, quote = FALSE)),"*"))
+  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
+        y)))}
+
+x <- df
+x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
+x <- x[which(is.na(x$age)==FALSE),]
+#### group by country for analysis ####
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+N_fun <- function(x){
+  length(x$sex3)
+}
+total_Ns <- lapply(x, N_fun)
+
+exclusions <- names(total_Ns)[which(total_Ns<3)]
+x <- df
+x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
+x <- x[which(is.na(x$age)==FALSE),]
+x <- subset(x, !(country_name %in% exclusions))
+
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+cor_fun <- function(x){
+  cor.test(x$moral_identity_symbolic,x$age)
+}
+all_cor_tests <- lapply(x, cor_fun)
+
+all_cor_rs <- function(c){
+  c$estimate
+}
+rs_for_table <- lapply(all_cor_tests, all_cor_rs)
+all_cor_ps <- function(c){
+  c$estimate
+}
+ps_for_table <- lapply(all_cor_tests, all_cor_ps)
+ps_output_for_table <- lapply((lapply(all_cor_tests, all_cor_ps)), ps)
+Ns_for_table <- lapply(x, N_fun)
+
+means_INT_fun <- function(x){
+  mean(x$moral_identity_symbolic)
+}
+mean_int_for_table <- lapply(x, means_INT_fun)
+sd_INT_fun <- function(x){
+  sd(x$moral_identity_symbolic)
+}
+sd_int_for_table <- lapply(x, sd_INT_fun)
+
+means_age_fun <- function(x){
+  mean(x$age)
+}
+mean_age_for_table <- lapply(x, means_age_fun)
+sd_age_fun <- function(x){
+  sd(x$age)
+}
+sd_age_for_table <- lapply(x, sd_age_fun)
+
+```
+
+```{r}
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind,mean_age_for_table),digits = 2)
+    ,round(do.call(rbind,sd_age_for_table),digits = 2)
+    ,round(do.call(rbind,mean_int_for_table),digits = 2)
+    ,round(do.call(rbind,sd_int_for_table),digits = 2)
+    ,round(do.call(rbind, Ns_for_table))
+    ,round(do.call(rbind, rs_for_table),digits=3)
+    ,do.call(rbind, ps_output_for_table)
+    )
+
+test <- `colnames<-`(test, c("mean age","SD age","mean symbolization", "SD symbolization","N", "r","p"))
+test
+
+sum(unlist(ps_for_table)<.05)
+
+test1 <- subset(test, p < .05)
+test1
+
+total_sig <- length(test1$`mean age`)
+
+neg <- sum(test1$r <0 )
+pos <- sum(test1$r>0)
+
+x <- df
+x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
+x <- x[which(is.na(x$age)==FALSE),]
+
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+P_R <- x$`Puerto Rico`
+P_R <- 
+  `rownames<-`(
+    `colnames<-`(
+      as.data.frame(
+        rbind(
+          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
+          # ,
+          c(
+             round(mean(P_R$age),digits=2)
+            ,round(sd(P_R$age),digits=2)
+            ,round(mean(P_R$moral_identity_symbolic),digits=2)
+            ,round(sd(P_R$moral_identity_symbolic),digits=2)
+            ,length(P_R$moral_identity_symbolic)
+            ,"-"
+            ,"-"))),
+      c("mean age","SD age","mean symbolization", "SD symbolization","N", "r","p"))
+    ,c("Puerto Rico"))
+
+test <- rbind(test[1:49,],P_R,test[50:length(test$p),])
+test <- test[order(rownames(test) ),]
+
+```
+
+```{r include=TRUE}
+
+apa_table(
+  test
+  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
+  , caption = "Correlation between Age and Symbolization for each Country"
+  , note = "* = sig. at p < .05; ** = sig. at p < .001")
+
+```

### 2023-02-06 H3.Rmd
started H3

--- 2023-02-06 H2.Rmd
@@
 ---
-title: "H2: Age Differences"
+title: "H3: Cultural Differences in Symbolization"
 author: "Mariola Paruzel-Czachura, Cillian McHugh"
@@
 
-```{r setuph2, include=FALSE}
+```{r setuph3, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE)
@@
 
+x <- df
 ```
@@
 
-x <- df
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
+# h3a yes
+# h3b n/a (competing)
+# h3c yes
+# h3d no (no relationship)
+# h3e yes
+# h3f yes
+# h3g no, no, yes
 
-c1 <- cor.test(x$moral_identity_internal,x$age)
+x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
+
+fit <- lm(moral_identity_symbolic ~
+                    # sex3
+                    # + age
+                     Power.Distance
+                    + Individualism
+                    + Masculinity
+                    + Uncertainty.Avoidance
+                    + Long.Term.Orientation
+                    + Indulgence
+                    + CTL_C
+                    + CTL_DS
+                    + CTL_DG
+                , data = x
+            )
+
+summary(fit)
+
+fit_results <- apa_print(fit)
+
+cor.test(x$Power.Distance,x$moral_identity_symbolic)
+
+fit_results$full_result
 
 ```
-
-```{r}
-
-x <- df
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-
-c2 <- cor.test(x$moral_identity_symbolic,x$age)
-
-```
-
-Due to mixed findings in the literature, we did not have specific predictions regarding the relationship between age and moral identity, and the analyses reported here are exploratory.
-Overall there was a significant negative correlation between age and internalization *r* = `r sprintf("%.3f", c1$estimate)`, *p* = `r paste(p_report(c1$p.value))`, suggesting that older participants had lower internalization scores.
-Similarly, we found a significant negative correlation between age and symbolization *r* = `r sprintf("%.3f", c2$estimate)`, *p* = `r paste(p_report(c2$p.value))`, again, suggesting that older participants had lower symbolization scores than younger participants.
-
-```{r}
-x <- df
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-
-model0 <- lmerTest::lmer(moral_identity_internal ~
-                 #  sex_01
-                 # * age
-                  + (1|country)
-                , data = x
-                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-
-model1 <- lmerTest::lmer(moral_identity_internal ~
-                 #  sex_01
-                   age
-                  + (1|country)
-                , data = x
-               # , contrasts = list(sex_01 = contr.sum)
-            )
-summary(model1)
-anova(model0,model1)
-
-summary(model1)
-anova(model1)
-results_anova <- as.data.frame(anova(model0,model1))
-results_anova
-results_anova$Chisq[2]
-results_anova$Df
-p1 <- results_anova$`Pr(>Chisq)`[2]
-p_report(p1)
-#p_report(results_anova$`Pr(>Chisq)`)[2]
-results_anova$AIC
-summary_model1 <- summary(model1)
-summary_model1
-results_coef <- as.data.frame(summary_model1$coefficients)
-results_coef
-
-aov1 <- anova(model1)
-
-f3a <- aov1$`F value`[1]
-p3a <- aov1$`Pr(>F)`[1]
-
-results_coef$Estimate[2]
-results_coef$`Std. Error`[2]
-results_coef$df[2]
-t1 <- results_coef$`t value`[2]
-p2 <- results_coef$`Pr(>|t|)`[2]
-
-#QuantPsyc::lm.beta(results_coef)
-anova(model1)
-
-```
-
-```{r}
-
-x <- df
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-#### group by country for analysis ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-N_fun <- function(x){
-  length(x$sex3)
-}
-total_Ns <- lapply(x, N_fun)
-
-exclusions <- names(total_Ns)[which(total_Ns<3)]
-x <- df
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-cor_fun <- function(x){
-  cor.test(x$moral_identity_symbolic,x$age)
-}
-all_cor_tests <- lapply(x, cor_fun)
-
-all_cor_rs <- function(c){
-  c$estimate
-}
-rs_for_table <- lapply(all_cor_tests, all_cor_rs)
-all_cor_ps <- function(c){
-  c$estimate
-}
-ps_for_table <- lapply(all_cor_tests, all_cor_ps)
-Ns_for_table <- lapply(x, N_fun)
-
-means_INT_fun <- function(x){
-  mean(x$moral_identity_internal)
-}
-mean_int_for_table <- lapply(x, means_INT_fun)
-sd_INT_fun <- function(x){
-  sd(x$moral_identity_internal)
-}
-sd_int_for_table <- lapply(x, sd_INT_fun)
-
-means_age_fun <- function(x){
-  mean(x$age)
-}
-mean_age_for_table <- lapply(x, means_age_fun)
-sd_age_fun <- function(x){
-  sd(x$age)
-}
-sd_age_for_table <- lapply(x, sd_age_fun)
-
-```
-
-```{r}
-test <- 
-  cbind.data.frame(
-     do.call(rbind,mean_age_for_table)
-    ,do.call(rbind,sd_age_for_table)
-    ,do.call(rbind,mean_int_for_table)
-    ,do.call(rbind,sd_int_for_table)
-    ,round(do.call(rbind, rs_for_table),digits=3)
-    ,do.call(rbind, ps_for_table)
-    ,round(do.call(rbind, Ns_for_table))
-    )
-
-test <- `colnames<-`(test, c("mean age","SD age","mean internalization", "SD internalization", "r","p","N"))
-test
-
-sum(unlist(ps_for_table)<.05)
-
-test1 <- subset(test, p < .05)
-test1
-
-total_sig <- length(test1$`mean age`)
-
-neg <- sum(test1$r <0 )
-pos <- sum(test1$r>0)
-
-```
-
-We conducted a linear-mixed-effects model to test if this relationship between age and internalization holds when participants are nested within country.
-Our outcome measure was internalization and our predictor variable was age; we allowed intercepts to vary by country.
-Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
-$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
-There was a significant main effect for age,
-*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
-`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
-with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
-*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
-`r sprintf("%.2f",t1)`,
-*p* `r paste(p_report(p2))`.
-We conducted a series of correlations test if age was related to internalization across all countries.
-There was a significant correlation between age and internalization in `r total_sig` countries.
-Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials Table S_X).
-
-```{r}
-
-x <- df
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-
-model0 <- lmerTest::lmer(moral_identity_symbolic ~
-                 #  sex_01
-                 # * age
-                  + (1|country)
-                , data = x
-                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
-            )
-
-model1 <- lmerTest::lmer(moral_identity_symbolic ~
-                 #  sex_01
-                   age
-                  + (1|country)
-                , data = x
-               # , contrasts = list(sex_01 = contr.sum)
-            )
-summary(model1)
-anova(model0,model1)
-
-summary(model1)
-anova(model1)
-results_anova <- as.data.frame(anova(model0,model1))
-results_anova
-results_anova$Chisq[2]
-results_anova$Df
-p1 <- results_anova$`Pr(>Chisq)`[2]
-p_report(p1)
-#p_report(results_anova$`Pr(>Chisq)`)[2]
-results_anova$AIC
-summary_model1 <- summary(model1)
-summary_model1
-results_coef <- as.data.frame(summary_model1$coefficients)
-results_coef
-
-aov1 <- anova(model1)
-
-f3a <- aov1$`F value`[1]
-p3a <- aov1$`Pr(>F)`[1]
-
-results_coef$Estimate[2]
-results_coef$`Std. Error`[2]
-results_coef$df[2]
-t1 <- results_coef$`t value`[2]
-p2 <- results_coef$`Pr(>|t|)`[2]
-
-#QuantPsyc::lm.beta(results_coef)
-anova(model1)
-
-```
-
-```{r}
-
-x <- df
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-#### group by country for analysis ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-N_fun <- function(x){
-  length(x$sex3)
-}
-total_Ns <- lapply(x, N_fun)
-
-exclusions <- names(total_Ns)[which(total_Ns<3)]
-x <- df
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-cor_fun <- function(x){
-  cor.test(x$moral_identity_symbolic,x$age)
-}
-all_cor_tests <- lapply(x, cor_fun)
-
-all_cor_rs <- function(c){
-  c$estimate
-}
-rs_for_table <- lapply(all_cor_tests, all_cor_rs)
-all_cor_ps <- function(c){
-  c$estimate
-}
-ps_for_table <- lapply(all_cor_tests, all_cor_ps)
-Ns_for_table <- lapply(x, N_fun)
-
-means_INT_fun <- function(x){
-  mean(x$moral_identity_symbolic)
-}
-mean_int_for_table <- lapply(x, means_INT_fun)
-sd_INT_fun <- function(x){
-  sd(x$moral_identity_symbolic)
-}
-sd_int_for_table <- lapply(x, sd_INT_fun)
-
-means_age_fun <- function(x){
-  mean(x$age)
-}
-mean_age_for_table <- lapply(x, means_age_fun)
-sd_age_fun <- function(x){
-  sd(x$age)
-}
-sd_age_for_table <- lapply(x, sd_age_fun)
-
-```
-
-```{r}
-test <- 
-  cbind.data.frame(
-     do.call(rbind,mean_age_for_table)
-    ,do.call(rbind,sd_age_for_table)
-    ,do.call(rbind,mean_int_for_table)
-    ,do.call(rbind,sd_int_for_table)
-    ,round(do.call(rbind, rs_for_table),digits=3)
-    ,do.call(rbind, ps_for_table)
-    ,round(do.call(rbind, Ns_for_table))
-    )
-
-test <- `colnames<-`(test, c("mean age","SD age","mean symbolization", "SD symbolization", "r","p","N"))
-test
-
-sum(unlist(ps_for_table)<.05)
-
-test1 <- subset(test, p < .05)
-test1
-
-total_sig <- length(test1$`mean age`)
-
-neg <- sum(test1$r <0 )
-pos <- sum(test1$r>0)
-
-```
-
-Similarly, for symbolization, we conducted a linear-mixed-effects model to test if the relationship between age and symbolization holds when participants are nested within country.
-Our outcome measure was symbolization and our predictor variable was age; we allowed intercepts to vary by country.
-Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
-$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
-There was a significant main effect for age,
-*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
-`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
-with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
-*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
-`r sprintf("%.2f",t1)`,
-*p* `r paste(p_report(p2))`.
-We conducted a series of correlations test if age was related to internalization across all countries.
-There was a significant correlation between age and internalization in `r total_sig` countries.
-Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials Table S_X).

### 2023-02-06 drafting_supplementary_analysis.Rmd
fixed plots

@@
 ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)
+raw_ps_for_table <- (lapply(all_t_tests, all_t_ps))
 
@@
 
+```{r}
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, female_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, male_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, ts_for_table),digits=2)
+    ,round(do.call(rbind, df_for_table),digits=2)
+    ,do.call(rbind, raw_ps_for_table)
+    ,round(do.call(rbind, ds_for_table),digits=2)
+    )
+
+test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
+test
+
+sig_countries <- rownames(test[which(test$p<.05),])
+```
+
 ```{r internalizationPlot}
 
-# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-# x$sex3 <- droplevels(x$sex3)
-# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-# 
-# #### identify countries with small samples
-# male_length <- function(x){sum(x$sex3=='male')}
-# males <- lapply(x, male_length)
-# female_length <- function(x){sum(x$sex3=='female')}
-# females <- lapply(x, female_length)
-# names(females)
-# 
-# #### generate a vector containing all countries with less than 10 observations for either males or females ####
-# exclusions <- c(names(males[males<2]),
-#   names(females[females<2]))
-# 
-# #### re-load ungrouped data ####
-# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-# x$sex3 <- droplevels(x$sex3)
-# 
-# # and remove missing again
-# sum(is.na(x$moral_identity_internal))
-# x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-# 
-# #### Filter out any countries to be excluded ####
-# x <- subset(x, !(country_name %in% exclusions))
-# 
-# df1 <- x
-# 
-# df1_male <- df1[which(df1$sex3=="male"),]
-# df1_female <- df1[which(df1$sex3=="female"),]
-# 
-# internal_mean_sd <- function(x){
-#   z <- x
-#   z$mean <- mean(z$moral_identity_internal, na.rm=T)
-#   z$sd <- sd(z$moral_identity_internal, na.rm=T)
-#   z
-# }
-# 
-# 
+x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+x$sex3 <- droplevels(x$sex3)
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+#### identify countries with small samples
+male_length <- function(x){sum(x$sex3=='male')}
+males <- lapply(x, male_length)
+female_length <- function(x){sum(x$sex3=='female')}
+females <- lapply(x, female_length)
+names(females)
+
+#### generate a vector containing all countries with less than 10 observations for either males or females ####
+exclusions <- c(names(males[males<2]),
+  names(females[females<2]))
+
+#### re-load ungrouped data ####
+x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+x$sex3 <- droplevels(x$sex3)
+
+# and remove missing again
+sum(is.na(x$moral_identity_internal))
+x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
+
+#### Filter out any countries to be excluded ####
+x <- subset(x, !(country_name %in% exclusions))
+
+df1 <- x
+
+df1_male <- df1[which(df1$sex3=="male"),]
+df1_female <- df1[which(df1$sex3=="female"),]
+
+internal_mean_sd <- function(x){
+  z <- x
+  z$mean <- mean(z$moral_identity_internal, na.rm=T)
+  z$sd <- sd(z$moral_identity_internal, na.rm=T)
+  z
+}
+
 # df1 <- rbind.data.frame(
@@
 # )
+
+loop_sigs_fun3 <- function(y){
+  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
+  else print(df1$country_name[y])
+}
+
+df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))
+
+N_fun <- function(x){
+  length(x$sex3)
+}
+length(df1$sex3)
+x <- df1
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+df1 <- left_join(df1
+                      ,  
+                      `colnames<-`(
+                        cbind.data.frame(
+                          unlist(lapply(x, N_fun))
+                          ,names(unlist(lapply(x, N_fun))))
+                        ,c("N","country_name"))
+                      , by = "country_name")
+
+df1$country_name3 <- print(paste0(df1$country_name2, " (N = ", df1$N, ")"))
+
+df1_male <- df1[which(df1$sex3=="male"),]
+df1_female <- df1[which(df1$sex3=="female"),]
+
+# x <- df1
 # 
-# df1$sex3 <- dplyr::recode(df1$sex3
-#                            , "male" = "Male"
-#                            , "female" = "Female")
-# 
-# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
-#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
-#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
-#   geom_violin(fill = NA) +
-#   #ggforce::geom_sina(size=.01)+
-#   # geom_sina(shape=16
-#   #           , position=position_jitter(height=.25,width=0)
-#   #           , size=.000001
-#   #           , color="dark grey"
-#   #           ,jitter_y=F
-#   # )+
-#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
-#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
-#                 position=position_dodge(0.05), color="#5a5a5a")+
-#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
-#   # stat_summary(geom = "linerange",
-#   #   fun.data = mean_sdl,
-#   #   fun.args = list(mult = 1),
-#   #   colour = "black"
-#   # )+
-#   xlab("Gender")+
-#   ylab("Internalization")+
-#   facet_wrap(~df1$ISO3, ncol = 9 )+
-#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-#   theme_bw() +
-#   theme(panel.border = element_blank(),
-#         axis.line = element_line(size = .2),
-#         strip.background  = element_blank(),
-#         panel.grid = element_blank(),
-#         plot.title=element_text(#family="Times",
-#           size=12
-#         ),
-#         #legend.position="right",
-#         legend.text=element_text(#family="Times",
-#           size=8
-#         ),
-#         legend.title=element_text(#family="Times",
-#           size=10
-#         ),
-#         axis.text=element_text(#family="Times",
-#           colour = "black",
-#           size=8
-#         ),
-#         axis.ticks.x = element_blank(),
-#         axis.title=element_text(#family="Times",
-#           size=12
-#         ),
-#         strip.text=element_text(#family = "Times",
-#           size = 12
-#         ),
-#         # strip.background = element_rect(fill = "white"),
-#         legend.position="none")
-# 
-# ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
+# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+means_fun <- function(x){
+  mean(x$moral_identity_internal)
+}
+sd_fun <- function(x){
+  sd(x$moral_identity_internal)
+}
+
+x <- df1_male
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+df1_male <- left_join(df1_male
+                      ,  
+                      `colnames<-`(
+                        cbind.data.frame(
+                          unlist(lapply(x, means_fun))
+                          ,names(unlist(lapply(x, means_fun))))
+                        ,c("means","country_name"))
+                      , by = "country_name")
+df1_male <- left_join(df1_male
+                      ,  
+                      `colnames<-`(
+                        cbind.data.frame(
+                          unlist(lapply(x, sd_fun))
+                          ,names(unlist(lapply(x, sd_fun))))
+                        ,c("sds","country_name"))
+                      , by = "country_name")
+
+x <- df1_female
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+df1_female <- left_join(df1_female
+                      ,  
+                      `colnames<-`(
+                        cbind.data.frame(
+                          unlist(lapply(x, means_fun))
+                          ,names(unlist(lapply(x, means_fun))))
+                        ,c("means","country_name"))
+                      , by = "country_name")
+df1_female <- left_join(df1_female
+                      ,  
+                      `colnames<-`(
+                        cbind.data.frame(
+                          unlist(lapply(x, sd_fun))
+                          ,names(unlist(lapply(x, sd_fun))))
+                        ,c("sds","country_name"))
+                      , by = "country_name")
+
+df2 <- rbind.data.frame(df1_male,df1_female)
+
+df2$sex3 <- dplyr::recode(df2$sex3
+                           , "male" = "Male"
+                           , "female" = "Female")
+
+g1 <- ggplot(df2,aes(x=sex3,y=moral_identity_internal))+
+  #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
+  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
+  geom_violin(fill = NA) +
+  #ggforce::geom_sina(size=.01)+
+  # geom_sina(shape=16
+  #           , position=position_jitter(height=.25,width=0)
+  #           , size=.000001
+  #           , color="dark grey"
+  #           ,jitter_y=F
+  # )+
+  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
+  geom_errorbar(aes(ymin=means - sds, ymax = means + sds), width=.06,
+                position=position_dodge(0.05), color="#5a5a5a")+
+  stat_summary(fun=mean, geom="point", shape=16, size=1)+
+  # stat_summary(geom = "linerange",
+  #   fun.data = mean_sdl,
+  #   fun.args = list(mult = 1),
+  #   colour = "black"
+  # )+
+  xlab("Gender")+
+  ylab("Internalization")+
+  facet_wrap(~df2$country_name3, ncol = 9 )+
+  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        #panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
 
@@
 
+```{r}
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, female_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, male_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, ts_for_table),digits=2)
+    ,round(do.call(rbind, df_for_table),digits=2)
+    ,do.call(rbind, raw_ps_for_table)
+    ,round(do.call(rbind, ds_for_table),digits=2)
+    )
+
+test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
+test
+
+sig_countries <- rownames(test[which(test$p<.05),])
+```
+
 ```{r symbolizationPlot}
 
-# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-# x$sex3 <- droplevels(x$sex3)
-# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-# 
-# #### identify countries with small samples
-# male_length <- function(x){sum(x$sex3=='male')}
-# males <- lapply(x, male_length)
-# female_length <- function(x){sum(x$sex3=='female')}
-# females <- lapply(x, female_length)
-# names(females)
-# 
-# #### generate a vector containing all countries with less than 10 observations for either males or females ####
-# exclusions <- c(names(males[males<2]),
-#   names(females[females<2]))
-# 
-# #### re-load ungrouped data ####
-# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-# x$sex3 <- droplevels(x$sex3)
-# 
-# # and remove missing again
-# sum(is.na(x$moral_identity_symbolic))
-# x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-# 
-# #### Filter out any countries to be excluded ####
-# x <- subset(x, !(country_name %in% exclusions))
-# 
-# df1 <- x
-# 
-# df1_male <- df1[which(df1$sex3=="male"),]
-# df1_female <- df1[which(df1$sex3=="female"),]
-# 
-# internal_mean_sd <- function(x){
-#   z <- x
-#   z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
-#   z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
-#   z
-# }
-# 
-# 
+x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+x$sex3 <- droplevels(x$sex3)
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+#### identify countries with small samples
+male_length <- function(x){sum(x$sex3=='male')}
+males <- lapply(x, male_length)
+female_length <- function(x){sum(x$sex3=='female')}
+females <- lapply(x, female_length)
+names(females)
+
+#### generate a vector containing all countries with less than 10 observations for either males or females ####
+exclusions <- c(names(males[males<2]),
+  names(females[females<2]))
+
+#### re-load ungrouped data ####
+x <- df[which(df$sex3=="male"|df$sex3=="female"),]
+x$sex3 <- droplevels(x$sex3)
+
+# and remove missing again
+sum(is.na(x$moral_identity_symbolic))
+x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
+
+#### Filter out any countries to be excluded ####
+x <- subset(x, !(country_name %in% exclusions))
+
+df1 <- x
+
+df1_male <- df1[which(df1$sex3=="male"),]
+df1_female <- df1[which(df1$sex3=="female"),]
+
+internal_mean_sd <- function(x){
+  z <- x
+  z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
+  z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
+  z
+}
+
 # df1 <- rbind.data.frame(
@@
 # )
+
+loop_sigs_fun3 <- function(y){
+  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
+  else print(df1$country_name[y])
+}
+
+df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))
+
+N_fun <- function(x){
+  length(x$sex3)
+}
+length(df1$sex3)
+x <- df1
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+df1 <- left_join(df1
+                      ,  
+                      `colnames<-`(
+                        cbind.data.frame(
+                          unlist(lapply(x, N_fun))
+                          ,names(unlist(lapply(x, N_fun))))
+                        ,c("N","country_name"))
+                      , by = "country_name")
+
+df1$country_name3 <- print(paste0(df1$country_name2, " (N = ", df1$N,")"))
+
+df1_male <- df1[which(df1$sex3=="male"),]
+df1_female <- df1[which(df1$sex3=="female"),]
+
+# x <- df1
 # 
-# df1$sex3 <- dplyr::recode(df1$sex3
-#                            , "male" = "Male"
-#                            , "female" = "Female")
-# 
-# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
-#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
-#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
-#   geom_violin(fill = NA) +
-#   #ggforce::geom_sina(size=.01)+
-#   # geom_sina(shape=16
-#   #           , position=position_jitter(height=.25,width=0)
-#   #           , size=.000001
-#   #           , color="dark grey"
-#   #           ,jitter_y=F
-#   # )+
-#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
-#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
-#                 position=position_dodge(0.05), color="#5a5a5a")+
-#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
-#   # stat_summary(geom = "linerange",
-#   #   fun.data = mean_sdl,
-#   #   fun.args = list(mult = 1),
-#   #   colour = "black"
-#   # )+
-#   xlab("Gender")+
-#   ylab("Symbolization")+
-#   facet_wrap(~df1$ISO3, ncol = 9 )+
-#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-#   theme_bw() +
-#   theme(panel.border = element_blank(),
-#         axis.line = element_line(size = .2),
-#         strip.background  = element_blank(),
-#         panel.grid = element_blank(),
-#         plot.title=element_text(#family="Times",
-#           size=12
-#         ),
-#         #legend.position="right",
-#         legend.text=element_text(#family="Times",
-#           size=8
-#         ),
-#         legend.title=element_text(#family="Times",
-#           size=10
-#         ),
-#         axis.text=element_text(#family="Times",
-#           colour = "black",
-#           size=8
-#         ),
-#         axis.ticks.x = element_blank(),
-#         axis.title=element_text(#family="Times",
-#           size=12
-#         ),
-#         strip.text=element_text(#family = "Times",
-#           size = 12
-#         ),
-#         # strip.background = element_rect(fill = "white"),
-#         legend.position="none")
-# 
-# #g1
-# 
-# ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
-# #g2
+# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+means_fun <- function(x){
+  mean(x$moral_identity_symbolic)
+}
+
+sd_fun <- function(x){
+  sd(x$moral_identity_symbolic)
+}
+
+x <- df1_male
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+df1_male <- left_join(df1_male
+                      ,  
+                      `colnames<-`(
+                        cbind.data.frame(
+                          unlist(lapply(x, means_fun))
+                          ,names(unlist(lapply(x, means_fun))))
+                        ,c("means","country_name"))
+                      , by = "country_name")
+df1_male <- left_join(df1_male
+                      ,  
+                      `colnames<-`(
+                        cbind.data.frame(
+                          unlist(lapply(x, sd_fun))
+                          ,names(unlist(lapply(x, sd_fun))))
+                        ,c("sds","country_name"))
+                      , by = "country_name")
+
+x <- df1_female
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+df1_female <- left_join(df1_female
+                      ,  
+                      `colnames<-`(
+                        cbind.data.frame(
+                          unlist(lapply(x, means_fun))
+                          ,names(unlist(lapply(x, means_fun))))
+                        ,c("means","country_name"))
+                      , by = "country_name")
+df1_female <- left_join(df1_female
+                      ,  
+                      `colnames<-`(
+                        cbind.data.frame(
+                          unlist(lapply(x, sd_fun))
+                          ,names(unlist(lapply(x, sd_fun))))
+                        ,c("sds","country_name"))
+                      , by = "country_name")
+
+df2 <- rbind.data.frame(df1_male,df1_female)
+
+df2$sex3 <- dplyr::recode(df2$sex3
+                           , "male" = "Male"
+                           , "female" = "Female")
+
+g1 <- ggplot(df2,aes(x=sex3,y=moral_identity_symbolic))+
+  #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
+  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
+  geom_violin(fill = NA) +
+  #ggforce::geom_sina(size=.01)+
+  # geom_sina(shape=16
+  #           , position=position_jitter(height=.25,width=0)
+  #           , size=.000001
+  #           , color="dark grey"
+  #           ,jitter_y=F
+  # )+
+  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
+  geom_errorbar(aes(ymin=means - sds, ymax = means + sds), width=.06,
+                position=position_dodge(0.05), color="#5a5a5a")+
+  stat_summary(fun=mean, geom="point", shape=16, size=1)+
+  # stat_summary(geom = "linerange",
+  #   fun.data = mean_sdl,
+  #   fun.args = list(mult = 1),
+  #   colour = "black"
+  # )+
+  xlab("Gender")+
+  ylab("Internalization")+
+  facet_wrap(~df2$country_name3, ncol = 9 )+
+  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        #panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
+#g2
 ```
@@
 
+```{r}
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind,mean_age_for_table),digits = 2)
+    ,round(do.call(rbind,sd_age_for_table),digits = 2)
+    ,round(do.call(rbind,mean_int_for_table),digits = 2)
+    ,round(do.call(rbind,sd_int_for_table),digits = 2)
+    ,round(do.call(rbind, Ns_for_table))
+    ,round(do.call(rbind, rs_for_table),digits=3)
+    ,do.call(rbind, ps_for_table)
+    )
+
+test <- `colnames<-`(test, c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
+test
+
+sig_countries <- rownames(test[which(test$p<.05),])
+
+# loop_sigs_fun <- function(x){
+#   if(rownames(test)[x] %in% sig_countries) print(paste0(rownames(test)[x],"*"),quote = FALSE)
+#   else print(rownames(test)[x])
+# }
+# 
+# rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_sigs_fun))
+# 
+# loop_sigs_fun2 <- function(x,y){
+#   if(x$country_name[y] %in% sig_countries) print(paste0(x$country_name[y],"*"),quote = FALSE)
+#   else print(x$country_name[y])
+# }
+
+```
+
+```{r}
+
+df1 <- subset(df, !(country_name %in% exclusions))
+
+loop_sigs_fun3 <- function(y){
+  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
+  else print(df1$country_name[y])
+}
+
+df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))
+
+ggplot(df1, aes(age, moral_identity_internal))+
+  geom_jitter(size=.05, color='darkgrey') + 
+  #ylim(0,12) +
+  geom_smooth(method=lm, size = .5,color='black') +
+  labs(y = "Internalization",
+       x = "Age"
+  )+ 
+  theme_apa()+
+  theme_bw()+
+  theme(plot.title=element_text(#family="Times",
+    size=12
+  ),
+  legend.text=element_text(#family="Times",
+    size=8
+  ),
+  legend.title=element_text(#family="Times",
+    size=10
+  ),
+  axis.text=element_text(#family="Times",
+    colour = "black",
+    size=8
+  ),
+  axis.ticks.x = element_blank(),
+  axis.title=element_text(#family="Times",
+    size=12
+  ),
+  strip.text=element_text(#family = "Times",
+    size = 12
+  ),
+  strip.background = element_rect(fill = "white"),
+  legend.position="right")+
+  facet_wrap(~df1$country_name2, ncol = 9 )
+```
+
 ## Age & Symbolization

### 2023-02-06 drafting_supplementary_analysis.Rmd
tidied up all plots, added * and N

--- 2023-02-05 drafting_supplementary_analysis.Rmd
@@
 
-# H1 Gender Differences
+# Gender
 
-## Internalization
-
-```{r}
-
-ps <- function(y){
-  y <- round(y, digits = 3)
-  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
-  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
-        y, quote = FALSE)),"*"))
-  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
-        y)))}
-
-#### ensure correct data is loaded ####
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-#### remove any missing data #### 
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-table(x$country_name,x$sex3)
-x$country_name
-
-#### group by country ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-#### identify countries with small samples
-male_length <- function(x){sum(x$sex3=='male')}
-males <- lapply(x, male_length)
-female_length <- function(x){sum(x$sex3=='female')}
-females <- lapply(x, female_length)
-names(females)
-
-#### generate a vector containing all countries with less than 10 observations for either males or females ####
-exclusions <- c(names(males[males<2]),
-  names(females[females<2]))
-
-#### re-load ungrouped data ####
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-
-#### Filter out any countries to be excluded ####
-x <- subset(x, !(country_name %in% exclusions))
-
-#### group by country for analysis ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-ttest_fun <- function(x){
-  t.test(moral_identity_internal ~ sex3, data = x)
-}
-all_t_tests <- lapply(x, ttest_fun)
-
-# Means and Standard Deviations
-means_fun <- function(x){
-  mean(x$moral_identity_internal)
-}
-lapply(x, means_fun)
-sd_fun <- function(x){
-  sd(x$moral_identity_internal)
-}
-lapply(x, sd_fun)
-
-N_fun <- function(x){
-  length(x$sex3)
-}
-total_Ns <- lapply(x, N_fun)
-
-# Statistics for table
-# Cohen's d
-cohens_d_fun <- function(x){
-  cohen.d(x$moral_identity_symbolic, x$sex3)
-}
-all_ds <- lapply(x, cohens_d_fun)
-show_d_fun <- function(x){
-  x$cohen.d[2]
-}
-ds_for_table <- lapply(all_ds, show_d_fun)
-
-# t statistic
-all_t_stats <- function(t){
-  t$statistic
-}
-ts_for_table <- lapply(all_t_tests, all_t_stats)
-
-# df
-all_t_df <- function(t){
-  t$parameter
-}
-df_for_table <- lapply(all_t_tests, all_t_df)
-
-# p value
-all_t_ps <- function(t){
-  t$p.value
-}
-ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)
-
-sum(unlist(lapply(all_t_tests, all_t_ps))<.05)
-
-#### means for Males ####
-# re-load ungrouped data #
-x <- df[which(df$sex3=="male"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-male_means <- lapply(x, means_fun)
-male_sds <- lapply(x, sd_fun)
-male_Ns <- lapply(x, N_fun)
-
-#### means for Females
-# re-load ungrouped data #
-x <- df[which(df$sex3=="female"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-female_means <- lapply(x, means_fun)
-female_sds <- lapply(x, sd_fun)
-female_Ns <- lapply(x, N_fun)
+```{r child = 'supp_H1.Rmd'}
 
@@
 
-### Internalization Ns
+# Age
 
-```{r}
-#### Total Ns
-x <- df[which(df$sex3=="male"
-              |df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-total_Ns <- lapply(x, N_fun)
-
-#### Ns for Males 
-# re-load ungrouped data #
-x <- df[which(df$sex3=="male"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-male_Ns <- lapply(x, N_fun)
-
-#### Ns for Females
-# re-load ungrouped data #
-x <- df[which(df$sex3=="female"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-female_Ns <- lapply(x, N_fun)
-
-test <- 
-  cbind.data.frame(do.call(rbind, total_Ns)
-                 ,do.call(rbind, female_Ns)
-                 ,do.call(rbind, male_Ns))
-
-test <- `colnames<-`(test, c("Total N","n Female","N male"))
-
-loop_exclusions_fun <- function(x){
-  if(rownames(test)[x] %in% exclusions) print(paste0(rownames(test)[x],"*"),quote = FALSE)
-  else print(rownames(test)[x])
-  }
-
-rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_exclusions_fun))
-test
-test <- test[order(rownames(test) ),]
+```{r child = 'supp_H2.Rmd'}
 
 ```
-
-```{r include=TRUE}
-
-apa_table(
-  test
-  , align = c("c", "c", "c")
-  , caption = "Total samples for each country for Internalization analysis"
-  , note = "* = sample too small to be included in analysis below")
-
-```
-
-### Internalization Table
-
-```{r}
-
-test <- 
-  cbind.data.frame(
-     round(do.call(rbind, female_means),digits=2)
-    ,round(do.call(rbind, female_sds),digits=2)
-    ,round(do.call(rbind, male_means),digits=2)
-    ,round(do.call(rbind, female_sds),digits=2)
-    ,round(do.call(rbind, ts_for_table),digits=2)
-    ,round(do.call(rbind, df_for_table),digits=2)
-    ,do.call(rbind, ps_for_table)
-    ,round(do.call(rbind, ds_for_table),digits=2)
-    )
-
-test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
-test
-
-x <- df[which(df$sex3=="male"
-              |df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_internal))
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-total_Ns <- lapply(x, N_fun)
-
-P_R <- x$`Puerto Rico`
-P_R <- 
-  `rownames<-`(
-    `colnames<-`(
-      as.data.frame(
-        rbind(
-          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
-          # ,
-          c(
-            P_R$moral_identity_internal[which(P_R$sex3=="male")]
-            ,"-"
-            ,P_R$moral_identity_internal[which(P_R$sex3=="female")]
-            ,"-"
-            ,"-"
-            ,"-"
-            ,"-"
-            ,"-"))),
-      c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
-    ,c("Puerto Rico"))
-
-test <- rbind(test[1:49,],P_R,test[50:length(test$`mean F`),])
-test <- test[order(rownames(test) ),]
-
-```
-
-```{r include=TRUE}
-
-apa_table(
-  test
-  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
-  , caption = "Gender differences in Internalization for each Country"
-  , note = "* = sig. at p < .05; ** = sig. at p < .001")
-
-```
-
-### Internalization Plot
-
-(<a href="https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/internalization.png" target="_blank">open in new window</a>)
-
-```{r internalizationPlot}
-
-# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-# x$sex3 <- droplevels(x$sex3)
-# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-# 
-# #### identify countries with small samples
-# male_length <- function(x){sum(x$sex3=='male')}
-# males <- lapply(x, male_length)
-# female_length <- function(x){sum(x$sex3=='female')}
-# females <- lapply(x, female_length)
-# names(females)
-# 
-# #### generate a vector containing all countries with less than 10 observations for either males or females ####
-# exclusions <- c(names(males[males<2]),
-#   names(females[females<2]))
-# 
-# #### re-load ungrouped data ####
-# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-# x$sex3 <- droplevels(x$sex3)
-# 
-# # and remove missing again
-# sum(is.na(x$moral_identity_internal))
-# x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-# 
-# #### Filter out any countries to be excluded ####
-# x <- subset(x, !(country_name %in% exclusions))
-# 
-# df1 <- x
-# 
-# df1_male <- df1[which(df1$sex3=="male"),]
-# df1_female <- df1[which(df1$sex3=="female"),]
-# 
-# internal_mean_sd <- function(x){
-#   z <- x
-#   z$mean <- mean(z$moral_identity_internal, na.rm=T)
-#   z$sd <- sd(z$moral_identity_internal, na.rm=T)
-#   z
-# }
-# 
-# 
-# df1 <- rbind.data.frame(
-#   internal_mean_sd(df1_female),
-#   internal_mean_sd(df1_male)
-# )
-# 
-# df1$sex3 <- dplyr::recode(df1$sex3
-#                            , "male" = "Male"
-#                            , "female" = "Female")
-# 
-# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
-#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
-#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
-#   geom_violin(fill = NA) +
-#   #ggforce::geom_sina(size=.01)+
-#   # geom_sina(shape=16
-#   #           , position=position_jitter(height=.25,width=0)
-#   #           , size=.000001
-#   #           , color="dark grey"
-#   #           ,jitter_y=F
-#   # )+
-#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
-#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
-#                 position=position_dodge(0.05), color="#5a5a5a")+
-#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
-#   # stat_summary(geom = "linerange",
-#   #   fun.data = mean_sdl,
-#   #   fun.args = list(mult = 1),
-#   #   colour = "black"
-#   # )+
-#   xlab("Gender")+
-#   ylab("Internalization")+
-#   facet_wrap(~df1$ISO3, ncol = 9 )+
-#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-#   theme_bw() +
-#   theme(panel.border = element_blank(),
-#         axis.line = element_line(size = .2),
-#         strip.background  = element_blank(),
-#         panel.grid = element_blank(),
-#         plot.title=element_text(#family="Times",
-#           size=12
-#         ),
-#         #legend.position="right",
-#         legend.text=element_text(#family="Times",
-#           size=8
-#         ),
-#         legend.title=element_text(#family="Times",
-#           size=10
-#         ),
-#         axis.text=element_text(#family="Times",
-#           colour = "black",
-#           size=8
-#         ),
-#         axis.ticks.x = element_blank(),
-#         axis.title=element_text(#family="Times",
-#           size=12
-#         ),
-#         strip.text=element_text(#family = "Times",
-#           size = 12
-#         ),
-#         # strip.background = element_rect(fill = "white"),
-#         legend.position="none")
-# 
-# ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
-
-```
-
-```{r, InternalizationGender,fig.cap="Gender differences in Internalization for each country",include=TRUE}
-#suppressWarnings(print(g1))
-
-```
-
-<style>
-#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
-#scaled-frame { width: 250%; height: 900px; border: 1px; }
-#scaled-frame {
-    zoom: 0.50;
-    -moz-transform: scale(0.50);
-    -moz-transform-origin: 0 0;
-    -o-transform: scale(0.50);
-    -o-transform-origin: 0 0;
-    -webkit-transform: scale(0.50);
-    -webkit-transform-origin: 0 0;
-}
-
-@media screen and (-webkit-min-device-pixel-ratio:0) {
- #scaled-frame  { zoom: 1;  }
-}
-</style>
-
-<div id="wrapper"><iframe id="scaled-frame" src="plots/internalization.png"></iframe></div>
-
-## Symbolization
-
-```{r}
-
-ps <- function(y){
-  y <- round(y, digits = 3)
-  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
-  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
-        y, quote = FALSE)),"*"))
-  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
-        y)))}
-
-#### ensure correct data is loaded ####
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-#### remove any missing data #### 
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-table(x$country_name,x$sex3)
-x$country_name
-
-#### group by country ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-#### identify countries with small samples
-male_length <- function(x){sum(x$sex3=='male')}
-males <- lapply(x, male_length)
-female_length <- function(x){sum(x$sex3=='female')}
-females <- lapply(x, female_length)
-names(females)
-
-#### generate a vector containing all countries with less than 10 observations for either males or females ####
-exclusions <- c(names(males[males<2]),
-  names(females[females<2]))
-
-#### re-load ungrouped data ####
-x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-
-#### Filter out any countries to be excluded ####
-x <- subset(x, !(country_name %in% exclusions))
-
-#### group by country for analysis ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-ttest_fun <- function(x){
-  t.test(moral_identity_symbolic ~ sex3, data = x)
-}
-all_t_tests <- lapply(x, ttest_fun)
-
-means_fun <- function(x){
-  mean(x$moral_identity_symbolic)
-}
-lapply(x, means_fun)
-sd_fun <- function(x){
-  sd(x$moral_identity_symbolic)
-}
-lapply(x, sd_fun)
-
-cohens_d_fun <- function(x){
-  cohen.d(x$moral_identity_symbolic, x$sex3)
-}
-all_ds <- lapply(x, cohens_d_fun)
-show_d_fun <- function(x){
-  x$cohen.d[2]
-}
-ds_for_table <- lapply(all_ds, show_d_fun)
-
-all_t_stats <- function(t){
-  t$statistic
-}
-ts_for_table <- lapply(all_t_tests, all_t_stats)
-
-all_t_df <- function(t){
-  t$parameter
-}
-df_for_table <- lapply(all_t_tests, all_t_df)
-
-all_t_ps <- function(t){
-  t$p.value
-}
-ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)
-
-total_sig <- sum(unlist(lapply(all_t_tests, all_t_ps))<.05)
-
-#### means for Males ####
-# re-load ungrouped data #
-x <- df[which(df$sex3=="male"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-male_means <- lapply(x, means_fun)
-male_sds <- lapply(x, sd_fun)
-
-#### means for Females
-# re-load ungrouped data #
-x <- df[which(df$sex3=="female"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-female_means <- lapply(x, means_fun)
-female_sds <- lapply(x, sd_fun)
-
-```
-
-### Symbolization Ns
-
-```{r}
-#### Total Ns
-x <- df[which(df$sex3=="male"
-              |df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-total_Ns <- lapply(x, N_fun)
-
-#### Ns for Males 
-# re-load ungrouped data #
-x <- df[which(df$sex3=="male"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-male_Ns <- lapply(x, N_fun)
-
-#### Ns for Females
-# re-load ungrouped data #
-x <- df[which(df$sex3=="female"
-              #|df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-# and remove missing again
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-female_Ns <- lapply(x, N_fun)
-
-test <- 
-  cbind.data.frame(do.call(rbind, total_Ns)
-                 ,do.call(rbind, female_Ns)
-                 ,do.call(rbind, male_Ns))
-
-test <- `colnames<-`(test, c("Total N","n Female","N male"))
-
-loop_exclusions_fun <- function(x){
-  if(rownames(test)[x] %in% exclusions) print(paste0(rownames(test)[x],"*"),quote = FALSE)
-  else print(rownames(test)[x])
-  }
-
-rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_exclusions_fun))
-test
-#test <-
-test[order(rownames(test) ),]
-
-```
-
-```{r include=TRUE}
-
-apa_table(
-  test
-  , align = c("c", "c", "c")
-  , caption = "Total samples for each country for Symbolization analysis"
-  , note = "* = sample too small to be included in analysis below")
-
-```
-
-### Symbolization Table
-
-```{r}
-
-test <- 
-  cbind.data.frame(
-     round(do.call(rbind, female_means),digits=2)
-    ,round(do.call(rbind, female_sds),digits=2)
-    ,round(do.call(rbind, male_means),digits=2)
-    ,round(do.call(rbind, female_sds),digits=2)
-    ,round(do.call(rbind, ts_for_table),digits=2)
-    ,round(do.call(rbind, df_for_table),digits=2)
-    ,do.call(rbind, ps_for_table)
-    ,round(do.call(rbind, ds_for_table),digits=2)
-    )
-
-test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
-test
-
-x <- df[which(df$sex3=="male"
-              |df$sex3=="female"
-              ),]
-x$sex3 <- droplevels(x$sex3)
-
-# and remove missing again
-sum(is.na(x$moral_identity_symbolic))
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-total_Ns <- lapply(x, N_fun)
-
-P_R <- x$`Puerto Rico`
-P_R <- 
-  `rownames<-`(
-    `colnames<-`(
-      as.data.frame(
-        rbind(
-          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
-          # ,
-          c(
-            P_R$moral_identity_symbolic[which(P_R$sex3=="male")]
-            ,"-"
-            ,P_R$moral_identity_symbolic[which(P_R$sex3=="female")]
-            ,"-"
-            ,"-"
-            ,"-"
-            ,"-"
-            ,"-"))),
-      c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
-    ,c("Puerto Rico"))
-
-test <- rbind(test[1:49,],P_R,test[50:length(test$`mean F`),])
-test <- test[order(rownames(test) ),]
-
-```
-
-```{r include=TRUE}
-
-apa_table(
-  test
-  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
-  , caption = "Gender differences in Symbolization for each Country"
-  , note = "* = sig. at p < .05; ** = sig. at p < .001")
-
-```
-
-### Symbolization Plot
-
-(<a href="https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/symbolization.png" target="_blank">open in new window</a>)
-
-```{r symbolizationPlot}
-
-# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-# x$sex3 <- droplevels(x$sex3)
-# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-# 
-# #### identify countries with small samples
-# male_length <- function(x){sum(x$sex3=='male')}
-# males <- lapply(x, male_length)
-# female_length <- function(x){sum(x$sex3=='female')}
-# females <- lapply(x, female_length)
-# names(females)
-# 
-# #### generate a vector containing all countries with less than 10 observations for either males or females ####
-# exclusions <- c(names(males[males<2]),
-#   names(females[females<2]))
-# 
-# #### re-load ungrouped data ####
-# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
-# x$sex3 <- droplevels(x$sex3)
-# 
-# # and remove missing again
-# sum(is.na(x$moral_identity_symbolic))
-# x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-# 
-# #### Filter out any countries to be excluded ####
-# x <- subset(x, !(country_name %in% exclusions))
-# 
-# df1 <- x
-# 
-# df1_male <- df1[which(df1$sex3=="male"),]
-# df1_female <- df1[which(df1$sex3=="female"),]
-# 
-# internal_mean_sd <- function(x){
-#   z <- x
-#   z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
-#   z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
-#   z
-# }
-# 
-# 
-# df1 <- rbind.data.frame(
-#   internal_mean_sd(df1_female),
-#   internal_mean_sd(df1_male)
-# )
-# 
-# df1$sex3 <- dplyr::recode(df1$sex3
-#                            , "male" = "Male"
-#                            , "female" = "Female")
-# 
-# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
-#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
-#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
-#   geom_violin(fill = NA) +
-#   #ggforce::geom_sina(size=.01)+
-#   # geom_sina(shape=16
-#   #           , position=position_jitter(height=.25,width=0)
-#   #           , size=.000001
-#   #           , color="dark grey"
-#   #           ,jitter_y=F
-#   # )+
-#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
-#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
-#                 position=position_dodge(0.05), color="#5a5a5a")+
-#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
-#   # stat_summary(geom = "linerange",
-#   #   fun.data = mean_sdl,
-#   #   fun.args = list(mult = 1),
-#   #   colour = "black"
-#   # )+
-#   xlab("Gender")+
-#   ylab("Internalization")+
-#   facet_wrap(~df1$ISO3, ncol = 9 )+
-#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
-#   theme_bw() +
-#   theme(panel.border = element_blank(),
-#         axis.line = element_line(size = .2),
-#         strip.background  = element_blank(),
-#         panel.grid = element_blank(),
-#         plot.title=element_text(#family="Times",
-#           size=12
-#         ),
-#         #legend.position="right",
-#         legend.text=element_text(#family="Times",
-#           size=8
-#         ),
-#         legend.title=element_text(#family="Times",
-#           size=10
-#         ),
-#         axis.text=element_text(#family="Times",
-#           colour = "black",
-#           size=8
-#         ),
-#         axis.ticks.x = element_blank(),
-#         axis.title=element_text(#family="Times",
-#           size=12
-#         ),
-#         strip.text=element_text(#family = "Times",
-#           size = 12
-#         ),
-#         # strip.background = element_rect(fill = "white"),
-#         legend.position="none")
-# 
-# #g1
-# 
-# ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
-#g2
-```
-
-```{r, SymbolizationGender,fig.cap="Gender differences in Symbolization for each country",include=TRUE}
-#suppressWarnings(print(g1))
-
-```
-
-<style>
-#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
-#scaled-frame { width: 250%; height: 900px; border: 1px; }
-#scaled-frame {
-    zoom: 0.50;
-    -moz-transform: scale(0.50);
-    -moz-transform-origin: 0 0;
-    -o-transform: scale(0.50);
-    -o-transform-origin: 0 0;
-    -webkit-transform: scale(0.50);
-    -webkit-transform-origin: 0 0;
-}
-
-@media screen and (-webkit-min-device-pixel-ratio:0) {
- #scaled-frame  { zoom: 1;  }
-}
-</style>
-
-<div id="wrapper"><iframe id="scaled-frame" src="plots/internalization.png"></iframe></div>

### 2023-02-06 supp_H1.Rmd
tidied up all plots, added * and N

---
title: "H1 Supplement"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }

</style>

```{r setuph1supp, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
```

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)
```

```{r}

#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

df$sex3 <- as.factor(df$sex1)
df$sex3 <- dplyr::recode(df$sex3,
               "1"="male"
              ,"2"="female"
              ,"3"="other")

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
```

## Internalization

```{r}

ps <- function(y){
  y <- round(y, digits = 3)
  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y, quote = FALSE)),"*"))
  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y)))}

#### ensure correct data is loaded ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

#### remove any missing data #### 
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
table(x$country_name,x$sex3)
x$country_name

#### group by country ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

#### identify countries with small samples
male_length <- function(x){sum(x$sex3=='male')}
males <- lapply(x, male_length)
female_length <- function(x){sum(x$sex3=='female')}
females <- lapply(x, female_length)
names(females)

#### generate a vector containing all countries with less than 10 observations for either males or females ####
exclusions <- c(names(males[males<2]),
  names(females[females<2]))

#### re-load ungrouped data ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]

#### Filter out any countries to be excluded ####
x <- subset(x, !(country_name %in% exclusions))

#### group by country for analysis ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

ttest_fun <- function(x){
  t.test(moral_identity_internal ~ sex3, data = x)
}
all_t_tests <- lapply(x, ttest_fun)

# Means and Standard Deviations
means_fun <- function(x){
  mean(x$moral_identity_internal)
}
lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal)
}
lapply(x, sd_fun)

N_fun <- function(x){
  length(x$sex3)
}
total_Ns <- lapply(x, N_fun)

# Statistics for table
# Cohen's d
cohens_d_fun <- function(x){
  cohen.d(x$moral_identity_symbolic, x$sex3)
}
all_ds <- lapply(x, cohens_d_fun)
show_d_fun <- function(x){
  x$cohen.d[2]
}
ds_for_table <- lapply(all_ds, show_d_fun)

# t statistic
all_t_stats <- function(t){
  t$statistic
}
ts_for_table <- lapply(all_t_tests, all_t_stats)

# df
all_t_df <- function(t){
  t$parameter
}
df_for_table <- lapply(all_t_tests, all_t_df)

# p value
all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)
raw_ps_for_table <- (lapply(all_t_tests, all_t_ps))

sum(unlist(lapply(all_t_tests, all_t_ps))<.05)

#### means for Males ####
# re-load ungrouped data #
x <- df[which(df$sex3=="male"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
male_means <- lapply(x, means_fun)
male_sds <- lapply(x, sd_fun)
male_Ns <- lapply(x, N_fun)

#### means for Females
# re-load ungrouped data #
x <- df[which(df$sex3=="female"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
female_means <- lapply(x, means_fun)
female_sds <- lapply(x, sd_fun)
female_Ns <- lapply(x, N_fun)

```

### Internalization Ns

```{r}
#### Total Ns
x <- df[which(df$sex3=="male"
              |df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
total_Ns <- lapply(x, N_fun)

#### Ns for Males 
# re-load ungrouped data #
x <- df[which(df$sex3=="male"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
male_Ns <- lapply(x, N_fun)

#### Ns for Females
# re-load ungrouped data #
x <- df[which(df$sex3=="female"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)
# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
female_Ns <- lapply(x, N_fun)

test <- 
  cbind.data.frame(do.call(rbind, total_Ns)
                 ,do.call(rbind, female_Ns)
                 ,do.call(rbind, male_Ns))

test <- `colnames<-`(test, c("Total N","n Female","N male"))

loop_exclusions_fun <- function(x){
  if(rownames(test)[x] %in% exclusions) print(paste0(rownames(test)[x],"*"),quote = FALSE)
  else print(rownames(test)[x])
  }

rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_exclusions_fun))
test
test <- test[order(rownames(test) ),]

```

```{r include=TRUE}

apa_table(
  test
  , align = c("c", "c", "c")
  , caption = "Total samples for each country for Internalization analysis"
  , note = "* = sample too small to be included in analysis below")

```

### Internalization Table

```{r}

test <- 
  cbind.data.frame(
     round(do.call(rbind, female_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, male_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, ts_for_table),digits=2)
    ,round(do.call(rbind, df_for_table),digits=2)
    ,round(do.call(rbind, ds_for_table),digits=2)
    ,do.call(rbind, ps_for_table)
    )

test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","d","p"))
test

x <- df[which(df$sex3=="male"
              |df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
total_Ns <- lapply(x, N_fun)

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
            P_R$moral_identity_internal[which(P_R$sex3=="male")]
            ,"-"
            ,P_R$moral_identity_internal[which(P_R$sex3=="female")]
            ,"-"
            ,"-"
            ,"-"
            ,"-"
            ,"-"))),
      c("mean F","SD F","mean M", "SD M", "t","df","d","p"))
    ,c("Puerto Rico"))

test <- rbind(test[1:49,],P_R,test[50:length(test$`mean F`),])
test <- test[order(rownames(test) ),]

```

```{r include=TRUE}

apa_table(
  test
  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
  , caption = "Gender differences in Internalization for each Country"
  , note = "* = sig. at p < .05; ** = sig. at p < .001")

```

### Internalization Plot

(<a href="https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/internalization.png" target="_blank">open in new window</a>)

```{r}

test <- 
  cbind.data.frame(
     round(do.call(rbind, female_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, male_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, ts_for_table),digits=2)
    ,round(do.call(rbind, df_for_table),digits=2)
    ,do.call(rbind, raw_ps_for_table)
    ,round(do.call(rbind, ds_for_table),digits=2)
    )

test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
test

sig_countries <- rownames(test[which(test$p<.05),])
```

```{r internalizationPlot}

x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

#### identify countries with small samples
male_length <- function(x){sum(x$sex3=='male')}
males <- lapply(x, male_length)
female_length <- function(x){sum(x$sex3=='female')}
females <- lapply(x, female_length)
names(females)

#### generate a vector containing all countries with less than 10 observations for either males or females ####
exclusions <- c(names(males[males<2]),
  names(females[females<2]))

#### re-load ungrouped data ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]

#### Filter out any countries to be excluded ####
x <- subset(x, !(country_name %in% exclusions))

df1 <- x

df1_male <- df1[which(df1$sex3=="male"),]
df1_female <- df1[which(df1$sex3=="female"),]

internal_mean_sd <- function(x){
  z <- x
  z$mean <- mean(z$moral_identity_internal, na.rm=T)
  z$sd <- sd(z$moral_identity_internal, na.rm=T)
  z
}

# df1 <- rbind.data.frame(
#   internal_mean_sd(df1_female),
#   internal_mean_sd(df1_male)
# )

loop_sigs_fun3 <- function(y){
  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
  else print(df1$country_name[y])
}

df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))

N_fun <- function(x){
  length(x$sex3)
}
length(df1$sex3)
x <- df1
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1 <- left_join(df1
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, N_fun))
                          ,names(unlist(lapply(x, N_fun))))
                        ,c("N","country_name"))
                      , by = "country_name")

df1$country_name3 <- print(paste0(df1$country_name2, " (N = ", df1$N, ")"))

df1_male <- df1[which(df1$sex3=="male"),]
df1_female <- df1[which(df1$sex3=="female"),]

# x <- df1
# 
# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

means_fun <- function(x){
  mean(x$moral_identity_internal)
}
sd_fun <- function(x){
  sd(x$moral_identity_internal)
}

x <- df1_male
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1_male <- left_join(df1_male
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, means_fun))
                          ,names(unlist(lapply(x, means_fun))))
                        ,c("means","country_name"))
                      , by = "country_name")
df1_male <- left_join(df1_male
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, sd_fun))
                          ,names(unlist(lapply(x, sd_fun))))
                        ,c("sds","country_name"))
                      , by = "country_name")

x <- df1_female
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1_female <- left_join(df1_female
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, means_fun))
                          ,names(unlist(lapply(x, means_fun))))
                        ,c("means","country_name"))
                      , by = "country_name")
df1_female <- left_join(df1_female
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, sd_fun))
                          ,names(unlist(lapply(x, sd_fun))))
                        ,c("sds","country_name"))
                      , by = "country_name")

df2 <- rbind.data.frame(df1_male,df1_female)

df2$sex3 <- dplyr::recode(df2$sex3
                           , "male" = "Male"
                           , "female" = "Female")

g1 <- ggplot(df2,aes(x=sex3,y=moral_identity_internal))+
  #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=means - sds, ymax = means + sds), width=.06,
                position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=1)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl,
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Internalization")+
  facet_wrap(~df2$country_name3, ncol = 9 )+
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)

```

```{r, InternalizationGender,fig.cap="Gender differences in Internalization for each country",include=TRUE}
#suppressWarnings(print(g1))

```

<style>
#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
#scaled-frame { width: 250%; height: 900px; border: 1px; }
#scaled-frame {
    zoom: 0.50;
    -moz-transform: scale(0.50);
    -moz-transform-origin: 0 0;
    -o-transform: scale(0.50);
    -o-transform-origin: 0 0;
    -webkit-transform: scale(0.50);
    -webkit-transform-origin: 0 0;
}

@media screen and (-webkit-min-device-pixel-ratio:0) {
 #scaled-frame  { zoom: 1;  }
}
</style>

<div id="wrapper"><iframe id="scaled-frame" src="plots/internalization.png"></iframe></div>

## Symbolization

```{r}

ps <- function(y){
  y <- round(y, digits = 3)
  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y, quote = FALSE)),"*"))
  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y)))}

#### ensure correct data is loaded ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

#### remove any missing data #### 
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
table(x$country_name,x$sex3)
x$country_name

#### group by country ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

#### identify countries with small samples
male_length <- function(x){sum(x$sex3=='male')}
males <- lapply(x, male_length)
female_length <- function(x){sum(x$sex3=='female')}
females <- lapply(x, female_length)
names(females)

#### generate a vector containing all countries with less than 10 observations for either males or females ####
exclusions <- c(names(males[males<2]),
  names(females[females<2]))

#### re-load ungrouped data ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]

#### Filter out any countries to be excluded ####
x <- subset(x, !(country_name %in% exclusions))

#### group by country for analysis ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

ttest_fun <- function(x){
  t.test(moral_identity_symbolic ~ sex3, data = x)
}
all_t_tests <- lapply(x, ttest_fun)

means_fun <- function(x){
  mean(x$moral_identity_symbolic)
}
lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_symbolic)
}
lapply(x, sd_fun)

cohens_d_fun <- function(x){
  cohen.d(x$moral_identity_symbolic, x$sex3)
}
all_ds <- lapply(x, cohens_d_fun)
show_d_fun <- function(x){
  x$cohen.d[2]
}
ds_for_table <- lapply(all_ds, show_d_fun)

all_t_stats <- function(t){
  t$statistic
}
ts_for_table <- lapply(all_t_tests, all_t_stats)

all_t_df <- function(t){
  t$parameter
}
df_for_table <- lapply(all_t_tests, all_t_df)

all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)
raw_ps_for_table <- (lapply(all_t_tests, all_t_ps))

total_sig <- sum(unlist(lapply(all_t_tests, all_t_ps))<.05)

#### means for Males ####
# re-load ungrouped data #
x <- df[which(df$sex3=="male"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
male_means <- lapply(x, means_fun)
male_sds <- lapply(x, sd_fun)

#### means for Females
# re-load ungrouped data #
x <- df[which(df$sex3=="female"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
female_means <- lapply(x, means_fun)
female_sds <- lapply(x, sd_fun)

```

### Symbolization Ns

```{r}
#### Total Ns
x <- df[which(df$sex3=="male"
              |df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
total_Ns <- lapply(x, N_fun)

#### Ns for Males 
# re-load ungrouped data #
x <- df[which(df$sex3=="male"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
male_Ns <- lapply(x, N_fun)

#### Ns for Females
# re-load ungrouped data #
x <- df[which(df$sex3=="female"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)
# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
female_Ns <- lapply(x, N_fun)

test <- 
  cbind.data.frame(do.call(rbind, total_Ns)
                 ,do.call(rbind, female_Ns)
                 ,do.call(rbind, male_Ns))

test <- `colnames<-`(test, c("Total N","n Female","N male"))

loop_exclusions_fun <- function(x){
  if(rownames(test)[x] %in% exclusions) print(paste0(rownames(test)[x],"*"),quote = FALSE)
  else print(rownames(test)[x])
  }

rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_exclusions_fun))
test
#test <-
test[order(rownames(test) ),]

```

```{r include=TRUE}

apa_table(
  test
  , align = c("c", "c", "c")
  , caption = "Total samples for each country for Symbolization analysis"
  , note = "* = sample too small to be included in analysis below")

```

### Symbolization Table

```{r}

test <- 
  cbind.data.frame(
     round(do.call(rbind, female_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, male_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, ts_for_table),digits=2)
    ,round(do.call(rbind, df_for_table),digits=2)
    ,round(do.call(rbind, ds_for_table),digits=2)
    ,do.call(rbind, ps_for_table)
    )

test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","d","p"))
test

x <- df[which(df$sex3=="male"
              |df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
total_Ns <- lapply(x, N_fun)

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
            P_R$moral_identity_symbolic[which(P_R$sex3=="male")]
            ,"-"
            ,P_R$moral_identity_symbolic[which(P_R$sex3=="female")]
            ,"-"
            ,"-"
            ,"-"
            ,"-"
            ,"-"))),
      c("mean F","SD F","mean M", "SD M", "t","df","d","p"))
    ,c("Puerto Rico"))

test <- rbind(test[1:49,],P_R,test[50:length(test$`mean F`),])
test <- test[order(rownames(test) ),]

```

```{r include=TRUE}

apa_table(
  test
  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
  , caption = "Gender differences in Symbolization for each Country"
  , note = "* = sig. at p < .05; ** = sig. at p < .001")

```

### Symbolization Plot

(<a href="https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/symbolization.png" target="_blank">open in new window</a>)

```{r}

test <- 
  cbind.data.frame(
     round(do.call(rbind, female_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, male_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, ts_for_table),digits=2)
    ,round(do.call(rbind, df_for_table),digits=2)
    ,do.call(rbind, raw_ps_for_table)
    ,round(do.call(rbind, ds_for_table),digits=2)
    )

test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
test

sig_countries <- rownames(test[which(test$p<.05),])
```

```{r symbolizationPlot}

x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

#### identify countries with small samples
male_length <- function(x){sum(x$sex3=='male')}
males <- lapply(x, male_length)
female_length <- function(x){sum(x$sex3=='female')}
females <- lapply(x, female_length)
names(females)

#### generate a vector containing all countries with less than 10 observations for either males or females ####
exclusions <- c(names(males[males<2]),
  names(females[females<2]))

#### re-load ungrouped data ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]

#### Filter out any countries to be excluded ####
x <- subset(x, !(country_name %in% exclusions))

df1 <- x

df1_male <- df1[which(df1$sex3=="male"),]
df1_female <- df1[which(df1$sex3=="female"),]

internal_mean_sd <- function(x){
  z <- x
  z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
  z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
  z
}

# df1 <- rbind.data.frame(
#   internal_mean_sd(df1_female),
#   internal_mean_sd(df1_male)
# )

loop_sigs_fun3 <- function(y){
  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
  else print(df1$country_name[y])
}

df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))

N_fun <- function(x){
  length(x$sex3)
}
length(df1$sex3)
x <- df1
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1 <- left_join(df1
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, N_fun))
                          ,names(unlist(lapply(x, N_fun))))
                        ,c("N","country_name"))
                      , by = "country_name")

df1$country_name3 <- print(paste0(df1$country_name2, " (N = ", df1$N,")"))

df1_male <- df1[which(df1$sex3=="male"),]
df1_female <- df1[which(df1$sex3=="female"),]

# x <- df1
# 
# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

means_fun <- function(x){
  mean(x$moral_identity_symbolic)
}

sd_fun <- function(x){
  sd(x$moral_identity_symbolic)
}

x <- df1_male
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1_male <- left_join(df1_male
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, means_fun))
                          ,names(unlist(lapply(x, means_fun))))
                        ,c("means","country_name"))
                      , by = "country_name")
df1_male <- left_join(df1_male
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, sd_fun))
                          ,names(unlist(lapply(x, sd_fun))))
                        ,c("sds","country_name"))
                      , by = "country_name")

x <- df1_female
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1_female <- left_join(df1_female
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, means_fun))
                          ,names(unlist(lapply(x, means_fun))))
                        ,c("means","country_name"))
                      , by = "country_name")
df1_female <- left_join(df1_female
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, sd_fun))
                          ,names(unlist(lapply(x, sd_fun))))
                        ,c("sds","country_name"))
                      , by = "country_name")

df2 <- rbind.data.frame(df1_male,df1_female)

df2$sex3 <- dplyr::recode(df2$sex3
                           , "male" = "Male"
                           , "female" = "Female")

g1 <- ggplot(df2,aes(x=sex3,y=moral_identity_symbolic))+
  #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=means - sds, ymax = means + sds), width=.06,
                position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=1)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl,
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Internalization")+
  facet_wrap(~df2$country_name3, ncol = 9 )+
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
#g2
```

```{r, SymbolizationGender,fig.cap="Gender differences in Symbolization for each country",include=TRUE}
#suppressWarnings(print(g1))

```

<style>
#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
#scaled-frame { width: 250%; height: 900px; border: 1px; }
#scaled-frame {
    zoom: 0.50;
    -moz-transform: scale(0.50);
    -moz-transform-origin: 0 0;
    -o-transform: scale(0.50);
    -o-transform-origin: 0 0;
    -webkit-transform: scale(0.50);
    -webkit-transform-origin: 0 0;
}

@media screen and (-webkit-min-device-pixel-ratio:0) {
 #scaled-frame  { zoom: 1;  }
}
</style>

<div id="wrapper"><iframe id="scaled-frame" src="plots/internalization.png"></iframe></div>

### 2023-02-06 supp_H2.Rmd
tidied up all plots, added * and N

---
title: "H2 Supplement"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }

</style>

```{r setuph2supp, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
```

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)
```

```{r}

#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

df$sex3 <- as.factor(df$sex1)
df$sex3 <- dplyr::recode(df$sex3,
               "1"="male"
              ,"2"="female"
              ,"3"="other")

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
```

```{r}
rm(list = ls())
#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

df$sex3 <- as.factor(df$sex1)
df$sex3 <- dplyr::recode(df$sex3,
               "1"="male"
              ,"2"="female"
              ,"3"="other")

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
```

## Age & Internalization

```{r}

ps <- function(y){
  y <- round(y, digits = 3)
  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y, quote = FALSE)),"*"))
  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y)))}

x <- df
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
#### group by country for analysis ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

N_fun <- function(x){
  length(x$sex3)
}
total_Ns <- lapply(x, N_fun)

exclusions <- names(total_Ns)[which(total_Ns<3)]
x <- df
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

cor_fun <- function(x){
  cor.test(x$moral_identity_symbolic,x$age)
}
all_cor_tests <- lapply(x, cor_fun)

all_cor_rs <- function(c){
  c$estimate
}
rs_for_table <- lapply(all_cor_tests, all_cor_rs)
all_cor_ps <- function(c){
  c$estimate
}
ps_for_table <- lapply(all_cor_tests, all_cor_ps)
ps_output_for_table <- lapply((lapply(all_cor_tests, all_cor_ps)), ps)
Ns_for_table <- lapply(x, N_fun)

means_INT_fun <- function(x){
  mean(x$moral_identity_internal)
}
mean_int_for_table <- lapply(x, means_INT_fun)
sd_INT_fun <- function(x){
  sd(x$moral_identity_internal)
}
sd_int_for_table <- lapply(x, sd_INT_fun)

means_age_fun <- function(x){
  mean(x$age)
}
mean_age_for_table <- lapply(x, means_age_fun)
sd_age_fun <- function(x){
  sd(x$age)
}
sd_age_for_table <- lapply(x, sd_age_fun)

```

```{r}

test <- 
  cbind.data.frame(
     round(do.call(rbind,mean_age_for_table),digits = 2)
    ,round(do.call(rbind,sd_age_for_table),digits = 2)
    ,round(do.call(rbind,mean_int_for_table),digits = 2)
    ,round(do.call(rbind,sd_int_for_table),digits = 2)
    ,round(do.call(rbind, Ns_for_table))
    ,round(do.call(rbind, rs_for_table),digits=3)
    ,do.call(rbind, ps_output_for_table)
    )

test <- `colnames<-`(test, c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
test

sum(unlist(ps_for_table)<.05)

test1 <- subset(test, p < .05)
test1

total_sig <- length(test1$`mean age`)

neg <- sum(test1$r <0 )
pos <- sum(test1$r>0)

x <- df
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
            round(mean(P_R$age),digits=2)
            ,round(sd(P_R$age),digits=2)
            ,round(mean(P_R$moral_identity_internal),digits=2)
            ,round(sd(P_R$moral_identity_internal),digits=2)
            ,length(P_R$moral_identity_internal)
            ,"-"
            ,"-"))),
      c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
    ,c("Puerto Rico"))

test <- rbind(test[1:49,],P_R,test[50:length(test$p),])
test <- test[order(rownames(test) ),]

```

```{r include=TRUE}

apa_table(
  test
  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
  , caption = "Correlation between Age and Internalization for each Country"
  , note = "* = sig. at p < .05; ** = sig. at p < .001")

```

```{r}

test <- 
  cbind.data.frame(
     round(do.call(rbind,mean_age_for_table),digits = 2)
    ,round(do.call(rbind,sd_age_for_table),digits = 2)
    ,round(do.call(rbind,mean_int_for_table),digits = 2)
    ,round(do.call(rbind,sd_int_for_table),digits = 2)
    ,round(do.call(rbind, Ns_for_table))
    ,round(do.call(rbind, rs_for_table),digits=3)
    ,do.call(rbind, ps_for_table)
    )

test <- `colnames<-`(test, c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
test

sig_countries <- rownames(test[which(test$p<.05),])

# loop_sigs_fun <- function(x){
#   if(rownames(test)[x] %in% sig_countries) print(paste0(rownames(test)[x],"*"),quote = FALSE)
#   else print(rownames(test)[x])
# }
# 
# rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_sigs_fun))
# 
# loop_sigs_fun2 <- function(x,y){
#   if(x$country_name[y] %in% sig_countries) print(paste0(x$country_name[y],"*"),quote = FALSE)
#   else print(x$country_name[y])
# }

```

```{r}

df1 <- subset(df, !(country_name %in% exclusions))

loop_sigs_fun3 <- function(y){
  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
  else print(df1$country_name[y])
}

df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))

N_fun <- function(x){
  length(x$sex3)
}
length(df1$sex3)
x <- df1
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1 <- left_join(df1
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, N_fun))
                          ,names(unlist(lapply(x, N_fun))))
                        ,c("N","country_name"))
                      , by = "country_name")

df1$country_name3 <- print(paste0(df1$country_name2, " (N = ", df1$N,")"))

g1 <- ggplot(df1, aes(age, moral_identity_internal))+
  geom_jitter(size=.05, color='darkgrey') + 
  ylim(0,10) +
  geom_smooth(method=lm, size = .5,color='black') +
  labs(y = "Internalization",
       x = "Age"
  )+ 
  theme_apa()+
  theme_bw()+
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")+
  facet_wrap(~df1$country_name3, ncol = 9 )

ggsave("plots/age_internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)

```

(<a href="https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/age_internalization.png" target="_blank">open in new window</a>)

<style>
#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
#scaled-frame { width: 250%; height: 900px; border: 1px; }
#scaled-frame {
    zoom: 0.50;
    -moz-transform: scale(0.50);
    -moz-transform-origin: 0 0;
    -o-transform: scale(0.50);
    -o-transform-origin: 0 0;
    -webkit-transform: scale(0.50);
    -webkit-transform-origin: 0 0;
}

@media screen and (-webkit-min-device-pixel-ratio:0) {
 #scaled-frame  { zoom: 1;  }
}
</style>

<div id="wrapper"><iframe id="scaled-frame" src="plots/age_internalization.png"></iframe></div>

## Age & Symbolization

```{r}

ps <- function(y){
  y <- round(y, digits = 3)
  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y, quote = FALSE)),"*"))
  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y)))}

x <- df
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
#### group by country for analysis ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

N_fun <- function(x){
  length(x$sex3)
}
total_Ns <- lapply(x, N_fun)

exclusions <- names(total_Ns)[which(total_Ns<3)]
x <- df
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

cor_fun <- function(x){
  cor.test(x$moral_identity_symbolic,x$age)
}
all_cor_tests <- lapply(x, cor_fun)

all_cor_rs <- function(c){
  c$estimate
}
rs_for_table <- lapply(all_cor_tests, all_cor_rs)
all_cor_ps <- function(c){
  c$estimate
}
ps_for_table <- lapply(all_cor_tests, all_cor_ps)
ps_output_for_table <- lapply((lapply(all_cor_tests, all_cor_ps)), ps)
Ns_for_table <- lapply(x, N_fun)

means_INT_fun <- function(x){
  mean(x$moral_identity_symbolic)
}
mean_int_for_table <- lapply(x, means_INT_fun)
sd_INT_fun <- function(x){
  sd(x$moral_identity_symbolic)
}
sd_int_for_table <- lapply(x, sd_INT_fun)

means_age_fun <- function(x){
  mean(x$age)
}
mean_age_for_table <- lapply(x, means_age_fun)
sd_age_fun <- function(x){
  sd(x$age)
}
sd_age_for_table <- lapply(x, sd_age_fun)

```

```{r}

test <- 
  cbind.data.frame(
     round(do.call(rbind,mean_age_for_table),digits = 2)
    ,round(do.call(rbind,sd_age_for_table),digits = 2)
    ,round(do.call(rbind,mean_int_for_table),digits = 2)
    ,round(do.call(rbind,sd_int_for_table),digits = 2)
    ,round(do.call(rbind, Ns_for_table))
    ,round(do.call(rbind, rs_for_table),digits=3)
    ,do.call(rbind, ps_output_for_table)
    )

test <- `colnames<-`(test, c("mean age","SD age","mean symbolization", "SD symbolization","N", "r","p"))
test

sum(unlist(ps_for_table)<.05)

test1 <- subset(test, p < .05)
test1

total_sig <- length(test1$`mean age`)

neg <- sum(test1$r <0 )
pos <- sum(test1$r>0)

x <- df
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
             round(mean(P_R$age),digits=2)
            ,round(sd(P_R$age),digits=2)
            ,round(mean(P_R$moral_identity_symbolic),digits=2)
            ,round(sd(P_R$moral_identity_symbolic),digits=2)
            ,length(P_R$moral_identity_symbolic)
            ,"-"
            ,"-"))),
      c("mean age","SD age","mean symbolization", "SD symbolization","N", "r","p"))
    ,c("Puerto Rico"))

test <- rbind(test[1:49,],P_R,test[50:length(test$p),])
test <- test[order(rownames(test) ),]

```

```{r include=TRUE}

apa_table(
  test
  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
  , caption = "Correlation between Age and Symbolization for each Country"
  , note = "* = sig. at p < .05; ** = sig. at p < .001")

```

```{r}

test <- 
  cbind.data.frame(
     round(do.call(rbind,mean_age_for_table),digits = 2)
    ,round(do.call(rbind,sd_age_for_table),digits = 2)
    ,round(do.call(rbind,mean_int_for_table),digits = 2)
    ,round(do.call(rbind,sd_int_for_table),digits = 2)
    ,round(do.call(rbind, Ns_for_table))
    ,round(do.call(rbind, rs_for_table),digits=3)
    ,do.call(rbind, ps_for_table)
    )

test <- `colnames<-`(test, c("mean age","SD age","mean symbolization", "SD internalization","N", "r","p"))
test

sig_countries <- rownames(test[which(test$p<.05),])

# loop_sigs_fun <- function(x){
#   if(rownames(test)[x] %in% sig_countries) print(paste0(rownames(test)[x],"*"),quote = FALSE)
#   else print(rownames(test)[x])
# }
# 
# rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_sigs_fun))
# 
# loop_sigs_fun2 <- function(x,y){
#   if(x$country_name[y] %in% sig_countries) print(paste0(x$country_name[y],"*"),quote = FALSE)
#   else print(x$country_name[y])
# }

```

```{r}

df1 <- subset(df, !(country_name %in% exclusions))

loop_sigs_fun3 <- function(y){
  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
  else print(df1$country_name[y])
}

df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))

N_fun <- function(x){
  length(x$sex3)
}
length(df1$sex3)
x <- df1
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1 <- left_join(df1
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, N_fun))
                          ,names(unlist(lapply(x, N_fun))))
                        ,c("N","country_name"))
                      , by = "country_name")

df1$country_name3 <- print(paste0(df1$country_name2, " (N = ", df1$N,")"))

g1 <- ggplot(df1, aes(age, moral_identity_symbolic))+
  geom_jitter(size=.05, color='darkgrey') + 
  ylim(0,10) +
  geom_smooth(method=lm, size = .5,color='black') +
  labs(y = "Symbolization",
       x = "Age"
  )+ 
  theme_apa()+
  theme_bw()+
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")+
  facet_wrap(~df1$country_name3, ncol = 9 )

ggsave("plots/age_symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)

```

(<a href="https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/age_symbolization.png" target="_blank">open in new window</a>)

<style>
#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
#scaled-frame { width: 250%; height: 900px; border: 1px; }
#scaled-frame {
    zoom: 0.50;
    -moz-transform: scale(0.50);
    -moz-transform-origin: 0 0;
    -o-transform: scale(0.50);
    -o-transform-origin: 0 0;
    -webkit-transform: scale(0.50);
    -webkit-transform-origin: 0 0;
}

@media screen and (-webkit-min-device-pixel-ratio:0) {
 #scaled-frame  { zoom: 1;  }
}
</style>

<div id="wrapper"><iframe id="scaled-frame" src="plots/age_symbolization.png"></iframe></div>

### 2023-02-06 supp_H2.Rmd
made plots smaller for  viewing (rather than download)

@@
 
-ggsave("plots/age_internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
+ggsave("plots/age_internalization.png", g1, width = 30, height = 20, units = "in", dpi = 300)
 
@@
 
-ggsave("plots/age_symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
+ggsave("plots/age_symbolization.png", g1, width = 30, height = 20, units = "in", dpi = 300)
 

### 2023-02-06 H1.Rmd
created links to supplementary within the main results

@@
 We found significant gender differences in internalization across `r total_sig` countries.
-Of these, `r pos` were in the predicted direction, while in `r neg` countries (`r c1` and `r c2`), males showed higher internalization than females (see Supplementary Materials Table S_X).
+Of these, `r pos` were in the predicted direction, while in `r neg` countries (`r c1` and `r c2`), males showed higher internalization than females (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Internalization_Table)).
 
@@
 We found significant gender differences in symbolization across `r total_sig` countries.
-Of these, `r pos` were in the predicted direction, while in `r neg` countries (`r c1` and `r c2`), males showed higher symbolization than females (see Supplementary Materials Table S_X).
+Of these, `r pos` were in the predicted direction, while in `r neg` countries (`r c1` and `r c2`), males showed higher symbolization than females (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Symbolization_Table)).
 

### 2023-02-06 H2.Rmd
created links to supplementary within the main results

@@
 all_cor_ps <- function(c){
-  c$estimate
+  c$p.value
 }
@@
 There was a significant correlation between age and internalization in `r total_sig` countries.
-Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials Table S_X).
+Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Internalization)).
 
@@
 There was a significant correlation between age and internalization in `r total_sig` countries.
-Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials Table S_X).
+Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).

### 2023-02-06 supp_H3.Rmd
added cleaned data (nobots)

--- 2023-02-06 supp_H2.Rmd
@@
 
-```{r setuph2supp, include=FALSE}
+```{r setuph3supp, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE)
@@
 ```
-
-## Age & Internalization
-
-```{r}
-
-ps <- function(y){
-  y <- round(y, digits = 3)
-  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
-  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
-        y, quote = FALSE)),"*"))
-  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
-        y)))}
-
-x <- df
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-#### group by country for analysis ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-N_fun <- function(x){
-  length(x$sex3)
-}
-total_Ns <- lapply(x, N_fun)
-
-exclusions <- names(total_Ns)[which(total_Ns<3)]
-x <- df
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-cor_fun <- function(x){
-  cor.test(x$moral_identity_symbolic,x$age)
-}
-all_cor_tests <- lapply(x, cor_fun)
-
-all_cor_rs <- function(c){
-  c$estimate
-}
-rs_for_table <- lapply(all_cor_tests, all_cor_rs)
-all_cor_ps <- function(c){
-  c$p.value
-}
-ps_for_table <- lapply(all_cor_tests, all_cor_ps)
-ps_output_for_table <- lapply((lapply(all_cor_tests, all_cor_ps)), ps)
-Ns_for_table <- lapply(x, N_fun)
-
-means_INT_fun <- function(x){
-  mean(x$moral_identity_internal)
-}
-mean_int_for_table <- lapply(x, means_INT_fun)
-sd_INT_fun <- function(x){
-  sd(x$moral_identity_internal)
-}
-sd_int_for_table <- lapply(x, sd_INT_fun)
-
-means_age_fun <- function(x){
-  mean(x$age)
-}
-mean_age_for_table <- lapply(x, means_age_fun)
-sd_age_fun <- function(x){
-  sd(x$age)
-}
-sd_age_for_table <- lapply(x, sd_age_fun)
-
-```
-
-```{r}
-
-test <- 
-  cbind.data.frame(
-     round(do.call(rbind,mean_age_for_table),digits = 2)
-    ,round(do.call(rbind,sd_age_for_table),digits = 2)
-    ,round(do.call(rbind,mean_int_for_table),digits = 2)
-    ,round(do.call(rbind,sd_int_for_table),digits = 2)
-    ,round(do.call(rbind, Ns_for_table))
-    ,round(do.call(rbind, rs_for_table),digits=3)
-    ,do.call(rbind, ps_output_for_table)
-    )
-
-test <- `colnames<-`(test, c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
-test
-
-sum(unlist(ps_for_table)<.05)
-
-test1 <- subset(test, p < .05)
-test1
-
-total_sig <- length(test1$`mean age`)
-
-neg <- sum(test1$r <0 )
-pos <- sum(test1$r>0)
-
-x <- df
-x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-P_R <- x$`Puerto Rico`
-P_R <- 
-  `rownames<-`(
-    `colnames<-`(
-      as.data.frame(
-        rbind(
-          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
-          # ,
-          c(
-            round(mean(P_R$age),digits=2)
-            ,round(sd(P_R$age),digits=2)
-            ,round(mean(P_R$moral_identity_internal),digits=2)
-            ,round(sd(P_R$moral_identity_internal),digits=2)
-            ,length(P_R$moral_identity_internal)
-            ,"-"
-            ,"-"))),
-      c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
-    ,c("Puerto Rico"))
-
-test <- rbind(test[1:49,],P_R,test[50:length(test$p),])
-test <- test[order(rownames(test) ),]
-
-```
-
-```{r include=TRUE}
-
-apa_table(
-  test
-  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
-  , caption = "Correlation between Age and Internalization for each Country"
-  , note = "* = sig. at p < .05; ** = sig. at p < .001")
-
-```
-
-```{r}
-
-test <- 
-  cbind.data.frame(
-     round(do.call(rbind,mean_age_for_table),digits = 2)
-    ,round(do.call(rbind,sd_age_for_table),digits = 2)
-    ,round(do.call(rbind,mean_int_for_table),digits = 2)
-    ,round(do.call(rbind,sd_int_for_table),digits = 2)
-    ,round(do.call(rbind, Ns_for_table))
-    ,round(do.call(rbind, rs_for_table),digits=3)
-    ,do.call(rbind, ps_for_table)
-    )
-
-test <- `colnames<-`(test, c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
-test
-
-sig_countries <- rownames(test[which(test$p<.05),])
-
-# loop_sigs_fun <- function(x){
-#   if(rownames(test)[x] %in% sig_countries) print(paste0(rownames(test)[x],"*"),quote = FALSE)
-#   else print(rownames(test)[x])
-# }
-# 
-# rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_sigs_fun))
-# 
-# loop_sigs_fun2 <- function(x,y){
-#   if(x$country_name[y] %in% sig_countries) print(paste0(x$country_name[y],"*"),quote = FALSE)
-#   else print(x$country_name[y])
-# }
-
-```
-
-```{r}
-
-df1 <- subset(df, !(country_name %in% exclusions))
-
-loop_sigs_fun3 <- function(y){
-  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
-  else print(df1$country_name[y])
-}
-
-df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))
-
-N_fun <- function(x){
-  length(x$sex3)
-}
-length(df1$sex3)
-x <- df1
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-df1 <- left_join(df1
-                      ,  
-                      `colnames<-`(
-                        cbind.data.frame(
-                          unlist(lapply(x, N_fun))
-                          ,names(unlist(lapply(x, N_fun))))
-                        ,c("N","country_name"))
-                      , by = "country_name")
-
-df1$country_name3 <- print(paste0(df1$country_name2, " (N = ", df1$N,")"))
-
-g1 <- ggplot(df1, aes(age, moral_identity_internal))+
-  geom_jitter(size=.05, color='darkgrey') + 
-  ylim(0,10) +
-  geom_smooth(method=lm, size = .5,color='black') +
-  labs(y = "Internalization",
-       x = "Age"
-  )+ 
-  theme_apa()+
-  theme_bw()+
-  theme(panel.border = element_blank(),
-        axis.line = element_line(size = .2),
-        strip.background  = element_blank(),
-        #panel.grid = element_blank(),
-        plot.title=element_text(#family="Times",
-          size=12
-        ),
-        #legend.position="right",
-        legend.text=element_text(#family="Times",
-          size=8
-        ),
-        legend.title=element_text(#family="Times",
-          size=10
-        ),
-        axis.text=element_text(#family="Times",
-          colour = "black",
-          size=8
-        ),
-        axis.ticks.x = element_blank(),
-        axis.title=element_text(#family="Times",
-          size=12
-        ),
-        strip.text=element_text(#family = "Times",
-          size = 12
-        ),
-        # strip.background = element_rect(fill = "white"),
-        legend.position="none")+
-  facet_wrap(~df1$country_name3, ncol = 9 )
-
-ggsave("plots/age_internalization.png", g1, width = 30, height = 20, units = "in", dpi = 300)
-
-```
-
-(<a href="https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/age_internalization.png" target="_blank">open in new window</a>)
-
-<style>
-#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
-#scaled-frame { width: 250%; height: 900px; border: 1px; }
-#scaled-frame {
-    zoom: 0.50;
-    -moz-transform: scale(0.50);
-    -moz-transform-origin: 0 0;
-    -o-transform: scale(0.50);
-    -o-transform-origin: 0 0;
-    -webkit-transform: scale(0.50);
-    -webkit-transform-origin: 0 0;
-}
-
-@media screen and (-webkit-min-device-pixel-ratio:0) {
- #scaled-frame  { zoom: 1;  }
-}
-</style>
-
-<div id="wrapper"><iframe id="scaled-frame" src="plots/age_internalization.png"></iframe></div>
-
-## Age & Symbolization
-
-```{r}
-
-ps <- function(y){
-  y <- round(y, digits = 3)
-  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
-  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
-        y, quote = FALSE)),"*"))
-  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
-        y)))}
-
-x <- df
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-#### group by country for analysis ####
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-N_fun <- function(x){
-  length(x$sex3)
-}
-total_Ns <- lapply(x, N_fun)
-
-exclusions <- names(total_Ns)[which(total_Ns<3)]
-x <- df
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-x <- subset(x, !(country_name %in% exclusions))
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-cor_fun <- function(x){
-  cor.test(x$moral_identity_symbolic,x$age)
-}
-all_cor_tests <- lapply(x, cor_fun)
-
-all_cor_rs <- function(c){
-  c$estimate
-}
-rs_for_table <- lapply(all_cor_tests, all_cor_rs)
-all_cor_ps <- function(c){
-  c$p.value
-}
-ps_for_table <- lapply(all_cor_tests, all_cor_ps)
-ps_output_for_table <- lapply((lapply(all_cor_tests, all_cor_ps)), ps)
-Ns_for_table <- lapply(x, N_fun)
-
-means_INT_fun <- function(x){
-  mean(x$moral_identity_symbolic)
-}
-mean_int_for_table <- lapply(x, means_INT_fun)
-sd_INT_fun <- function(x){
-  sd(x$moral_identity_symbolic)
-}
-sd_int_for_table <- lapply(x, sd_INT_fun)
-
-means_age_fun <- function(x){
-  mean(x$age)
-}
-mean_age_for_table <- lapply(x, means_age_fun)
-sd_age_fun <- function(x){
-  sd(x$age)
-}
-sd_age_for_table <- lapply(x, sd_age_fun)
-
-```
-
-```{r}
-
-test <- 
-  cbind.data.frame(
-     round(do.call(rbind,mean_age_for_table),digits = 2)
-    ,round(do.call(rbind,sd_age_for_table),digits = 2)
-    ,round(do.call(rbind,mean_int_for_table),digits = 2)
-    ,round(do.call(rbind,sd_int_for_table),digits = 2)
-    ,round(do.call(rbind, Ns_for_table))
-    ,round(do.call(rbind, rs_for_table),digits=3)
-    ,do.call(rbind, ps_output_for_table)
-    )
-
-test <- `colnames<-`(test, c("mean age","SD age","mean symbolization", "SD symbolization","N", "r","p"))
-test
-
-sum(unlist(ps_for_table)<.05)
-
-test1 <- subset(test, p < .05)
-test1
-
-total_sig <- length(test1$`mean age`)
-
-neg <- sum(test1$r <0 )
-pos <- sum(test1$r>0)
-
-x <- df
-x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
-x <- x[which(is.na(x$age)==FALSE),]
-
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-
-P_R <- x$`Puerto Rico`
-P_R <- 
-  `rownames<-`(
-    `colnames<-`(
-      as.data.frame(
-        rbind(
-          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
-          # ,
-          c(
-             round(mean(P_R$age),digits=2)
-            ,round(sd(P_R$age),digits=2)
-            ,round(mean(P_R$moral_identity_symbolic),digits=2)
-            ,round(sd(P_R$moral_identity_symbolic),digits=2)
-            ,length(P_R$moral_identity_symbolic)
-            ,"-"
-            ,"-"))),
-      c("mean age","SD age","mean symbolization", "SD symbolization","N", "r","p"))
-    ,c("Puerto Rico"))
-
-test <- rbind(test[1:49,],P_R,test[50:length(test$p),])
-test <- test[order(rownames(test) ),]
-
-```
-
-```{r include=TRUE}
-
-apa_table(
-  test
-  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
-  , caption = "Correlation between Age and Symbolization for each Country"
-  , note = "* = sig. at p < .05; ** = sig. at p < .001")
-
-```
-
-```{r}
-
-test <- 
-  cbind.data.frame(
-     round(do.call(rbind,mean_age_for_table),digits = 2)
-    ,round(do.call(rbind,sd_age_for_table),digits = 2)
-    ,round(do.call(rbind,mean_int_for_table),digits = 2)
-    ,round(do.call(rbind,sd_int_for_table),digits = 2)
-    ,round(do.call(rbind, Ns_for_table))
-    ,round(do.call(rbind, rs_for_table),digits=3)
-    ,do.call(rbind, ps_for_table)
-    )
-
-test <- `colnames<-`(test, c("mean age","SD age","mean symbolization", "SD internalization","N", "r","p"))
-test
-
-sig_countries <- rownames(test[which(test$p<.05),])
-
-# loop_sigs_fun <- function(x){
-#   if(rownames(test)[x] %in% sig_countries) print(paste0(rownames(test)[x],"*"),quote = FALSE)
-#   else print(rownames(test)[x])
-# }
-# 
-# rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_sigs_fun))
-# 
-# loop_sigs_fun2 <- function(x,y){
-#   if(x$country_name[y] %in% sig_countries) print(paste0(x$country_name[y],"*"),quote = FALSE)
-#   else print(x$country_name[y])
-# }
-
-```
-
-```{r}
-
-df1 <- subset(df, !(country_name %in% exclusions))
-
-loop_sigs_fun3 <- function(y){
-  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
-  else print(df1$country_name[y])
-}
-
-df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))
-
-N_fun <- function(x){
-  length(x$sex3)
-}
-length(df1$sex3)
-x <- df1
-x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
-df1 <- left_join(df1
-                      ,  
-                      `colnames<-`(
-                        cbind.data.frame(
-                          unlist(lapply(x, N_fun))
-                          ,names(unlist(lapply(x, N_fun))))
-                        ,c("N","country_name"))
-                      , by = "country_name")
-
-df1$country_name3 <- print(paste0(df1$country_name2, " (N = ", df1$N,")"))
-
-g1 <- ggplot(df1, aes(age, moral_identity_symbolic))+
-  geom_jitter(size=.05, color='darkgrey') + 
-  ylim(0,10) +
-  geom_smooth(method=lm, size = .5,color='black') +
-  labs(y = "Symbolization",
-       x = "Age"
-  )+ 
-  theme_apa()+
-  theme_bw()+
-  theme(panel.border = element_blank(),
-        axis.line = element_line(size = .2),
-        strip.background  = element_blank(),
-        #panel.grid = element_blank(),
-        plot.title=element_text(#family="Times",
-          size=12
-        ),
-        #legend.position="right",
-        legend.text=element_text(#family="Times",
-          size=8
-        ),
-        legend.title=element_text(#family="Times",
-          size=10
-        ),
-        axis.text=element_text(#family="Times",
-          colour = "black",
-          size=8
-        ),
-        axis.ticks.x = element_blank(),
-        axis.title=element_text(#family="Times",
-          size=12
-        ),
-        strip.text=element_text(#family = "Times",
-          size = 12
-        ),
-        # strip.background = element_rect(fill = "white"),
-        legend.position="none")+
-  facet_wrap(~df1$country_name3, ncol = 9 )
-
-ggsave("plots/age_symbolization.png", g1, width = 30, height = 20, units = "in", dpi = 300)
-
-```
-
-(<a href="https://raw.githubusercontent.com/cillianmiltown/moral_ID_gender/main/plots/age_symbolization.png" target="_blank">open in new window</a>)
-
-<style>
-#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
-#scaled-frame { width: 250%; height: 900px; border: 1px; }
-#scaled-frame {
-    zoom: 0.50;
-    -moz-transform: scale(0.50);
-    -moz-transform-origin: 0 0;
-    -o-transform: scale(0.50);
-    -o-transform-origin: 0 0;
-    -webkit-transform: scale(0.50);
-    -webkit-transform-origin: 0 0;
-}
-
-@media screen and (-webkit-min-device-pixel-ratio:0) {
- #scaled-frame  { zoom: 1;  }
-}
-</style>
-
-<div id="wrapper"><iframe id="scaled-frame" src="plots/age_symbolization.png"></iframe></div>

### 2023-02-06 cleaning.R

@@ -1,0 +1,17 @@
+rm(list = ls())
+
+load("data/data_with_means_raw.RData")
+df_nobots <- read.csv("../data/ICSMP_cleaned_data_nobots.csv")
+
+head(df)
+
+no_bots <- df_nobots$participantID
+
+
+x <- df
+x <- subset(x, (participantID %in% no_bots))
+
+df <- x
+
+write.csv(df, "data/data_with_means.csv", row.names = FALSE)
+save(df, file = "data/data_with_means.RData")

### 2023-02-06 set_up_data_calculate_means.R

@@ -381,6 +381,9 @@ df3 <- merge(df,df1, by  = "ISO3")
 
 df <- df3
 
-write.csv(df, "data/data_with_means.csv", row.names = FALSE)
-save(df, file = "data/data_with_means.RData")
+# write.csv(df, "data/data_with_means.csv", row.names = FALSE)
+# save(df, file = "data/data_with_means.RData")
+
+write.csv(df, "data/data_with_means_raw.csv", row.names = FALSE)
+save(df, file = "data/data_with_means_raw.RData")
 

### 2023-02-06 H3.Rmd
added h3

@@
 
+fit0 <- lm(moral_identity_symbolic ~ 
+             mean(x$moral_identity_symbolic)
+                    # sex3
+                    # + age
+                    #  Power.Distance
+                    # + Individualism
+                    # + Masculinity
+                    # + Uncertainty.Avoidance
+                    # + Long.Term.Orientation
+                    # + Indulgence
+                    # + CTL_C
+                    # + CTL_DS
+                    # + CTL_DG
+                 , data = x
+            )
+
+summary(fit0)
+
 fit <- lm(moral_identity_symbolic ~
@@
 summary(fit)
-
+anova(fit)
 fit_results <- apa_print(fit)
@@
 ```
+
+Our third hypothesis predicted relationships between symbolization and specific cultural variables.
+The variables question are: power distance, individualism, masculinity, uncertainty avoidance, long term orientation, and indulgence, taken from Hofstede (2001), as well as three measures of cultural tightness (domain-specific, domain-general, and a combination index).
+These variables were inputted at the country level, and as such, we conducted a hierarchical linear regression model to investigate relationship with symbolization.
+Symbolization was our outcome measure and each cultural variable was included as a predictor in the model.

### 2023-02-07 H4.Rmd
added H4 (brief)

---
title: "H4: Cultural Differences in Internalization"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }

</style>

```{r setuph4, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
```

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)
```

```{r}
rm(list = ls())

#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

df$sex3 <- as.factor(df$sex1)
df$sex3 <- dplyr::recode(df$sex3,
               "1"="male"
              ,"2"="female"
              ,"3"="other")

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")

x <- df
```

```{r}

# h3a yes
# h3b n/a (competing)
# h3c yes
# h3d no (no relationship)
# h3e yes
# h3f yes
# h3g no, no, yes

x <- x[which(is.na(x$moral_identity_internal)==FALSE),]

fit <- lm(moral_identity_internal ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = x
            )

fit_results <- summary(fit)
fit_results$adj.r.squared
anova(fit)
apa_fit_results <- apa_print(fit)

cor.test(x$Power.Distance,x$moral_identity_internal)

apa_fit_results$full_result$modelfit$r2
fit$qr
apa_fit_results$table
results_for_table <- apa_fit_results$table

estimate_for_table <-
  `colnames<-`(
    cbind.data.frame(
      unlist(fit_results$coefficients[,1])
      ,names(unlist(fit_results$coefficients[,1]))
    ), c("estimate","rows"))$estimate

stderror_for_table <-
  `colnames<-`(
    cbind.data.frame(
      unlist(fit_results$coefficients[,2])
      ,names(unlist(fit_results$coefficients[,2]))
    ), c("stderror","rows"))$stderror

estimate_for_table
stderror_for_table

results_for_table$estimate <- estimate_for_table
results_for_table$StdError <- stderror_for_table

results_for_table <- results_for_table[c(1,2,7,3,4,5,6)]

results_for_table$estimate <- sprintf("%.3f", results_for_table$estimate)
results_for_table$StdError <- sprintf("%.3f", results_for_table$StdError)

# library(Hmisc)
# 
# var.labels = 
#   c(
#     term        = "Predictor" 
#     , "estimate"  = "$b$" 
#     , "StdError"  = "$S.E.$"
#     , conf.int  = "95\\% CI" 
#     , statistic = "$t$" 
#     , df        = "$\\mathit{df}$" 
#     , p.value   = "$p$" 
#     )
# 
# label(results_for_table) = as.list(var.labels[match(names(results_for_table), names(var.labels))])

results_for_table$term <- c(
  "Intercept"
  ,"Power Distance"
  ,"Individualism"
  ,"Masculinity"
  ,"Uncertainty Avoidance"
  ,"Long Term Orientation"
  ,"Indulgence"
  ,"Tightness: Domain General"
  ,"Tightness: Domain Specific"
  ,"Tightness: Combination Measure"
)

variable_label(results_for_table$estimate) <- "$b$"
variable_label(results_for_table$StdError) <- "$S.E.$"
variable_label(results_for_table$term) <- "Predictor"

```

We did not make specific predictions regarding the relationship between internalization and the selected cultural variables. As such, the analyses below are exploratory. We conducted a regression analysis to investigate the relationship bewteen these cultural variables and internalization. We entered internalization as our outcome measure and included each of power distance, individualism, masculinity, uncertainty avoidance, long term orientation, and indulgence, and the three dimensions of cultural tightness (domain-specific, domain-general, and a combination index) as predictor variables.

Overall the model was a significant predictor of internalization `r apa_fit_results$full_result$modelfit$r2`. The full regression results are displayed in Table\ \@ref(tab:regressionTable2).

```{r regressionTable2, include=TRUE}
apa_table(
  results_for_table
#  , align = c("c", "c", "c")
  , caption = "Full Regression Results for each country level variable predicting internalization"
  )

```

In contrast to symbolization, power distance was negatively related to internalization.

Similarly, individualism showed a negative relationship with internalization.

Masculinity was unrelated to internalization.

Uncertainty avoidance and long-term orientation were both negatively related to internalization.

Indulgence was positively related to internalization.

Regarding cultural tightness, both domain genera, and the combination measure were both positively related to internalization, while domain specific tightness was negatively related to internalization.

### 2023-02-10 H1.Rmd
heat maps and flag plots added

@@
 df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
+
+```
+
+```{r}
+
+## Internalization
+
+alpha_generic <- function(x){
+  df <- x
+
+  df$moralid4R <- reverse.code(c(-1), df$moralid4)
+  df$moralid7R <- reverse.code(-1, df$moralid7)
+
+  y <- subset(df,select=c(
+    moralid1
+    , moralid2
+    , moralid4R
+    , moralid7R
+    , moralid10
+  ))
+  cronbach.alpha(y[complete.cases(y),])
+}
+
+alpha_generic(df)
+
+## Symbolization
+
+alpha_generic <- function(x){
+  df <- x
+  y <- subset(df,select=c(
+    moralid3
+  , moralid5
+  , moralid6
+  , moralid8
+  , moralid9
+))
+  cronbach.alpha(y[complete.cases(y),])
+}
+
+alpha_generic(df)
 
@@
         strip.background  = element_blank(),
-        panel.grid = element_blank(),
+       # panel.grid = element_blank(),
         plot.title=element_text(#family="Times",
@@
         strip.background  = element_blank(),
-        panel.grid = element_blank(),
+     #   panel.grid = element_blank(),
         plot.title=element_text(#family="Times",

### 2023-02-10 H2.Rmd
heat maps and flag plots added

@@
 *p* `r paste(p_report(p2))`.
-We conducted a series of correlations test if age was related to internalization across all countries.
+To interpret this we conducted a series of bivariate correlations to test if age was related to internalization across all countries.
 There was a significant correlation between age and internalization in `r total_sig` countries.
@@
 *p* `r paste(p_report(p2))`.
-We conducted a series of correlations test if age was related to internalization across all countries.
+Again, to interpret this, we conducted a series of correlations to test if age was related to internalization across all countries.
 There was a significant correlation between age and internalization in `r total_sig` countries.

### 2023-02-10 H3.Rmd
heat maps and flag plots added

@@
 library(countrycode)
+
 ```
@@
 
-fit0 <- lm(moral_identity_symbolic ~ 
-             mean(x$moral_identity_symbolic)
+fit <- lm(moral_identity_symbolic ~
                     # sex3
                     # + age
-                    #  Power.Distance
-                    # + Individualism
-                    # + Masculinity
-                    # + Uncertainty.Avoidance
+                     Power.Distance
+                    + Individualism
+                    + Masculinity
+                    + Uncertainty.Avoidance
                     # + Long.Term.Orientation
                     # + Indulgence
+                    # + CTL_DG
+                    # + CTL_DS
                     # + CTL_C
-                    # + CTL_DS
-                    # + CTL_DG
                 , data = x
             )
+fit
+fit_results <- summary(fit)
+fit_results
 
-summary(fit0)
+fit_results$adj.r.squared
+anova(fit)
+apa_fit_results <- apa_print(fit)
+
+cor.test(x$Power.Distance,x$moral_identity_symbolic)
+
+apa_fit_results$full_result$modelfit$r2
+fit$qr
+apa_fit_results$table
+results_for_table <- apa_fit_results$table
+
+estimate_for_table <-
+  `colnames<-`(
+    cbind.data.frame(
+      unlist(fit_results$coefficients[,1])
+      ,names(unlist(fit_results$coefficients[,1]))
+    ), c("estimate","rows"))$estimate
+
+stderror_for_table <-
+  `colnames<-`(
+    cbind.data.frame(
+      unlist(fit_results$coefficients[,2])
+      ,names(unlist(fit_results$coefficients[,2]))
+    ), c("stderror","rows"))$stderror
+
+estimate_for_table
+stderror_for_table
+
+results_for_table$estimate <- estimate_for_table
+results_for_table$StdError <- stderror_for_table
+
+results_for_table <- results_for_table[c(1,2,7,3,4,5,6)]
+
+results_for_table$estimate <- sprintf("%.3f", results_for_table$estimate)
+results_for_table$StdError <- sprintf("%.3f", results_for_table$StdError)
+
+# library(Hmisc)
+# 
+# var.labels = 
+#   c(
+#     term        = "Predictor" 
+#     , "estimate"  = "$b$" 
+#     , "StdError"  = "$S.E.$"
+#     , conf.int  = "95\\% CI" 
+#     , statistic = "$t$" 
+#     , df        = "$\\mathit{df}$" 
+#     , p.value   = "$p$" 
+#     )
+# 
+# label(results_for_table) = as.list(var.labels[match(names(results_for_table), names(var.labels))])
+
+results_for_table$term <- c(
+  "Intercept"
+  ,"Power Distance"
+  ,"Individualism"
+  ,"Masculinity"
+  ,"Uncertainty Avoidance"
+  ,"Long Term Orientation"
+  ,"Indulgence"
+  ,"Tightness: Domain General"
+  ,"Tightness: Domain Specific"
+  ,"Tightness: Combination Measure"
+)
+
+variable_label(results_for_table$estimate) <- "$b$"
+variable_label(results_for_table$StdError) <- "$S.E.$"
+variable_label(results_for_table$term) <- "Predictor"
+
+```
+
+```{r}
+
+# h3a yes
+# h3b n/a (competing)
+# h3c yes
+# h3d no (no relationship)
+# h3e yes
+# h3f yes
+# h3g no, no, yes
+
+x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
 
@@
                     + Indulgence
+                    + CTL_DG
+                    + CTL_DS
                     + CTL_C
-                    + CTL_DS
-                    + CTL_DG
                 , data = x
@@
 
-summary(fit)
+fit_results <- summary(fit)
+fit_results$adj.r.squared
 anova(fit)
-fit_results <- apa_print(fit)
+apa_fit_results <- apa_print(fit)
 
@@
 
-fit_results$full_result
+apa_fit_results$full_result$modelfit$r2
+fit$qr
+apa_fit_results$table
+results_for_table <- apa_fit_results$table
+
+estimate_for_table <-
+  `colnames<-`(
+    cbind.data.frame(
+      unlist(fit_results$coefficients[,1])
+      ,names(unlist(fit_results$coefficients[,1]))
+    ), c("estimate","rows"))$estimate
+
+stderror_for_table <-
+  `colnames<-`(
+    cbind.data.frame(
+      unlist(fit_results$coefficients[,2])
+      ,names(unlist(fit_results$coefficients[,2]))
+    ), c("stderror","rows"))$stderror
+
+estimate_for_table
+stderror_for_table
+
+results_for_table$estimate <- estimate_for_table
+results_for_table$StdError <- stderror_for_table
+
+results_for_table <- results_for_table[c(1,2,7,3,4,5,6)]
+
+results_for_table$estimate <- sprintf("%.3f", results_for_table$estimate)
+results_for_table$StdError <- sprintf("%.3f", results_for_table$StdError)
+
+# library(Hmisc)
+# 
+# var.labels = 
+#   c(
+#     term        = "Predictor" 
+#     , "estimate"  = "$b$" 
+#     , "StdError"  = "$S.E.$"
+#     , conf.int  = "95\\% CI" 
+#     , statistic = "$t$" 
+#     , df        = "$\\mathit{df}$" 
+#     , p.value   = "$p$" 
+#     )
+# 
+# label(results_for_table) = as.list(var.labels[match(names(results_for_table), names(var.labels))])
+
+results_for_table$term <- c(
+  "Intercept"
+  ,"Power Distance"
+  ,"Individualism"
+  ,"Masculinity"
+  ,"Uncertainty Avoidance"
+  ,"Long Term Orientation"
+  ,"Indulgence"
+  ,"Tightness: Domain General"
+  ,"Tightness: Domain Specific"
+  ,"Tightness: Combination Measure"
+)
+
+variable_label(results_for_table$estimate) <- "$b$"
+variable_label(results_for_table$StdError) <- "$S.E.$"
+variable_label(results_for_table$term) <- "Predictor"
 
@@
 Symbolization was our outcome measure and each cultural variable was included as a predictor in the model.
+
+Overall the model was a significant predictor of symbolization `r apa_fit_results$full_result$modelfit$r2`. The full regression results are displayed in Table\ \@ref(tab:regressionTable).
+
+```{r regressionTable, include=TRUE}
+apa_table(
+  results_for_table
+#  , align = c("c", "c", "c")
+  , caption = "Full Regression Results for each country level variable predicting symbolization"
+  )
+
+```
+
+In line with H3a greater power distance was associated with higher symbolization scores.
+
+We proposed two competing hypotheses for the relationship between symbolization and symbolization.
+H3b~1~ predicted that symbolization would be negatively related to individualism (i.e., higher symbolization would be observed in more collectivist cultures).
+H3b~2~ predicted that individualism and symbolization would be positively associated.
+Our results support H3b~2~ (over H3b~1~), suggesting that members of more individualistic societies show greater symbolization scores.
+
+We predicted that members of more masculine cultures would score higher in symbolization (H3c). Our results were in line with this prediction.
+
+For H3d we predicted that uncertainty avoidance would be related to higher symbolization. This was not supported, and we found no relationship between symbolization and uncertainty avoidance.
+
+We predicted a negative association between long-term orientation and symbolization (H3e), that is, we expected participants in societies showing greater long-term orientation to present with lower symbolization scores.
+Our results supported this hypothesis.
+
+Regarding indulgence/restraint, we predicted (H3f) that greater indulgence would be related to higher symbolization scores, and this hypothesis was supported.
+
+We employed measures of three dimensions of cultural tightness, domain-general, domain-specific, and combination, and predicted that symbolization would be positively associated with each dimension.
+Our hypothesis was supported for only one dimension (domain-general).
+Interestingly, both domain-specific and combination dimensions of cultural tightness were negatively related to symbolization.

### 2023-02-10 supp_H1.Rmd
created links to supplementary within the main results
heat maps and flag plots added

@@
 library(countrycode)
+library(sf)
+# install.packages("rnaturalearth")
+# install.packages("rnaturalearthdata")
+library("rnaturalearth")
+library("rnaturalearthdata")
+
 ```
@@
 
-test <- `colnames<-`(test, c("Total N","n Female","N male"))
+test <- `colnames<-`(test, c("Total N","n Female","n Male"))
 
@@
 
+### Heat Map
+
+```{r, include=FALSE}
+
+world <- ne_countries(scale = "medium", returnclass = "sf")
+world
+
+#country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
+
+test$country <- rownames(test)
+test$name <- test$country
+
+test_sig <- test[which(test$p<.05),]
+test_sig$mean_diff <- test_sig$`mean F`-test_sig$`mean M`
+
+test_non_sig <- test[which(test$p>.05),]
+test_non_sig$mean_diff <- rep(0, length(test_non_sig$`mean F`))
+rbind.data.frame(test_sig,test_non_sig)
+test <- rbind.data.frame(test_sig,test_non_sig)
+
+#test <- test[which(test$p<.05),]
+
+test1 <- left_join(world,test, by = "name")
+
+#test1$mean_diff <- test1$`mean F`-test1$`mean M`
+
+#install.packages("sf")
+#library(sf)
+g1 <- ggplot(test1
+       ,aes(fill=mean_diff)
+       )+
+  geom_sf()+
+  scale_fill_gradient2(
+  low = "blue", #muted("red"),
+  mid = "grey90",
+  high = "red", #muted("blue"),
+  midpoint = 0,
+  space = "Lab",
+  na.value = "white",
+  guide = "colourbar",
+  aesthetics = "fill"
+)+
+  labs(fill = "Mean\nDifference")+
+  theme_bw()+
+  theme(#legend.position = "none"
+   plot.title=element_text(#family="Times",
+    size=12
+  )
+  , legend.text=element_text(#family="Times",
+    size=8
+  )
+  , legend.title=element_text(#family="Times",
+    size=10
+  )
+  , axis.text=element_text(#family="Times",
+    colour = "black",
+    size=8
+  )
+  , axis.ticks.x = element_blank()
+  , axis.title=element_text(#family="Times",
+    size=12
+  )
+  , strip.text=element_text(#family = "Times",
+    size = 12
+  )
+  , strip.background = element_rect(fill = NA, size = 1,
+                                    colour = "white"
+  )
+  , panel.border = element_blank()
+  , axis.line.x = element_line(size = 0.1
+                               , linetype = "solid", colour = "black")
+  , axis.line.y = # element_blank()
+    element_line(size = 0.1
+                 , linetype = "solid", colour = "black")
+  #, legend.position="none"
+  , panel.spacing = unit(2, "lines")
+  )
+
+ggsave("plots/internalization_heatmap.png", g1, width = 10, height = 6, units = "in", dpi = 300)
+
+```
+
+```{r, InternalizationHeatMAp,fig.cap="Effect size for gender differences in Internalization across countries",include=TRUE}
+suppressWarnings(print(g1))
+
+```
+
 ## Symbolization
@@
 <div id="wrapper"><iframe id="scaled-frame" src="plots/internalization.png"></iframe></div>
+
+### Heat Map
+
+```{r, include=FALSE}
+
+world <- ne_countries(scale = "medium", returnclass = "sf")
+world
+
+#country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
+
+test$country <- rownames(test)
+test$name <- test$country
+
+test_sig <- test[which(test$p<.05),]
+test_sig$mean_diff <- test_sig$`mean F`-test_sig$`mean M`
+
+test_non_sig <- test[which(test$p>.05),]
+test_non_sig$mean_diff <- rep(0, length(test_non_sig$`mean F`))
+test_non_sig$`mean F`
+length(test_non_sig$`mean F`)
+test <- rbind.data.frame(test_sig,test_non_sig)
+
+test1 <- left_join(world,test, by = "name")
+
+#test1$mean_diff <- test1$`mean F`-test1$`mean M`
+
+#install.packages("sf")
+#library(sf)
+g1 <- ggplot(test1
+       ,aes(fill=mean_diff)
+       )+
+  geom_sf()+
+  scale_fill_gradient2(
+  low = "blue", #muted("red"),
+  mid = "grey95",
+  high = "red", #muted("blue"),
+  midpoint = 0,
+  space = "Lab",
+  na.value = "white",
+  guide = "colourbar",
+  aesthetics = "fill"
+)+
+  labs(fill = "Mean\nDifference")+
+  theme_bw()+
+  theme(#legend.position = "none"
+   plot.title=element_text(#family="Times",
+    size=12
+  )
+  , legend.text=element_text(#family="Times",
+    size=8
+  )
+  , legend.title=element_text(#family="Times",
+    size=10
+  )
+  , axis.text=element_text(#family="Times",
+    colour = "black",
+    size=8
+  )
+  , axis.ticks.x = element_blank()
+  , axis.title=element_text(#family="Times",
+    size=12
+  )
+  , strip.text=element_text(#family = "Times",
+    size = 12
+  )
+  , strip.background = element_rect(fill = NA, size = 1,
+                                    colour = "white"
+  )
+  , panel.border = element_blank()
+  , axis.line.x = element_line(size = 0.1
+                               , linetype = "solid", colour = "black")
+  , axis.line.y = # element_blank()
+    element_line(size = 0.1
+                 , linetype = "solid", colour = "black")
+  #, legend.position="none"
+  , panel.spacing = unit(2, "lines")
+  )
+
+ggsave("plots/symbolization_heatmap.png", g1, width = 10, height = 6, units = "in", dpi = 300)
+
+```
+
+```{r, SymbolizationHeatMAp,fig.cap="Effect size for gender differences in Symbolization across countries",include=TRUE}
+suppressWarnings(print(g1))
+
+```

### 2023-02-10 supp_H3.Rmd
heat maps and flag plots added

@@
 ---
-title: "H2 Supplement"
+title: "H3 Supplement"
 author: "Mariola Paruzel-Czachura, Cillian McHugh"
@@
 library(rworldmap)
-#devtools::install_github("rensa/ggflags")
+#install.packages("grConvert")
+#devtools::install_github("sjp/grConvert")
+library(grConvert)
+#remove.packages("grImport2")
+#install.packages("grImport2")
+library(grImport2)
+#install.packages("ragg")
+#remove.packages("ggflags")
+#install.packages("devtools")
+#devtools::install_github("jimjam-slam/ggflags", force = TRUE)
+#help("install_github")
+#devtools::install_github("rensa/ggflags", force = TRUE, dependencies = TRUE)
 library(ggflags)
@@
 library(countrycode)
+
+source('modify_flags.R')
+
 ```
@@
 ```
+
+## Power Distance
+## Power Distance
+
+```{r}
+x <- df
+
+x <- x[which(is.na(x$Power.Distance)==FALSE),]
+
+x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
+x$iso2 <- tolower(x$ISO2)
+
+x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )
+
+means_fun <- function(x){
+  mean(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_means <- lapply(x, means_fun)
+sd_fun <- function(x){
+  sd(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_sds <- lapply(x, sd_fun)
+N_fun <- function(x){
+  length(x$sex3)
+}
+Ns <- lapply(x, N_fun)
+
+power_means_fun <- function(x){
+  mean(x$Power.Distance)
+}
+power_score <- lapply(x, power_means_fun)
+x$Ukraine$Power.Distance
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, symbolic_means),digits=2)
+    ,round(do.call(rbind, symbolic_sds),digits=2)
+    ,round(do.call(rbind, power_score),digits=2)
+    ,round(do.call(rbind, Ns),digits=2)
+    )
+
+test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
+test$iso2c <- rownames(test)
+#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- tolower(test$iso2c)
+test$country <- countrycode(test$iso2c, "iso2c", "country.name")
+
+test
+```
+
+```{r}
+
+h1 <- .3
+w1 <- .5
+s1 <- 18
+
+lm_fit_intercept <- lm(moral_identity_symbolic ~ Power.Distance, data = df)
+
+lm_fit <- lm(moral_identity_symbolic ~
+                    # sex3
+                    # + age
+                     Power.Distance
+                    + Individualism
+                    + Masculinity
+                    + Uncertainty.Avoidance
+                    + Long.Term.Orientation
+                    + Indulgence
+                    + CTL_DG
+                    + CTL_DS
+                    + CTL_C
+                , data = df
+            )
+lm_fit$coefficients
+
+lm_fit$coefficients[1]
+lm_fit$coefficients[2]
+
+g1 <- ggplot(test, aes(power_score
+                       ,symbolic_means
+                       ,country=iso2c
+                       #,size=Ns
+))+
+  geom_abline(slope=lm_fit_intercept$coefficients[2],
+              #slope=lm_fit$coefficients[2],
+              intercept=lm_fit_intercept$coefficients[1],
+              color="darkgrey",
+              size=.5)+
+  #geom_point(size=13,color="black")+
+  geom_flag(
+    position=position_jitter(
+      h = h1
+      , w = w1
+      , seed = s1)
+    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
+    #)
+    ,size=7.5
+  )+
+  scale_country()+
+  #scale_size(range = c(8,10))+
+  geom_text(aes(power_score,symbolic_means),label=test$country
+            ,vjust=3.8
+            ,hjust=.44
+            #,nudge_x = .03
+            ,size = 1.6
+            #,check_overlap = TRUE
+            ,position = position_jitter(
+              h = h1
+              , w = w1
+              , seed = s1
+            )
+  )+
+  xlab("Power Distance")+
+  ylab("Symbolization")+
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        #panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/power_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)
+
+```
+
+```{r, Symbolizationpower,fig.cap="Relationship between Power Diatance and Symbolization",include=TRUE}
+suppressWarnings(print(g1))
+
+```
+
+## Individualism
+
+```{r}
+x <- df
+x$Individualism
+x <- x[which(is.na(x$Individualism)==FALSE),]
+
+x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
+x$iso2 <- tolower(x$ISO2)
+
+x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )
+
+means_fun <- function(x){
+  mean(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_means <- lapply(x, means_fun)
+sd_fun <- function(x){
+  sd(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_sds <- lapply(x, sd_fun)
+N_fun <- function(x){
+  length(x$sex3)
+}
+Ns <- lapply(x, N_fun)
+
+power_means_fun <- function(x){
+  mean(x$Individualism)
+}
+power_score <- lapply(x, power_means_fun)
+x$Ukraine$Power.Distance
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, symbolic_means),digits=2)
+    ,round(do.call(rbind, symbolic_sds),digits=2)
+    ,round(do.call(rbind, power_score),digits=2)
+    ,round(do.call(rbind, Ns),digits=2)
+    )
+
+test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
+test$iso2c <- rownames(test)
+#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- tolower(test$iso2c)
+test$country <- countrycode(test$iso2c, "iso2c", "country.name")
+
+test
+```
+
+```{r}
+
+h1 <- .3
+w1 <- .5
+s1 <- 18
+
+lm_fit_intercept <- lm(moral_identity_symbolic ~ Individualism, data = df)
+
+lm_fit <- lm(moral_identity_symbolic ~
+                    # sex3
+                    # + age
+                     Power.Distance
+                    + Individualism
+                    + Masculinity
+                    + Uncertainty.Avoidance
+                    + Long.Term.Orientation
+                    + Indulgence
+                    + CTL_DG
+                    + CTL_DS
+                    + CTL_C
+                , data = df
+            )
+
+lm_fit$coefficients[1]
+lm_fit$coefficients[3]
+
+g1 <- ggplot(test, aes(power_score
+                       ,symbolic_means
+                       ,country=iso2c
+                       #,size=Ns
+))+
+  geom_abline(slope=lm_fit_intercept$coefficients[2],
+              #slope=lm_fit$coefficients[3],
+              intercept=lm_fit_intercept$coefficients[1],
+              color="darkgrey",
+              size=.5)+
+  #geom_point(size=13,color="black")+
+  geom_flag(
+    position=position_jitter(
+      h = h1
+      , w = w1
+      , seed = s1)
+    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
+    #)
+    ,size=7.5
+  )+
+  scale_country()+
+  #scale_size(range = c(8,10))+
+  geom_text(aes(power_score,symbolic_means),label=test$country
+            ,vjust=3.8
+            ,hjust=.44
+            #,nudge_x = .03
+            ,size = 1.6
+            #,check_overlap = TRUE
+            ,position = position_jitter(
+              h = h1
+              , w = w1
+              , seed = s1
+            )
+  )+
+  xlab("Individualism")+
+  ylab("Symbolization")+
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        #panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/individualism_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)
+
+```
+
+```{r, SymbolizationIndividualism,fig.cap="Relationship between Individualism and Symbolization",include=TRUE}
+suppressWarnings(print(g1))
+
+```
+
+## Masculinity
+
+```{r}
+x <- df
+
+df$Uncertainty.Avoidance
+x <- x[which(is.na(x$Masculinity)==FALSE),]
+
+x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
+x$iso2 <- tolower(x$ISO2)
+
+x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )
+
+means_fun <- function(x){
+  mean(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_means <- lapply(x, means_fun)
+sd_fun <- function(x){
+  sd(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_sds <- lapply(x, sd_fun)
+N_fun <- function(x){
+  length(x$sex3)
+}
+Ns <- lapply(x, N_fun)
+
+power_means_fun <- function(x){
+  mean(x$Masculinity)
+}
+power_score <- lapply(x, power_means_fun)
+x$Ukraine$Uncertainty.Avoidance
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, symbolic_means),digits=2)
+    ,round(do.call(rbind, symbolic_sds),digits=2)
+    ,round(do.call(rbind, power_score),digits=2)
+    ,round(do.call(rbind, Ns),digits=2)
+    )
+
+test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
+test$iso2c <- rownames(test)
+#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- tolower(test$iso2c)
+test$country <- countrycode(test$iso2c, "iso2c", "country.name")
+
+test
+```
+
+```{r}
+
+h1 <- .3
+w1 <- .5
+s1 <- 18
+
+lm_fit_intercept <- lm(moral_identity_symbolic ~ Masculinity, data = df)
+
+lm_fit <- lm(moral_identity_symbolic ~
+                    # sex3
+                    # + age
+                     Power.Distance
+                    + Individualism
+                    + Masculinity
+                    + Uncertainty.Avoidance
+                    + Long.Term.Orientation
+                    + Indulgence
+                    + CTL_DG
+                    + CTL_DS
+                    + CTL_C
+                , data = df
+            )
+
+lm_fit$coefficients[1]
+lm_fit$coefficients[2]
+
+g1 <- ggplot(test, aes(power_score
+                       ,symbolic_means
+                       ,country=iso2c
+                       #,size=Ns
+))+
+  geom_abline(slope=lm_fit_intercept$coefficients[2],
+              #slope=lm_fit$coefficients[5],
+              intercept=lm_fit_intercept$coefficients[1],
+              color="darkgrey",
+              size=.5)+
+  #geom_point(size=13,color="black")+
+  geom_flag(
+    position=position_jitter(
+      h = h1
+      , w = w1
+      , seed = s1)
+    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
+    #)
+    ,size=7.5
+  )+
+  scale_country()+
+  #scale_size(range = c(8,10))+
+  geom_text(aes(power_score,symbolic_means),label=test$country
+            ,vjust=3.8
+            ,hjust=.44
+            #,nudge_x = .03
+            ,size = 1.6
+            #,check_overlap = TRUE
+            ,position = position_jitter(
+              h = h1
+              , w = w1
+              , seed = s1
+            )
+  )+
+  xlab("Masculinity")+
+  ylab("Symbolization")+
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        #panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/masc_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)
+
+```
+
+```{r, SymbolizationMasc,fig.cap="Relationship between Masculinity and Symbolization",include=TRUE}
+suppressWarnings(print(g1))
+
+```
+
+## Long Term Orientation
+
+```{r}
+x <- df
+
+x$Long.Term.Orientation
+x <- x[which(is.na(x$Long.Term.Orientation)==FALSE),]
+
+x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
+x$iso2 <- tolower(x$ISO2)
+
+x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )
+
+means_fun <- function(x){
+  mean(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_means <- lapply(x, means_fun)
+sd_fun <- function(x){
+  sd(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_sds <- lapply(x, sd_fun)
+N_fun <- function(x){
+  length(x$sex3)
+}
+Ns <- lapply(x, N_fun)
+
+power_means_fun <- function(x){
+  mean(x$Long.Term.Orientation)
+}
+power_score <- lapply(x, power_means_fun)
+x$Ukraine$Long.Term.Orientation
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, symbolic_means),digits=2)
+    ,round(do.call(rbind, symbolic_sds),digits=2)
+    ,round(do.call(rbind, power_score),digits=2)
+    ,round(do.call(rbind, Ns),digits=2)
+    )
+
+test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
+test$iso2c <- rownames(test)
+#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- tolower(test$iso2c)
+test$country <- countrycode(test$iso2c, "iso2c", "country.name")
+
+test
+```
+
+```{r}
+
+h1 <- .3
+w1 <- .5
+s1 <- 18
+
+lm_fit_intercept <- lm(moral_identity_symbolic ~ Long.Term.Orientation, data = df)
+
+lm_fit <- lm(moral_identity_symbolic ~
+                    # sex3
+                    # + age
+                     Power.Distance
+                    + Individualism
+                    + Masculinity
+                    + Uncertainty.Avoidance
+                    + Long.Term.Orientation
+                    + Indulgence
+                    + CTL_DG
+                    + CTL_DS
+                    + CTL_C
+                , data = df
+            )
+
+lm_fit
+lm_fit$coefficients[1]
+lm_fit$coefficients[6]
+
+g1 <- ggplot(test, aes(power_score
+                       ,symbolic_means
+                       ,country=iso2c
+                       #,size=Ns
+))+
+  geom_abline(slope=lm_fit_intercept$coefficients[2],
+              #slope=lm_fit$coefficients[6],
+              intercept=lm_fit_intercept$coefficients[1],
+              color="darkgrey",
+              size=.5)+
+  #geom_point(size=13,color="black")+
+  geom_flag(
+    position=position_jitter(
+      h = h1
+      , w = w1
+      , seed = s1)
+    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
+    #)
+    ,size=7.5
+  )+
+  scale_country()+
+  #scale_size(range = c(8,10))+
+  geom_text(aes(power_score,symbolic_means),label=test$country
+            ,vjust=3.8
+            ,hjust=.44
+            #,nudge_x = .03
+            ,size = 1.6
+            #,check_overlap = TRUE
+            ,position = position_jitter(
+              h = h1
+              , w = w1
+              , seed = s1
+            )
+  )+
+  xlab("Long Term Orientation")+
+  ylab("Symbolization")+
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        #panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/LTO_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)
+
+```
+
+```{r, SymbolizationLTO,fig.cap="Relationship between Long Term Orientation and Symbolization",include=TRUE}
+suppressWarnings(print(g1))
+
+```
+
+## Indulgence
+
+```{r}
+x <- df
+x$Indulgence
+x <- x[which(is.na(x$Indulgence)==FALSE),]
+
+x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
+x$iso2 <- tolower(x$ISO2)
+
+x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )
+
+means_fun <- function(x){
+  mean(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_means <- lapply(x, means_fun)
+sd_fun <- function(x){
+  sd(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_sds <- lapply(x, sd_fun)
+N_fun <- function(x){
+  length(x$sex3)
+}
+Ns <- lapply(x, N_fun)
+
+power_means_fun <- function(x){
+  mean(x$Indulgence)
+}
+power_score <- lapply(x, power_means_fun)
+x$Ukraine$Indulgence
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, symbolic_means),digits=2)
+    ,round(do.call(rbind, symbolic_sds),digits=2)
+    ,round(do.call(rbind, power_score),digits=2)
+    ,round(do.call(rbind, Ns),digits=2)
+    )
+
+test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
+test$iso2c <- rownames(test)
+#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- tolower(test$iso2c)
+test$country <- countrycode(test$iso2c, "iso2c", "country.name")
+
+test
+```
+
+```{r}
+
+h1 <- .3
+w1 <- .5
+s1 <- 18
+
+lm_fit_intercept <- lm(moral_identity_symbolic ~ Indulgence, data = df)
+
+lm_fit <- lm(moral_identity_symbolic ~
+                    # sex3
+                    # + age
+                     Power.Distance
+                    + Individualism
+                    + Masculinity
+                    + Uncertainty.Avoidance
+                    + Long.Term.Orientation
+                    + Indulgence
+                    + CTL_DG
+                    + CTL_DS
+                    + CTL_C
+                , data = df
+            )
+
+lm_fit$coefficients[1]
+lm_fit$coefficients[2]
+
+g1 <- ggplot(test, aes(power_score
+                       ,symbolic_means
+                       ,country=iso2c
+                       #,size=Ns
+))+
+  geom_abline(slope=lm_fit_intercept$coefficients[2],
+              #slope=lm_fit$coefficients[7],
+              intercept=lm_fit_intercept$coefficients[1],
+              color="darkgrey",
+              size=.5)+
+  #geom_point(size=13,color="black")+
+  geom_flag(
+    position=position_jitter(
+      h = h1
+      , w = w1
+      , seed = s1)
+    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
+    #)
+    ,size=7.5
+  )+
+  scale_country()+
+  #scale_size(range = c(8,10))+
+  geom_text(aes(power_score,symbolic_means),label=test$country
+            ,vjust=3.8
+            ,hjust=.44
+            #,nudge_x = .03
+            ,size = 1.6
+            #,check_overlap = TRUE
+            ,position = position_jitter(
+              h = h1
+              , w = w1
+              , seed = s1
+            )
+  )+
+  xlab("Indulgence")+
+  ylab("Symbolization")+
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        #panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/indulgence_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)
+
+```
+
+```{r, SymbolizationIndulgence,fig.cap="Relationship between Indulgence and Symbolization",include=TRUE}
+suppressWarnings(print(g1))
+
+```
+
+## Tightness Domain General
+
+```{r}
+x <- df
+x$CTL_DG
+x <- x[which(is.na(x$CTL_DG)==FALSE),]
+
+x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
+x$iso2 <- tolower(x$ISO2)
+
+x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )
+
+means_fun <- function(x){
+  mean(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_means <- lapply(x, means_fun)
+sd_fun <- function(x){
+  sd(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_sds <- lapply(x, sd_fun)
+N_fun <- function(x){
+  length(x$sex3)
+}
+Ns <- lapply(x, N_fun)
+
+power_means_fun <- function(x){
+  mean(x$CTL_DG)
+}
+power_score <- lapply(x, power_means_fun)
+x$Ukraine$CTL_DG
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, symbolic_means),digits=2)
+    ,round(do.call(rbind, symbolic_sds),digits=2)
+    ,round(do.call(rbind, power_score),digits=2)
+    ,round(do.call(rbind, Ns),digits=2)
+    )
+
+test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
+test$iso2c <- rownames(test)
+#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- tolower(test$iso2c)
+test$country <- countrycode(test$iso2c, "iso2c", "country.name")
+
+test
+```
+
+```{r}
+
+h1 <- .3
+w1 <- .5
+s1 <- 18
+
+lm_fit_intercept <- lm(moral_identity_symbolic ~ CTL_DG, data = df)
+
+lm_fit <- lm(moral_identity_symbolic ~
+                    # sex3
+                    # + age
+                     Power.Distance
+                    + Individualism
+                    + Masculinity
+                    + Uncertainty.Avoidance
+                    + Long.Term.Orientation
+                    + Indulgence
+                    + CTL_DG
+                    + CTL_DS
+                    + CTL_C
+                , data = df
+            )
+
+lm_fit$coefficients[1]
+lm_fit$coefficients[2]
+
+g1 <- ggplot(test, aes(power_score
+                       ,symbolic_means
+                       ,country=iso2c
+                       #,size=Ns
+))+
+  geom_abline(slope=lm_fit_intercept$coefficients[2],
+              #slope=lm_fit$coefficients[8],
+              intercept=lm_fit_intercept$coefficients[1],
+              color="darkgrey",
+              size=.5)+
+  #geom_point(size=13,color="black")+
+  geom_flag(
+    position=position_jitter(
+      h = h1
+      , w = w1
+      , seed = s1)
+    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
+    #)
+    ,size=7.5
+  )+
+  scale_country()+
+  #scale_size(range = c(8,10))+
+  geom_text(aes(power_score,symbolic_means),label=test$country
+            ,vjust=3.8
+            ,hjust=.44
+            #,nudge_x = .03
+            ,size = 1.6
+            #,check_overlap = TRUE
+            ,position = position_jitter(
+              h = h1
+              , w = w1
+              , seed = s1
+            )
+  )+
+  xlab("Tightness: Domain General")+
+  ylab("Symbolization")+
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        #panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/ct_dg_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)
+
+```
+
+```{r, SymbolizationTDG,fig.cap="Relationship between Domain General Tightness and Symbolization",include=TRUE}
+suppressWarnings(print(g1))
+
+```
+
+## Tightness Domain Specific
+
+```{r}
+x <- df
+x$CTL_DS
+x <- x[which(is.na(x$CTL_DS)==FALSE),]
+
+x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
+x$iso2 <- tolower(x$ISO2)
+
+x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )
+
+means_fun <- function(x){
+  mean(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_means <- lapply(x, means_fun)
+sd_fun <- function(x){
+  sd(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_sds <- lapply(x, sd_fun)
+N_fun <- function(x){
+  length(x$sex3)
+}
+Ns <- lapply(x, N_fun)
+
+power_means_fun <- function(x){
+  mean(x$CTL_DS)
+}
+power_score <- lapply(x, power_means_fun)
+x$Ukraine$CTL_DS
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, symbolic_means),digits=2)
+    ,round(do.call(rbind, symbolic_sds),digits=2)
+    ,round(do.call(rbind, power_score),digits=2)
+    ,round(do.call(rbind, Ns),digits=2)
+    )
+
+test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
+test$iso2c <- rownames(test)
+#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- tolower(test$iso2c)
+test$country <- countrycode(test$iso2c, "iso2c", "country.name")
+
+test
+```
+
+```{r}
+
+h1 <- .3
+w1 <- .5
+s1 <- 18
+
+lm_fit_intercept <- lm(moral_identity_symbolic ~ CTL_DS, data = df)
+
+lm_fit <- lm(moral_identity_symbolic ~
+                    # sex3
+                    # + age
+                     Power.Distance
+                    + Individualism
+                    + Masculinity
+                    + Uncertainty.Avoidance
+                    + Long.Term.Orientation
+                    + Indulgence
+                    + CTL_DG
+                    + CTL_DS
+                    + CTL_C
+                , data = df
+            )
+
+lm_fit$coefficients[1]
+lm_fit$coefficients[2]
+
+g1 <- ggplot(test, aes(power_score
+                       ,symbolic_means
+                       ,country=iso2c
+                       #,size=Ns
+))+
+  geom_abline(slope=lm_fit_intercept$coefficients[2],
+              #slope=lm_fit$coefficients[9],
+              intercept=lm_fit_intercept$coefficients[1],
+              color="darkgrey",
+              size=.5)+
+  #geom_point(size=13,color="black")+
+  geom_flag(
+    position=position_jitter(
+      h = h1
+      , w = w1
+      , seed = s1)
+    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
+    #)
+    ,size=7.5
+  )+
+  scale_country()+
+  #scale_size(range = c(8,10))+
+  geom_text(aes(power_score,symbolic_means),label=test$country
+            ,vjust=3.8
+            ,hjust=.44
+            #,nudge_x = .03
+            ,size = 1.6
+            #,check_overlap = TRUE
+            ,position = position_jitter(
+              h = h1
+              , w = w1
+              , seed = s1
+            )
+  )+
+  xlab("Tightness: Domain Specific")+
+  ylab("Symbolization")+
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        #panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/ct_ds_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)
+
+```
+
+```{r, SymbolizationTDS,fig.cap="Relationship between Domain Specific Tightness and Symbolization",include=TRUE}
+suppressWarnings(print(g1))
+
+```
+
+## Tightness Combination
+
+```{r}
+x <- df
+x$CTL_C
+x <- x[which(is.na(x$CTL_C)==FALSE),]
+
+x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
+x$iso2 <- tolower(x$ISO2)
+
+x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )
+
+means_fun <- function(x){
+  mean(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_means <- lapply(x, means_fun)
+sd_fun <- function(x){
+  sd(x$moral_identity_symbolic,na.rm = T)
+}
+symbolic_sds <- lapply(x, sd_fun)
+N_fun <- function(x){
+  length(x$sex3)
+}
+Ns <- lapply(x, N_fun)
+
+power_means_fun <- function(x){
+  mean(x$CTL_C)
+}
+power_score <- lapply(x, power_means_fun)
+x$Ukraine$CTL_C
+
+test <- 
+  cbind.data.frame(
+     round(do.call(rbind, symbolic_means),digits=2)
+    ,round(do.call(rbind, symbolic_sds),digits=2)
+    ,round(do.call(rbind, power_score),digits=2)
+    ,round(do.call(rbind, Ns),digits=2)
+    )
+
+test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
+test$iso2c <- rownames(test)
+#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
+# test$iso2c <- tolower(test$iso2c)
+test$country <- countrycode(test$iso2c, "iso2c", "country.name")
+
+test
+```
+
+```{r}
+
+h1 <- .3
+w1 <- .5
+s1 <- 18
+
+lm_fit_intercept <- lm(moral_identity_symbolic ~ CTL_C, data = df)
+
+lm_fit <- lm(moral_identity_symbolic ~
+                    # sex3
+                    # + age
+                     Power.Distance
+                    + Individualism
+                    + Masculinity
+                    + Uncertainty.Avoidance
+                    + Long.Term.Orientation
+                    + Indulgence
+                    + CTL_DG
+                    + CTL_DS
+                    + CTL_C
+                , data = df
+            )
+
+lm_fit$coefficients[1]
+lm_fit$coefficients[2]
+
+g1 <- ggplot(test, aes(power_score
+                       ,symbolic_means
+                       ,country=iso2c
+                       #,size=Ns
+))+
+  geom_abline(slope=lm_fit_intercept$coefficients[2],
+              #slope=lm_fit$coefficients[10],
+              intercept=lm_fit_intercept$coefficients[1],
+              color="darkgrey",
+              size=.5)+
+  #geom_point(size=13,color="black")+
+  geom_flag(
+    position=position_jitter(
+      h = h1
+      , w = w1
+      , seed = s1)
+    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
+    #)
+    ,size=7.5
+  )+
+  scale_country()+
+  #scale_size(range = c(8,10))+
+  geom_text(aes(power_score,symbolic_means),label=test$country
+            ,vjust=3.8
+            ,hjust=.44
+            #,nudge_x = .03
+            ,size = 1.6
+            #,check_overlap = TRUE
+            ,position = position_jitter(
+              h = h1
+              , w = w1
+              , seed = s1
+            )
+  )+
+  xlab("Tightness: Combination")+
+  ylab("Symbolization")+
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
+  theme_bw() +
+  theme(panel.border = element_blank(),
+        axis.line = element_line(size = .2),
+        strip.background  = element_blank(),
+        #panel.grid = element_blank(),
+        plot.title=element_text(#family="Times",
+          size=12
+        ),
+        #legend.position="right",
+        legend.text=element_text(#family="Times",
+          size=8
+        ),
+        legend.title=element_text(#family="Times",
+          size=10
+        ),
+        axis.text=element_text(#family="Times",
+          colour = "black",
+          size=8
+        ),
+        axis.ticks.x = element_blank(),
+        axis.title=element_text(#family="Times",
+          size=12
+        ),
+        strip.text=element_text(#family = "Times",
+          size = 12
+        ),
+        # strip.background = element_rect(fill = "white"),
+        legend.position="none")
+
+ggsave("plots/ct_c_symbolization.png", g1, width = 10, height = 6, units = "in", dpi = 300)
+
+```
+
+```{r, SymbolizationTC,fig.cap="Relationship between Tightness: Combination and Symbolization",include=TRUE}
+suppressWarnings(print(g1))
+
+```

### 2023-02-10 supp_H4.Rmd
heat maps and flag plots added

---
title: "H4 Supplement"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }

</style>

```{r setuph4supp, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
```

```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#install.packages("grConvert")
#devtools::install_github("sjp/grConvert")
library(grConvert)
#remove.packages("grImport2")
#install.packages("grImport2")
library(grImport2)
#install.packages("ragg")
#remove.packages("ggflags")
#install.packages("devtools")
#devtools::install_github("jimjam-slam/ggflags", force = TRUE)
#help("install_github")
#devtools::install_github("rensa/ggflags", force = TRUE, dependencies = TRUE)
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)

source('modify_flags.R')

```

```{r}

#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

df$sex3 <- as.factor(df$sex1)
df$sex3 <- dplyr::recode(df$sex3,
               "1"="male"
              ,"2"="female"
              ,"3"="other")

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
```

```{r}
rm(list = ls())
#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

df$sex3 <- as.factor(df$sex1)
df$sex3 <- dplyr::recode(df$sex3,
               "1"="male"
              ,"2"="female"
              ,"3"="other")

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
```

## Power Distance

```{r}
x <- df

x <- x[which(is.na(x$Power.Distance)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_internal,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$Power.Distance)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$Power.Distance

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

```{r}

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_internal ~ Power.Distance, data = df)

lm_fit <- lm(moral_identity_internal ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )
lm_fit$coefficients

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[2],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Power Distance")+
  ylab("Internalization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/power_internalization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, Internalizationpower,fig.cap="Relationship between Power Diatance and Internalization",include=TRUE}
suppressWarnings(print(g1))

```

## Individualism

```{r}
x <- df
x$Individualism
x <- x[which(is.na(x$Individualism)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_internal,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$Individualism)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$Power.Distance

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

```{r}

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_internal ~ Individualism, data = df)

lm_fit <- lm(moral_identity_internal ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[3]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[3],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Individualism")+
  ylab("Internalization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/individualism_internalization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, InternalizationIndividualism,fig.cap="Relationship between Individualism and Internalization",include=TRUE}
suppressWarnings(print(g1))

```

## Uncertainty Avoidance

```{r}
x <- df

df$Uncertainty.Avoidance
x <- x[which(is.na(x$Uncertainty.Avoidance)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_internal,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$Uncertainty.Avoidance)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$Uncertainty.Avoidance

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

```{r}

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_internal ~ Uncertainty.Avoidance, data = df)

lm_fit <- lm(moral_identity_internal ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[5],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Uncertainty Avoidance")+
  ylab("Internalization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/uncertainty_internalization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, InternalizationMasc,fig.cap="Relationship between Uncertainty Avoidance and Internalization",include=TRUE}
suppressWarnings(print(g1))

```

## Long Term Orientation

```{r}
x <- df

x$Long.Term.Orientation
x <- x[which(is.na(x$Long.Term.Orientation)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_internal,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$Long.Term.Orientation)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$Long.Term.Orientation

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

```{r}

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_internal ~ Long.Term.Orientation, data = df)

lm_fit <- lm(moral_identity_internal ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit
lm_fit$coefficients[1]
lm_fit$coefficients[6]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[6],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Long Term Orientation")+
  ylab("Internalization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/LTO_internalization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, InternalizationLTO,fig.cap="Relationship between Long Term Orientation and Internalization",include=TRUE}
suppressWarnings(print(g1))

```

## Indulgence

```{r}
x <- df
x$Indulgence
x <- x[which(is.na(x$Indulgence)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_internal,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$Indulgence)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$Indulgence

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

```{r}

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_internal ~ Indulgence, data = df)

lm_fit <- lm(moral_identity_internal ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[7],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Indulgence")+
  ylab("Internalization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/indulgence_internalization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, InternalizationIndulgence,fig.cap="Relationship between Indulgence and Internalization",include=TRUE}
suppressWarnings(print(g1))

```

## Tightness Domain General

```{r}
x <- df
x$CTL_DG
x <- x[which(is.na(x$CTL_DG)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_internal,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$CTL_DG)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$CTL_DG

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

```{r}

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_internal ~ CTL_DG, data = df)

lm_fit <- lm(moral_identity_internal ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[8],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Tightness: Domain General")+
  ylab("Internalization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/ct_dg_internalization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, InternalizationTDG,fig.cap="Relationship between Domain General Tightness and Internalization",include=TRUE}
suppressWarnings(print(g1))

```

## Tightness Domain Specific

```{r}
x <- df
x$CTL_DS
x <- x[which(is.na(x$CTL_DS)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_internal,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$CTL_DS)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$CTL_DS

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

```{r}

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_internal ~ CTL_DS, data = df)

lm_fit <- lm(moral_identity_internal ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[9],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Tightness: Domain Specific")+
  ylab("Internalization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/ct_ds_internalization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, InternalizationTDS,fig.cap="Relationship between Domain Specific Tightness and Internalization",include=TRUE}
suppressWarnings(print(g1))

```

## Tightness Combination

```{r}
x <- df
x$CTL_C
x <- x[which(is.na(x$CTL_C)==FALSE),]

x$ISO2 <- countrycode(x$ISO3, "iso3c", "iso2c")
x$iso2 <- tolower(x$ISO2)

x <- x %>% group_by(iso2) %>% do(data = (.)) %>% with( set_names(data, iso2) )

means_fun <- function(x){
  mean(x$moral_identity_internal,na.rm = T)
}
symbolic_means <- lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal,na.rm = T)
}
symbolic_sds <- lapply(x, sd_fun)
N_fun <- function(x){
  length(x$sex3)
}
Ns <- lapply(x, N_fun)

power_means_fun <- function(x){
  mean(x$CTL_C)
}
power_score <- lapply(x, power_means_fun)
x$Ukraine$CTL_C

test <- 
  cbind.data.frame(
     round(do.call(rbind, symbolic_means),digits=2)
    ,round(do.call(rbind, symbolic_sds),digits=2)
    ,round(do.call(rbind, power_score),digits=2)
    ,round(do.call(rbind, Ns),digits=2)
    )

test <- `colnames<-`(test, c("symbolic_means","symbolic_sds","power_score", "Ns"))
test$iso2c <- rownames(test)
#autocoup_df$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- countrycode(test$country, "country.name", "iso2c")
# test$iso2c <- tolower(test$iso2c)
test$country <- countrycode(test$iso2c, "iso2c", "country.name")

test
```

```{r}

h1 <- .3
w1 <- .5
s1 <- 18

lm_fit_intercept <- lm(moral_identity_internal ~ CTL_C, data = df)

lm_fit <- lm(moral_identity_internal ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = df
            )

lm_fit$coefficients[1]
lm_fit$coefficients[2]

g1 <- ggplot(test, aes(power_score
                       ,symbolic_means
                       ,country=iso2c
                       #,size=Ns
))+
  geom_abline(slope=lm_fit_intercept$coefficients[2],
              #slope=lm_fit$coefficients[10],
              intercept=lm_fit_intercept$coefficients[1],
              color="darkgrey",
              size=.5)+
  #geom_point(size=13,color="black")+
  geom_flag(
    position=position_jitter(
      h = h1
      , w = w1
      , seed = s1)
    #aes(power_score,symbolic_means,country = iso2c#, size=1#(Ns)
    #)
    ,size=7.5
  )+
  scale_country()+
  #scale_size(range = c(8,10))+
  geom_text(aes(power_score,symbolic_means),label=test$country
            ,vjust=3.8
            ,hjust=.44
            #,nudge_x = .03
            ,size = 1.6
            #,check_overlap = TRUE
            ,position = position_jitter(
              h = h1
              , w = w1
              , seed = s1
            )
  )+
  xlab("Tightness: Combination")+
  ylab("Internalization")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 10))+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/ct_c_internalization.png", g1, width = 10, height = 6, units = "in", dpi = 300)

```

```{r, InternalizationTC,fig.cap="Relationship between Tightness: Combination and Internalization",include=TRUE}
suppressWarnings(print(g1))

```

### 2023-02-10 modify_flags.R

@@ -1,0 +1,35 @@
+library(ggflags)
+
+# data(lflags)
+# set.seed(1234)
+#
+# # 15% opacity gives 2B in the alpha channel
+# .flaglist[["lv"]]@content[[1]]@content[[2]]@content[[1]]@gp$fill <- "#C28FEF2B"
+#   # 33% opacity gives 54 in the alpha channel
+# .flaglist[["qa"]]@content[[1]]@content[[2]]@content[[1]]@gp$fill <- "#9450E054"
+#   d <- data.frame(x=rnorm(10), y=rnorm(10),
+#                   country=sample(c("ar","fr"), 10, TRUE),
+#                   country=sample(c("lv","qa"), 10, TRUE),
+#                   stringsAsFactors = FALSE)
+#   ggplot(d, aes(x=x, y=y, country=country, size=x)) +
+#     geom_flag() +
+#     scale_country()
+
+
+
+    # modify flags
+    # attempt to load the RDA, edit out problematic data, and save it again
+
+    # Looking at the upstream svg, bth the Latvian and Qatari flags appear
+    # to have a semi-transparent overlay over the coloured portions of their
+    # flags. In both cases the fractional opacity is not reflected in the
+    # converted version in the rda.
+
+    data(lflags)
+
+  # 15% opacity gives 2B in the alpha channel
+  .flaglist[["lv"]]@content[[1]]@content[[2]]@content[[1]]@gp$fill <- "#9E3039"
+    # 33% opacity gives 54 in the alpha channel
+  .flaglist[["qa"]]@content[[1]]@content[[2]]@content[[1]]@gp$fill <- "#9450E054"
+
+  save(.flaglist, file="data/lflags.rda")

### 2023-02-10 participants_section.R

@@ -1,0 +1,66 @@
+
+rm(list = ls())
+#source("set_up_data_calculate_means.R")
+load("data/data_with_means_raw.RData")
+
+df$sex3 <- as.factor(df$sex1)
+df$sex3 <- dplyr::recode(df$sex3,
+                         "1"="male"
+                         ,"2"="female"
+                         ,"3"="other")
+
+df$country_lower <- tolower(df$country)
+df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
+
+
+table(df$sex3)
+sum(is.na(df$sex3))
+
+desnum::descriptives(df$age)
+
+
+rm(list = ls())
+#source("set_up_data_calculate_means.R")
+load("data/data_with_means.RData")
+
+df$sex3 <- as.factor(df$sex1)
+df$sex3 <- dplyr::recode(df$sex3,
+                         "1"="male"
+                         ,"2"="female"
+                         ,"3"="other")
+
+df$country_lower <- tolower(df$country)
+df$country_name <- countrycode::countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
+
+
+table(df$sex3)
+sum(is.na(df$sex3))
+
+desnum::descriptives(df$age)
+
+table(x$country_name)
+country_Ns <- table(x$country_name)
+
+
+table(x$country_name)
+country_Ns <- table(x$country_name)
+sum(as.vector(country_Ns)<50)
+
+sum(as.vector(country_Ns)<20)
+sum(as.vector(country_Ns)<100)
+
+sum(as.vector(country_Ns)<500)-sum(as.vector(country_Ns)<100)
+
+##### cultural variables #####
+levels(as.factor(df$country_name[which(is.na(df$Power.Distance))]))
+levels(as.factor(df$country_name[which(is.na(df$Individualism))]))
+levels(as.factor(df$country_name[which(is.na(df$Masculinity))]))
+levels(as.factor(df$country_name[which(is.na(df$Uncertainty.Avoidance))]))
+levels(as.factor(df$country_name[which(is.na(df$Long.Term.Orientation))]))
+levels(as.factor(df$country_name[which(is.na(df$Indulgence))]))
+levels(as.factor(df$country_name[which(is.na(df$CTL_DG))]))
+levels(as.factor(df$country_name[which(is.na(df$CTL_DS))]))
+levels(as.factor(df$country_name[which(is.na(df$CTL_C))]))
+
+
+

### 2023-02-10 rw.R

@@ -246,3 +246,5 @@ alpha(risk_perception_tot)
 
 df$risk_perception_tot <- rowMeans(risk_perception_tot, na.rm = TRUE)
 
+
+

### 2023-07-28 H3_semi_clean.Rmd
ran extra semi-clean analyses

--- 2023-02-10 H3.Rmd
@@
 #source("set_up_data_calculate_means.R")
-load("data/data_with_means.RData")
+load("data/data_with_means_semi_clean.RData")
 
@@
                     + Uncertainty.Avoidance
-                    # + Long.Term.Orientation
-                    # + Indulgence
-                    # + CTL_DG
-                    # + CTL_DS
-                    # + CTL_C
+                    + Long.Term.Orientation
+                    + Indulgence
+                    + CTL_DG
+                    + CTL_DS
+                    + CTL_C
                 , data = x

### 2023-07-28 cleaning.R

@@ -7,6 +7,7 @@ head(df)
 
 no_bots <- df_nobots$participantID
 
+df_raw <- df
 
 x <- df
 x <- subset(x, (participantID %in% no_bots))
@@ -15,3 +16,16 @@ df <- x
 
 write.csv(df, "data/data_with_means.csv", row.names = FALSE)
 save(df, file = "data/data_with_means.RData")
+
+x <- df_raw
+
+sum(x$att_check_nobots, na.rm = T)
+variable.names(x)
+
+46745-46490
+
+x <- x[which(x$att_check_nobots==1),]
+df <- x
+
+write.csv(df, "data/data_with_means_semi_clean.csv", row.names = FALSE)
+save(df, file = "data/data_with_means_semi_clean.RData")

### 2023-07-28 rw.R

@@ -247,4 +247,21 @@ alpha(risk_perception_tot)
 df$risk_perception_tot <- rowMeans(risk_perception_tot, na.rm = TRUE)
 
 
+####
+as.data.frame(table(df$country_name,df$Power.Distance))
+
+length(levels(as.factor(df$country_name[which(is.na(df$Power.Distance==0)==FALSE)])))
+length(levels(as.factor(df$country_name[which(is.na(df$Individualism==0)==FALSE)])))
+length(levels(as.factor(df$country_name[which(is.na(df$Uncertainty.Avoidance==0)==FALSE)])))
+length(levels(as.factor(df$country_name[which(is.na(df$Masculinity==0)==FALSE)])))
+
+length(levels(as.factor(df$country_name[which(is.na(df$Indulgence==0)==FALSE)])))
+length(levels(as.factor(df$country_name[which(is.na(df$Long.Term.Orientation==0)==FALSE)])))
+
+
+length(levels(as.factor(df$country_name[which(is.na(df$CTL_DG==0)==FALSE)])))
+length(levels(as.factor(df$country_name[which(is.na(df$CTL_DS==0)==FALSE)])))
+length(levels(as.factor(df$country_name[which(is.na(df$CTL_C==0)==FALSE)])))
+
+x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
 

### 2023-07-28 set_up_data_calculate_means.R

@@ -19,6 +19,14 @@ library(foreign)
 rm(list = ls())
 getwd()
 df <- read.csv("../data/ICSMP_cleaned_data.csv")
+#many_labs_COVID_data <- read_sav("/media/cillian/intel250G/Home/OneDrive - University of Limerick/Teaching/PS4033_PS6112_research_methods/2023/assessment/22_23/Assignment/many_labs_COVID_data.sav")
+
+#test <- dplyr::sample_n(df, 500)
+#test1 <- test %>% select(variable.names(many_labs_COVID_data))
+
+#many_labs_COVID_data_REPEAT <- test1
+
+#write_sav(many_labs_COVID_data_REPEAT, "/media/cillian/intel250G/Home/OneDrive - University of Limerick/Teaching/PS4033_PS6112_research_methods/2023/assessment/22_23/Assignment/many_labs_COVID_data_REPEAT.sav")
 
 #### moral identity internal alpha and combine ####
 

### 2023-07-31 H2.Rmd
ran extra semi-clean analyses
added list of countries for age correlations

@@
 
+rownames(subset(test, p < .05))
+
 total_sig <- length(test1$`mean age`)
@@
 pos <- sum(test1$r>0)
+neg
+
+noquote(paste0(rownames(test1[which(test1$r<0),]),sep=", "))
+noquote(paste0(rownames(test1[which(test1$r>0),]),sep=", "))
+
+neg_names <- rownames(test1[which(test1$r<0),])
+neg_names_first <- c(paste0(neg_names[1:(length(neg_names)-1)], sep = ", "))
+neg_names_end <- c("and " , neg_names[length(neg_names)])
+noquote(c(neg_names_first, neg_names_end))
+
+pos_names <- rownames(test1[which(test1$r>0),])
+pos_names_first <- c(paste0(pos_names[1:(length(pos_names)-1)], sep = ", "))
+pos_names_end <- c("and " , pos_names[length(pos_names)])
+noquote(c(pos_names_first, pos_names_end))
+
+test1$r>0
 
@@
 There was a significant correlation between age and internalization in `r total_sig` countries.
-Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Internalization)).
+Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries.
+The countries with a positive correlation were `r noquote(paste0(c(pos_names_first, pos_names_end), collapse = ""))`, and the countries with a negative correlation were `r noquote(paste0(c(neg_names_first, neg_names_end), collapse = ""))`  (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Internalization)).
 
@@
 
+neg_names <- rownames(test1[which(test1$r<0),])
+neg_names_first <- c(paste0(neg_names[1:(length(neg_names)-1)], sep = ", "))
+neg_names_end <- c("and " , neg_names[length(neg_names)])
+noquote(c(neg_names_first, neg_names_end))
+
+pos_names <- rownames(test1[which(test1$r>0),])
+pos_names_first <- c(paste0(pos_names[1:(length(pos_names)-1)], sep = ", "))
+pos_names_end <- c("and " , pos_names[length(pos_names)])
+print(noquote(c(pos_names_first, pos_names_end)))
+toString(noquote(paste0(c(pos_names_first, pos_names_end), collapse = "")))
+help("toString")
+
+toString(paste0(pos_names_first,collapse = ""))
+
+noquote(paste0(c(pos_names_first, pos_names_end), collapse = ""))
+noquote(paste0(c(neg_names_first, neg_names_end), collapse = ""))
+
 ```
@@
 `r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
-with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
+with a significant positive association between age and symbolization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
 *t*(`r sprintf("%.2f",results_coef$df[2])`) = 
@@
 *p* `r paste(p_report(p2))`.
-Again, to interpret this, we conducted a series of correlations to test if age was related to internalization across all countries.
-There was a significant correlation between age and internalization in `r total_sig` countries.
-Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).
+Again, to interpret this, we conducted a series of correlations to test if age was related to symbolization across all countries.
+There was a significant correlation between age and symbolization in `r total_sig` countries.
+Of these, there was a positive correlation between age and symbolization in `r pos` countries, and a negative correlation in `r neg` countries.
+The countries with a positive correlation were `r noquote(paste0(c(pos_names_first, pos_names_end), collapse = ""))`, and the countries with a negative correlation were `r noquote(paste0(c(neg_names_first, neg_names_end), collapse = ""))` (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).

### 2023-07-31 H2_semi_clean.Rmd
ran extra semi-clean analyses
added list of countries for age correlations

--- 2023-02-10 H2.Rmd
@@
 *p* `r paste(p_report(p2))`.
-Again, to interpret this, we conducted a series of correlations to test if age was related to internalization across all countries.
-There was a significant correlation between age and internalization in `r total_sig` countries.
-Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).
+Again, to interpret this, we conducted a series of correlations to test if age was related to symbolization across all countries.
+There was a significant correlation between age and symbolization in `r total_sig` countries.
+Of these, there was a positive correlation between age and symbolization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).

### 2023-07-31 H3.Rmd
added list of countries for age correlations

@@
   ,"Uncertainty Avoidance"
-  ,"Long Term Orientation"
-  ,"Indulgence"
-  ,"Tightness: Domain General"
-  ,"Tightness: Domain Specific"
-  ,"Tightness: Combination Measure"
+  # ,"Long Term Orientation"
+  # ,"Indulgence"
+  # ,"Tightness: Domain General"
+  # ,"Tightness: Domain Specific"
+  # ,"Tightness: Combination Measure"
 )
@@
             )
+
+# fit <- lm(moral_identity_symbolic ~
+#                      age
+#                     + sex3
+#                     #+ age
+#                     * (Power.Distance
+#                     + Individualism
+#                     + Masculinity
+#                     + Uncertainty.Avoidance
+#                     + Long.Term.Orientation
+#                     + Indulgence
+#                     + CTL_DG
+#                     + CTL_DS
+#                     + CTL_C)
+#                 , data = x
+#             )
 

### 2023-07-31 supp_H2.Rmd
added list of countries for age correlations

@@
 load("data/data_with_means.RData")
+#load("data/data_with_means_semi_clean.RData")
 
@@
     ,round(do.call(rbind, rs_for_table),digits=3)
-    ,do.call(rbind, ps_output_for_table)
+    ,do.call(rbind
+             , ps_output_for_table
+             #, ps_for_table
+             )
     )
@@
 test1
+test2 <- subset(test1, r < 0)
+
+test2
 
@@
 test <- test[order(rownames(test) ),]
+
+test[which(test$p<.05),]
 

### 2023-07-31 participants_section.R

@@ -63,4 +63,17 @@ levels(as.factor(df$country_name[which(is.na(df$CTL_DS))]))
 levels(as.factor(df$country_name[which(is.na(df$CTL_C))]))
 
 
+#### Countries with Cultural variables ####
+
+levels(as.factor(df$country_name[which(is.na(df$Power.Distance)==FALSE)]))
+levels(as.factor(df$country_name[which(is.na(df$Individualism)==FALSE)]))
+levels(as.factor(df$country_name[which(is.na(df$Masculinity)==FALSE)]))
+levels(as.factor(df$country_name[which(is.na(df$Uncertainty.Avoidance)==FALSE)]))
+levels(as.factor(df$country_name[which(is.na(df$Long.Term.Orientation)==FALSE)]))
+levels(as.factor(df$country_name[which(is.na(df$Indulgence)==FALSE)]))
+levels(as.factor(df$country_name[which(is.na(df$CTL_DG)==FALSE)]))
+levels(as.factor(df$country_name[which(is.na(df$CTL_DS)==FALSE)]))
+levels(as.factor(df$country_name[which(is.na(df$CTL_C)==FALSE)]))
+
+
 

### 2023-08-02 H1.Rmd
re-ran some analyses for paper (almost ready to submit)

@@
 
+test2 <- subset(test, p > .05)
+test2
+
+int_sig_pos <- test1[which(test1$`mean F`>test1$`mean M`),] # subset(test1, d > 0)
+int_sig_neg <- test1[which(test1$`mean F`<test1$`mean M`),] # subset(test1, d < 0)
+int_non_sig <- test2
+
 neg <- sum(test1$`mean F`<test1$`mean M`)
@@
 
+test2 <- subset(test, p > .05)
+test2
+
+symb_sig_pos <- test1[which(test1$`mean F`>test1$`mean M`),] # subset(test1, d > 0)
+symb_sig_neg <- test1[which(test1$`mean F`<test1$`mean M`),] # subset(test1, d < 0)
+symb_non_sig <- test2
+
 neg <- sum(test1$`mean F`<test1$`mean M`)

### 2023-08-02 H1_semi_clean.Rmd
ran extra semi-clean analyses
re-ran some analyses for paper (almost ready to submit)

--- 2023-02-10 H1.Rmd
@@
 x$sex3 <- droplevels(x$sex3)
+x$sex_01 <-  dplyr::recode(x$sex3,
+               "male"="0"
+              ,"female"="1")
 
@@
 x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
+
+regression_fun <- function(x){
+  fit <- lm(moral_identity_internal~sex_01+age, data = x)
+  summary(fit)
+}
+
+all_regressions <- lapply(x, regression_fun)
+all_regression_ps <- function(y){
+  y$coefficients[11]
+}
+lapply(all_regressions, all_regression_ps)
+regression_ps_for_table <- lapply(lapply(all_regressions, all_regression_ps), p_report)
 
@@
 
+mean(df$moral_identity_internal,na.rm=T)
+mean(df$moral_identity_symbolic,na.rm=T)
+
 ```
@@
     )
+
+test_with_regression <- 
+  cbind.data.frame(
+     round(do.call(rbind, female_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, male_means),digits=2)
+    ,round(do.call(rbind, female_sds),digits=2)
+    ,round(do.call(rbind, ts_for_table),digits=2)
+    ,round(do.call(rbind, df_for_table),digits=2)
+    ,do.call(rbind, ps_for_table)
+    ,do.call(rbind, regression_ps_for_table)
+    ,round(do.call(rbind, ds_for_table),digits=2)
+    )
+
+test_with_regression <- `colnames<-`(test_with_regression, c("mean F","SD F","mean M", "SD M", "t","df","p","p2","d"))
+test_with_regression
 

### 2023-08-02 H2.Rmd
re-ran some analyses for paper (almost ready to submit)

@@
 test1
+test2 <- subset(test, p > .05)
 
@@
 noquote(c(pos_names_first, pos_names_end))
+
+int_sig_pos <- pos_names # test1[which(test1$`mean F`>test1$`mean M`),] # subset(test1, d > 0)
+int_sig_neg <- neg_names # test1[which(test1$`mean F`<test1$`mean M`),] # subset(test1, d < 0)
+int_non_sig <- rownames(test2)
 
@@
 help("toString")
+
+symb_sig_pos <- pos_names # test1[which(test1$`mean F`>test1$`mean M`),] # subset(test1, d > 0)
+symb_sig_neg <- neg_names # test1[which(test1$`mean F`<test1$`mean M`),] # subset(test1, d < 0)
+symb_non_sig <- rownames(test2)
 

### 2023-08-02 participants_section.R

@@ -17,8 +17,8 @@ table(df$sex3)
 sum(is.na(df$sex3))
 
 desnum::descriptives(df$age)
-
-
+df_full <- df
+rm(df)
 rm(list = ls())
 #source("set_up_data_calculate_means.R")
 load("data/data_with_means.RData")
@@ -38,9 +38,30 @@ sum(is.na(df$sex3))
 
 desnum::descriptives(df$age)
 
+
+x <- df_full
+
 table(x$country_name)
+country_Ns_full <- table(x$country_name)
 country_Ns <- table(x$country_name)
 
+
+cbind(country_Ns,country_Ns_full)
+
+cbind(
+  rownames(country_Ns)
+  ,rownames(country_Ns_full)
+)
+
+country_full_names <- rownames(country_Ns_full)
+country_names <- rownames(country_Ns)
+
+sum(country_full_names %in% country_names)
+
+country_full_names[which(!(country_full_names %in% country_names))]
+Ghana <- df_full[which(df_full$country_name=="Ghana"),]
+
+df$country_name
 
 table(x$country_name)
 country_Ns <- table(x$country_name)

### 2023-08-02 rw.R

@@ -265,3 +265,132 @@ length(levels(as.factor(df$country_name[which(is.na(df$CTL_C==0)==FALSE)])))
 
 x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
 
+
+
+#### internalization / symbolization consistency across countries ####
+
+
+symb_sig
+symb_non_sig
+
+int_sig
+int_non_sig
+
+
+sum(rownames(symb_sig_pos) %in% rownames(int_sig_pos))
+sum(rownames(int_non_sig) %in% rownames(int_non_sig))
+
+sum(rownames(symb_sig_pos) %in% rownames(int_non_sig))
+sum(rownames(int_sig_pos) %in% rownames(symb_non_sig))
+
+sum(rownames(symb_sig_neg) %in% rownames(int_non_sig))
+sum(rownames(int_sig_neg) %in% rownames(symb_non_sig))
+
+sum(rownames(symb_sig_neg) %in% rownames(int_sig_pos))
+sum(rownames(int_sig_neg) %in% rownames(symb_sig_pos))
+
+
+rownames(symb_sig_pos[which(rownames(symb_sig_pos) %in% rownames(int_sig_pos)),])
+rownames(int_non_sig[which(rownames(int_non_sig) %in% rownames(symb_non_sig)),])
+
+rownames(symb_sig_pos[which(rownames(symb_sig_pos) %in% rownames(int_non_sig)),])
+rownames(int_sig_pos[which(rownames(int_sig_pos) %in% rownames(symb_non_sig)),])
+
+rownames(symb_sig_neg[which(rownames(symb_sig_neg) %in% rownames(int_non_sig)),])
+rownames(int_sig_neg[which(rownames(int_sig_neg) %in% rownames(symb_non_sig)),])
+rownames(symb_sig_neg[which(rownames(symb_sig_neg) %in% rownames(int_sig_pos)),])
+rownames(int_sig_neg[which(rownames(int_sig_neg) %in% rownames(symb_sig_pos)),])
+
+consistent <- c(
+  rownames(symb_sig_pos[which(rownames(symb_sig_pos) %in% rownames(int_sig_pos)),])
+  , rownames(int_non_sig[which(rownames(int_non_sig) %in% rownames(symb_non_sig)),])
+)
+
+#consistent %in%
[…]
